### 2017-12-20 Paper/paper.tex
Adding ICIP paper template

% Template for ICIP-2018 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{AUTHOR GUIDELINES FOR ICIP 2018 PROCEEDINGS MANUSCRIPTS}
%
% Single address.
% ---------------
\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
\address{Author Affiliation(s)}
%
% For example:
% ------------
%\address{School\\
%	Department\\
%	Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%	{School A-B\\
%	Department A-B\\
%	Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%	while at ...}}
%	{School C-D\\
%	Department C-D\\
%	Address C-D}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
Abstract
\end{abstract}
%
\begin{keywords}
One, two, three, four, five
\end{keywords}
%

% References should be produced using the bibtex program from suitable
% BiBTeX files (here: strings, refs, manuals). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{refs}

\end{document}

### 2017-12-21 ImageAnalogies.py
First try image analogies superresolution

@@ -1,0 +1,209 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import scipy.io as sio
+import scipy.misc
+from skimage.transform import pyramid_gaussian
+
+def rgb2gray(rgb):
+    r, g, b = rgb[:,:,0], rgb[:,:,1], rgb[:,:,2]
+    gray = 0.2989 * r + 0.5870 * g + 0.1140 * b
+    return gray
+
+def readImage(filename):
+    I = scipy.misc.imread(filename)
+    I = np.array(I, dtype=np.float32)/255.0
+    return I
+
+def writeImage(I, filename):
+    IRet = I*255.0
+    IRet[IRet > 255] = 255
+    IRet[IRet < 0] = 0
+    IRet = np.array(IRet, dtype=np.uint8)
+    scipy.misc.imsave(filename, IRet)
+
+def getPatches(I, dim):
+    """
+    Given an an MxN image I, get all dimxdim dimensional
+    patches
+    :return (M-dim+1)x(N-dim+1)x(dimxdim) array of patches
+    """
+    #http://stackoverflow.com/questions/13682604/slicing-a-numpy-image-array-into-blocks
+    shape = np.array(I.shape*2)
+    strides = np.array(I.strides*2)
+    W = np.asarray(dim)
+    shape[I.ndim:] = W
+    shape[:I.ndim] -= W - 1
+    if np.any(shape < 1):
+        raise ValueError('Window size %i is too large for image'%dim)
+    P = np.lib.stride_tricks.as_strided(I, shape=shape, strides=strides)
+    P = np.reshape(P, [P.shape[0], P.shape[1], dim*dim])
+    return P
+
+def getCausalPatches(I, dim):
+    """
+    Assuming dim is odd, return L-shaped patches that would
+    occur in raster order
+    """
+    P = getPatches(I, dim)
+    k = int((dim*dim-1)/2)
+    P = P[:, :, 0:k]
+    return P
+
+def getCoherenceMatch(X, x0, BpLidx, dim, i, j):
+    """
+    :param X: An MxNxDimFeatures array of feature vectors at each pixel
+    :param x0: The feature vector of the pixel that's being filled in
+    :param BpLidx: An MxN array of raveled indices from which pixels have
+        been drawn so far
+    :param dim: Dimension of patch
+    :param i: Row of pixel
+    :param j: Column of pixel
+    """
+    k = int((dim*dim-1)/2)
[…]

### 2018-01-07 VideoReordering.py
conv net features, reorganized options

@@ -10,6 +10,25 @@ import scipy.sparse as sparse
 import scipy.interpolate as interp
 from sklearn import manifold
 
+import argparse
+
+parser = argparse.ArgumentParser()
+parser.add_argument('--is-median-reorder', dest='median_reorder', action='store_true', help='enable median reordering')
+parser.add_argument('--is-simple-reorder', dest='median_reorder', action='store_false', help='enable simple reordering')
+parser.add_argument('--is-weighted-laplacian', dest='weighted_laplacian', action='store_true', help='enable weighted laplacian')
+parser.add_argument('--is-unweighted-laplacian', dest='weighted_laplacian', action='store_false', help='enable unweighted laplacian')
+parser.add_argument('--is-net-feat', dest='net_feat', action='store_true', help='enable resnet features')
+parser.add_argument('--is-pyr-feat', dest='net_feat', action='store_false', help='enable gaussian pyramid features')
+parser.add_argument('--pyr_level', type=int, default=0, help="pyramid level")
+parser.add_argument('--net_depth', type=int, default=0, help="at what layer do we extract features")
+parser.add_argument('--filename', default='jumpingjacks2menlowres.ogg', help="video filename")
+parser.set_defaults(median_reorder=False)
+parser.set_defaults(weighted_laplacian=False)
+parser.set_defaults(net_feat=False)
+
+opt = parser.parse_args()
+print(opt)
+
 def getReorderedConsensus1D(X, N, theta, doPlot = False):
     """
     Given an array of sliding windows and circular coordinates,
@@ -237,20 +256,19 @@ def reorderVideo(XOrig, X_feat, derivWin = 10, Weighted = False, doSimple = Fals
         return getReorderedConsensusVideo(X_proj, IDims, Mu_orig, VT_orig, dim, theta, doPlot, Verbose, lookAtVotes = False)
         #return getReorderedConsensusVideo(X, IDims, Mu, VT, dim, theta, doPlot, Verbose, lookAtVotes = False)
 
+def get_out_filename(base_filename, do_simple, is_weighted, is_net_feat, pyr_level=0, layer=0):
+    filename = str(base_filename)
+    filename = filename+'-simple' if do_simple else filename+'-median'
+    filename = filename+'-weighted' if is_weighted else filename+'-unweighted'
[…]

### 2018-01-07 VideoTools.py

@@ -11,6 +11,7 @@ import subprocess
 import matplotlib.image as mpimage
 import scipy.misc
 import scipy.signal
+import sys
 from scipy.ndimage import gaussian_gradient_magnitude
 from PIL import Image
 
@@ -153,6 +154,60 @@ def loadImageIOVideo(path,pyr_level=0):
             IDims = frame.shape
         I[i, :] = np.array(frame.flatten(), dtype = np.float32)/255.0
         I_feat[i, :] = np.array(feat_frame.flatten(), dtype = np.float32)/255.0
+    return (I, I_feat, IDims)
+
+def loadVideoResNetFeats(path, depth=0):
+    if not os.path.exists(path):
+        print("ERROR: Video path not found: %s"%path)
+        return None
+
+    import imageio
+    import torch
+    import torch.nn as nn
+    import torch.backends.cudnn as cudnn
+    import torchvision.transforms as transforms
+    import torchvision.models as models
+    from torch.autograd import Variable
+
+    # get first layers of network - we can try out different things here
+    if depth == 0:
+        shallow_layers = ['conv1','bn1','relu','maxpool']
+    elif depth == 1:
+        shallow_layers = ['conv1','bn1','relu','maxpool','layer1']
+    else:
+        print('unknown depth?',depth)
+        shallow_layers = ['conv1','bn1','relu','maxpool']
+    net = models.__dict__['resnet18'](pretrained=True)
+    resnet_module = net.modules().__next__()
+    resnet_modules = resnet_module.named_children()
+    shallow_nn = []
+    for module_name,module in resnet_modules:
+        if module_name in shallow_layers:
+            print('module ',module_name)
+            shallow_nn.append(module)
+
+    # preprocessing for network
+    full_transform = transforms.Compose([transforms.ToTensor(),transforms.Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
+
+    videoReader = imageio.get_reader(path, 'ffmpeg')
+    NFrames = videoReader.get_length()
+    I,I_feat = None,None
+    for i in range(0, NFrames):
+        frame = videoReader.get_data(i)
+        frame_th = full_transform(Image.fromarray(frame)) # easiest to convert to PIL, then apply torch transforms
+        frame_mb = frame_th.view(1,frame_th.size()[0],frame_th.size()[1],frame_th.size()[2])
+        frame_var = Variable(frame_mb,requires_grad=False)
[…]

### 2018-01-10 Paper/paper.tex
Adding most of references to bib file, starting to fill in paper background / methods

@@
+%%TODO: IF THIS GETS IN, CITE MY THESIS (since I present an early version
+%of this idea in my background and copied some text from there)
+
 % Template for ICIP-2018 paper; to be used with:
@@
 
+\section{Introduction}
+
+\section{Background}
+
+Similar tricks with the graph Laplacian have been used to re-arrange images around a loop as a pre-processing step for structure from motion (\cite{averbuch2015ringit}) and to re-order the frames of microscope images a developing embryo (\cite{dsilva2015diffusionvecordering}).
+A more topological approach with cohomology circular coordinates was used to parameterize a sliding window embedding of the Lorenz attractor (\cite{de2012topological}).
+
+\section{Method}
+As shown in , the sliding window embeddings of periodic signals form a topological loop.
+This implies that, at the right scale, a mutual nearest neighbor graph (Definition~\ref{eq:csmbinarymutual}) built on the sliding window point cloud should be a circle graph, which means the first two nonzero eigenvectors should be a sine and cosine, or orthogonal linear combinations therein.
+When plotted against each other, they make an approximate circle, and the arctangent of the two eigenvector coordinates at every window can be used to determine the {\em phase} of the corresponding window in the periodic signal.
+The first sample of each window can then be re-sorted by phase.
+Figure~\ref{fig:signaldelayresorted} shows an example of running this algorithm on a sampled signal $f(t) = \cos(t) + \cos(3t)$.
+There are only 12 samples per period in the original signal, so the details of each period are rather coarse.
+However, once they are re-sorted, we get a nice, fine-detailed representation of one period.
+This can be used to fake temporal super-resolution or ``slow motion'' for signals.
+Eventually, we hope to add some image processing tools to make aesthetically pleasing slow motion representations of periodic videos using this technique.
+
+Similar tricks with the graph Laplacian have been used to re-arrange images around a loop as a pre-processing step for structure from motion (\cite{averbuch2015ringit}) and to re-order the frames of microscope images a developing embryo (\cite{dsilva2015diffusionvecordering}).
+A more topological approach with cohomology circular coordinates was used to parameterize a sliding window embedding of the Lorenz attractor (\cite{de2012topological}).
+
 % References should be produced using the bibtex program from suitable

### 2018-01-11 ImageAnalogies.py
Working on paper figures, reverting back to old version of image analogies

@@ -3,54 +3,76 @@ import matplotlib.pyplot as plt
 import scipy.io as sio
 import scipy.misc
 from skimage.transform import pyramid_gaussian
-import spams
 import pyflann
-import time
-from VideoTools import *
 from PatchTools import *
 
-def getPatchDictionaries(As, Aps, NLevels = 3, KSpatials = [5, 5], FactorsPerFrame = 256, lam = 1, patchfn = getColorPatchesImageSet, NSubsample = 100000):
+
+def getCoherenceMatch(X, x0, BpLidx, dim, i, j):
     """
-    :param As: An array of images of the same dimension
-    :param Aps: An array of images of the same dimension as As, parallel to As
+    :param X: An NImagesxMxNxDimFeatures array of feature vectors at each pixel\
+                in each image
+    :param x0: The feature vector of the pixel that's being filled in
+    :param BpLidx: An MxN array of raveled indices from which pixels have
+        been drawn so far
+    :param dim: Dimension of patch
+    :param i: Row of pixel
+    :param j: Column of pixel
     """
-    #Initialize dictionaries at each level
-    Dicts = {}
-    for level in range(NLevels, -1, -1):
-        Dicts[level] = np.array([])
-    for i in range(len(As)):
-        #Make image pyramids
-        AL = tuple(pyramid_gaussian(As[i], NLevels, downscale = 2))
-        ApL = tuple(pyramid_gaussian(Aps[i], NLevels, downscale = 2))
-        #Build dictionaries level by level
-        for level in range(NLevels, -1, -1):
-            print("Making dictionary frame %i of %i, level %i"%(i, len(As), level))
-            KSpatial = KSpatials[-1]
-            if level == 0:
-                KSpatial = KSpatials[0]
-            #Step 1: Make features
-            X = patchfn([AL[level]], KSpatial, getPatches)
-            ApPatches = patchfn([ApL[level]], KSpatial, getCausalPatchesWPixel)
-            X = np.concatenate((X, ApPatches), 3)
-            if level < NLevels:
-                #Use multiresolution features
-                As2 = [scipy.misc.imresize(AL[level+1], AL[level].shape)]
[…]

### 2018-01-11 Laplacian.py

@@ -74,14 +74,17 @@ def getLapCircularCoordinatesSigma(D, sigma, NEigs = 20, doPlot = False):
             smallest = bothSum
             i1 = i       
     if doPlot:
-        plt.subplot(211)
+        plt.subplot(311)
         plt.imshow(v, cmap = 'afmhot', interpolation = 'nearest', aspect = 'auto')
         plt.xlim([0, v.shape[1]])
         plt.title("Eigenvectors")
-        plt.subplot(212)
+        plt.subplot(312)
         plt.plot(zcs)
         plt.title("Zero Crossings, Smallest = (%i, %i)"%(i1, i1+1))
         plt.xlim([0, v.shape[1]])
+        plt.subplot(313)
+        plt.plot(v[:, [i1, i1+1]])
+        plt.legend(["%i"%i1, "%i"%(i1+1)])
         plt.show()
     (theta, thetau) = getLapThetas(v, i1, i1+1)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}

### 2018-01-11 PaperFigures.py

@@ -5,6 +5,7 @@ import scipy.interpolate as interp
 from VideoReordering import *
 from Laplacian import *
 from CSMSSMTools import *
+from FundamentalFreq import *
 from sklearn.decomposition import PCA
 from ripser import ripser
 
@@ -30,20 +31,25 @@ def getSlidingWindow(x, dim, Tau, dT):
         xidx.append(xidx[-1])
     return (X, xidx)
 
-if __name__ == '__main__':
+def ReorderingExample1D():
     np.random.seed(100)
     useGroundTruth = False #Whether to use ground truth circular coordinates in the reordering
-    Weighted = False #Whether to use the weighted graph laplacian
+    Weighted = True #Whether to use the weighted graph laplacian
     NPeriods = 20
     SamplesPerPeriod = 12
     N = NPeriods*SamplesPerPeriod
     t = np.linspace(0, 2*np.pi*NPeriods, N)
     t2 = np.linspace(0, 2*np.pi, N)
-    x = np.cos(t) + np.cos(3*t) + np.cos(5*t)
+    x = np.cos(t) + 0.5*np.cos(3*t) + 0.5*np.cos(5*t)
     x = x + 0.6*np.random.randn(len(x))
-    x2 = np.cos(t2) + np.cos(3*t2) + np.cos(5*t2)
+    x2 = np.cos(t2) + 0.5*np.cos(3*t2) + 0.5*np.cos(5*t2)
 
-    dim = 40 #Sliding window length
+    doPlot = True
+    dim = int(np.round(estimateFundamentalFreq(x, shortBias = 0.0, doPlot = doPlot)[0]))
+    if doPlot:
+        plt.show()
+    dim = 2*dim
+    print("dim = %i"%dim)
     (X, xidx) = getSlidingWindow(x, dim, 1, 1)
     
     #Use rips filtration to guide Laplacian
@@ -53,7 +59,7 @@ if __name__ == '__main__':
     thresh = np.argmax(I[:, 1] - I[:, 0])
     thresh = np.mean(I[thresh, :])
     if Weighted:
-        res = getLapCircularCoordinatesSigma(D, thresh)
+        res = getLapCircularCoordinatesSigma(D, thresh, doPlot = True)
     else:
         res = getLapCircularCoordinatesThresh(D, thresh)
     [w, v, theta, A] = [res['w'], res['v'], res['theta'], res['A']]
@@ -133,3 +139,6 @@ if __name__ == '__main__':
[…]

### 2018-01-11 ImageAnalogies.py
Adding support for image analogies in video reordering

@@ -5,7 +5,8 @@ import scipy.misc
 from skimage.transform import pyramid_gaussian
 import pyflann
 from PatchTools import *
-
+from sklearn.decomposition import PCA
+import time
 
 def getCoherenceMatch(X, x0, BpLidx, dim, i, j):
     """
@@ -29,9 +30,11 @@ def getCoherenceMatch(X, x0, BpLidx, dim, i, j):
     #TODO: Vectorize code below
     for n in range(dI.size):
         #Indices of pixel picked for neighbor
-        imidx = int(BpLidx[dI[n]+i, dJ[n]+j][0])
-        ni = BpLidx[dI[n]+i, dJ[n]+j][1]
-        nj = BpLidx[dI[n]+i, dJ[n]+j][1]
+        offi = int(dI[n]+i)
+        offj = int(dJ[n]+j)
+        imidx = int(BpLidx[offi, offj][0])
+        ni = BpLidx[offi, offj][1]
+        nj = BpLidx[offi, offj][1]
         if ni == -1 or nj == -1:
             continue
         ni = int(ni - dI[n])
@@ -45,34 +48,7 @@ def getCoherenceMatch(X, x0, BpLidx, dim, i, j):
             idxmin = [imidx, ni, nj]
     return (idxmin, minDistSqr)
 
-def getGrayscalePatchesImageSet(As, KSpatial, patchfn):
-    if len(As) == 0:
-        return None
-    AllP = patchfn(rgb2gray(As[0]), KSpatial)[None, :, :, :]
-    for A in As[1::]:
-        P = patchfn(rgb2gray(A), KSpatial)[None, :, :, :]
-        AllP = np.concatenate((AllP, P), 0)
-    return AllP
-
-def getColorPatchesImageSet(As, KSpatial, patchfn):
-    if len(As) == 0:
-        return None
-    AllP = np.array([])
-    for A in As:
-        P = np.array([])
-        for k in range(3):
-            Pk = patchfn(A[:, :, k], KSpatial)
-            if P.size == 0:
-                P = Pk
-            else:
-                P = np.concatenate((P, Pk), 2)
-        if AllP.size == 0:
-            AllP = P[None, :, :, :]
-        else:
-            AllP = np.concatenate((AllP, P[None, :, :, :]), 0)
-    return AllP
-
-def getPatchDictionaries(As, Aps, NLevels = 3, KSpatials = [5, 5], patchfn = getColorPatchesImageSet):
[…]

### 2018-01-11 PatchTools.py

@@ -15,6 +15,11 @@ def writeImage(I, filename):
     IRet = np.array(IRet, dtype=np.uint8)
     scipy.misc.imsave(filename, IRet)
 
+def resizeImage(F, dims):
+    FNew = scipy.misc.imresize(np.array(255*F, dtype = np.uint8), dims)
+    FNew = np.array(FNew, dtype = np.float64)/255.0
+    return FNew
+
 def rgb2gray(rgb):
     r, g, b = rgb[:,:,0], rgb[:,:,1], rgb[:,:,2]
     gray = 0.2989 * r + 0.5870 * g + 0.1140 * b

### 2018-01-11 VideoReordering.py

@@ -3,6 +3,8 @@ from ripser import ripser
 from CSMSSMTools import *
 from Laplacian import *
 from FundamentalFreq import *
+from PatchTools import *
+from ImageAnalogies import *
 import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib.image as mpimage
@@ -13,6 +15,7 @@ from sklearn import manifold
 import argparse
 
 parser = argparse.ArgumentParser()
+parser.add_argument('--do-image-analogies', dest='image_analogies', action='store_true', help='use image analogies to sharpen')
 parser.add_argument('--is-median-reorder', dest='median_reorder', action='store_true', help='enable median reordering')
 parser.add_argument('--is-simple-reorder', dest='median_reorder', action='store_false', help='enable simple reordering')
 parser.add_argument('--is-weighted-laplacian', dest='weighted_laplacian', action='store_true', help='enable weighted laplacian')
@@ -162,8 +165,47 @@ def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, theta, doPlot = False, Ver
         mpimage.imsave("%s%i.png"%(TEMP_STR, i+1), np.reshape(XRet[i, :], IDims))
     return XRet
     
+def downsampleVideo(I, IDims, fac):
+    INew = []
+    IDimsNew = [int(IDims[0]*fac), int(IDims[1]*fac), 3]
+    for i in range(I.shape[0]):
+        FNew = resizeImage(np.reshape(I[i, :], IDims), IDimsNew)
+        INew.append(FNew.flatten())
+    return (np.array(INew), IDimsNew)
 
-def reorderVideo(XOrig, X_feat, derivWin = 10, Weighted = False, doSimple = False, doPlot = True, Verbose = False):
+def upsampleVideo(I, IDims, IDimsNew):
+    INew = []
+    for i in range(I.shape[0]):
+        FNew = resizeImage(np.reshape(I[i, :], IDims), IDimsNew)
+        INew.append(FNew.flatten())
+    return np.array(INew)
+
+def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = 20):
+    """
+    Use image analogies to sharpen the consensus video
+    """
+    #Randomly sample 10 analogy image pairs from original video
+    As = []
+    Aps = []
+    np.random.seed(NExamples)
[…]

### 2018-01-15 AllExperiments.py
Adding batch tests for the videos that are there now

@@ -1,0 +1,23 @@
+import subprocess
+import os
+import numpy as np
+from VideoReordering import *
+
+Videos=['jumpingjacks2menlowres.ogg', 'jumpingjacks2men.ogg', 'Videos/ChrisNeckAmp.avi'\
+        'Videos/face_results.avi', 'Videos/baby_results.mp4', 'Videos/throat_mag_crop.mp4',
+        'Videos/exercise_1_crop.mp4', 'Videos/exercise_2_crop.mp4']
+LapOpt = ["--is-unweighted-laplacian", "--is-weighted-laplacian"]
+MedianOpt = ["--is-simple-reorder", "--is-median-reorder"]
+pyrLevel = 2
+
+for V in Videos:
+    for medianReorder in [0, 1]:
+        for weighted in [0, 1]:
+            strs = [MedianOpt[medianReorder], LapOpt[weighted]]
+            fileprefix = get_out_fileprefix('reordered', V, not medianReorder, weighted, opt.net_feat, pyrLevel, opt.net_depth)
+            print(fileprefix)
+            if os.path.exists("%s.avi"%fileprefix):
+                print("Skipping %s..."%fileprefix)
+                continue
+            cmd = ["python", "VideoReordering.py", "--filename", V, "--show-plots", "--pyr_level", "%i"%pyrLevel] + strs
+            subprocess.call(cmd)

### 2018-01-15 Laplacian.py

@@ -85,7 +85,6 @@ def getLapCircularCoordinatesSigma(D, sigma, NEigs = 20, doPlot = False):
         plt.subplot(313)
         plt.plot(v[:, [i1, i1+1]])
         plt.legend(["%i"%i1, "%i"%(i1+1)])
-        plt.show()
     (theta, thetau) = getLapThetas(v, i1, i1+1)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
 

### 2018-01-15 VideoReordering.py

@@ -15,6 +15,7 @@ from sklearn import manifold
 import argparse
 
 parser = argparse.ArgumentParser()
+parser.add_argument('--show-plots', dest='doPlot', action='store_true', help='Show plots of circular coordinates')
 parser.add_argument('--do-image-analogies', dest='image_analogies', action='store_true', help='use image analogies to sharpen')
 parser.add_argument('--is-median-reorder', dest='median_reorder', action='store_true', help='enable median reordering')
 parser.add_argument('--is-simple-reorder', dest='median_reorder', action='store_false', help='enable simple reordering')
@@ -30,7 +31,6 @@ parser.set_defaults(weighted_laplacian=False)
 parser.set_defaults(net_feat=False)
 
 opt = parser.parse_args()
-print(opt)
 
 def getReorderedConsensus1D(X, N, theta, doPlot = False):
     """
@@ -151,7 +151,7 @@ def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, theta, doPlot = False, Ver
     XRet = np.zeros(VT.shape)
     for i in range(VT.shape[0]):
         if Verbose:
-            print("Interpolating window %i of %i"%(i+1, N))
+            print("Taking consensus for window %i of %i"%(i+1, N))
         F = XInterp[:, i, :]
         F = F[np.sum(np.isnan(F), 1) == 0, :]
         F = F.dot(VT) + Mu
@@ -205,7 +205,8 @@ def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = 20):
     return np.array(XFinal)
 
 def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
-                doSimple = False, doImageAnalogies = False, doPlot = True, Verbose = False):
+                doSimple = False, doImageAnalogies = False, doPlot = True, \
+                Verbose = False, fileprefix = ""):
     """
     Reorder the video based on circular coordinates of a sliding
     window embedding
@@ -238,9 +239,18 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
     if derivWin > 0:
         [X, validIdx] = getTimeDerivative(X, derivWin)
     XIso = manifold.Isomap(10, 2).fit_transform(X)
[…]

### 2018-01-15 AllExperiments.py
Fixed a little mistake in the video paths

@@ -3,8 +3,8 @@ import os
 import numpy as np
 from VideoReordering import *
 
-Videos=['jumpingjacks2menlowres.ogg', 'jumpingjacks2men.ogg', 'Videos/ChrisNeckAmp.avi'\
-        'Videos/face_results.avi', 'Videos/baby_results.mp4', 'Videos/throat_mag_crop.mp4',
+Videos=['Videos/ChrisNeckAmp.avi','jumpingjacks2menlowres.ogg',\
+        'Videos/face_results.mp4', 'Videos/baby_result.mp4', 'Videos/throat_mag_crop.mp4',
         'Videos/exercise_1_crop.mp4', 'Videos/exercise_2_crop.mp4']
 LapOpt = ["--is-unweighted-laplacian", "--is-weighted-laplacian"]
 MedianOpt = ["--is-simple-reorder", "--is-median-reorder"]

### 2018-01-15 PaperFigures.py

@@ -34,24 +34,25 @@ def getSlidingWindow(x, dim, Tau, dT):
 def ReorderingExample1D():
     np.random.seed(100)
     useGroundTruth = False #Whether to use ground truth circular coordinates in the reordering
-    Weighted = True #Whether to use the weighted graph laplacian
+    Weighted = False #Whether to use the weighted graph laplacian
     NPeriods = 20
     SamplesPerPeriod = 12
     N = NPeriods*SamplesPerPeriod
     t = np.linspace(0, 2*np.pi*NPeriods, N)
     t2 = np.linspace(0, 2*np.pi, N)
-    x = np.cos(t) + 0.5*np.cos(3*t) + 0.5*np.cos(5*t)
+    cs = [1.0, 1.0, 1.0]
+    x = cs[0]*np.cos(t) + cs[1]*np.cos(3*t) + cs[2]*np.cos(5*t)
     x = x + 0.6*np.random.randn(len(x))
-    x2 = np.cos(t2) + 0.5*np.cos(3*t2) + 0.5*np.cos(5*t2)
+    x2 = cs[0]*np.cos(t2) + cs[1]*np.cos(3*t2) + cs[2]*np.cos(5*t2)
 
-    doPlot = True
+    doPlot = False
     dim = int(np.round(estimateFundamentalFreq(x, shortBias = 0.0, doPlot = doPlot)[0]))
     if doPlot:
         plt.show()
     dim = 2*dim
     print("dim = %i"%dim)
     (X, xidx) = getSlidingWindow(x, dim, 1, 1)
-    
+
     #Use rips filtration to guide Laplacian
     D = getSSM(X)
     Is = ripser.doRipsFiltrationDM(D, 1, coeff=41)
@@ -63,16 +64,20 @@ def ReorderingExample1D():
     else:
         res = getLapCircularCoordinatesThresh(D, thresh)
     [w, v, theta, A] = [res['w'], res['v'], res['theta'], res['A']]
-    
+
     ##Ground truth
     if useGroundTruth:
         theta = np.mod(t[0:len(theta)], 2*np.pi)
-    
-    ridx = np.argsort(theta)
+
+    tu = np.unwrap(theta)
+    if tu[-1] - tu[0] < 0:
+        tu = -tu
+    tu = tu - np.min(tu)
+    ridx = np.argsort(np.mod(tu, 2*np.pi))
     xresort = x[ridx]
 
     #Do denoising
[…]

### 2018-01-15 VideoReordering.py

@@ -288,7 +288,7 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
         plt.subplot(234)
         plt.imshow(v, cmap = 'afmhot', interpolation = 'nearest', aspect = 'auto')
         plt.subplot(235)
-        plt.scatter(v[:, 1], v[:, 2], 20, np.arange(v.shape[0]), cmap = 'spectral')
+        plt.scatter(v[:, idxs[0]], v[:, idxs[1]], 20, np.arange(v.shape[0]), cmap = 'spectral')
         plt.title("Eigs %i and %i"%(idxs[0], idxs[1]))
         plt.subplot(236)
         plt.plot(theta)

### 2018-01-16 Laplacian.py
Found a math bug in the weighted Laplacian

@@ -50,18 +50,7 @@ def getSlopes(thetas, sWin = 10):
     slopes[-(sWin+1):] = slopes[-(sWin+1)]
     return slopes
 
-def getLapCircularCoordinatesSigma(D, sigma, NEigs = 20, doPlot = False):
-    """
-    Get circular coordinates using a weighted laplacian 
-    :param pD: Distance matrix
-    :param sigma: Standard deviation for exponential kernel
-    :param NEigs: Maximum number of eigenvectors to compute
-    :return {'w':eigenvalues, 'v':eigenvectors, 'theta':Circular coordinates,\
-            'thetau':Unwrapped circular coordinates, 'A':Adjacency matrix}
-    """
-    A = np.exp(-D*D/(2*sigma**2))
-    NEigs = min(NEigs, A.shape[0])
-    (w, v, L) = getLaplacianEigsDense(A, NEigs)
+def getSlowestEigenvectorIdx(v):
     #Compute zero crossings and put the low frequencies eigenvectors first
     s = v > 0
     zcs = np.sum(s[1::, :] - s[0:-1, :], 0)
@@ -72,7 +61,23 @@ def getLapCircularCoordinatesSigma(D, sigma, NEigs = 20, doPlot = False):
         bothSum = zcs[i] + zcs[i+1]
         if bothSum < smallest:
             smallest = bothSum
-            i1 = i       
+            i1 = i
+    return (i1, zcs)
+
+def getLapCircularCoordinatesSigma(D, sigma, NEigs = 20, doPlot = False):
+    """
+    Get circular coordinates using a weighted laplacian 
+    :param pD: Distance matrix
+    :param sigma: Standard deviation for exponential kernel
+    :param NEigs: Maximum number of eigenvectors to compute
+    :return {'w':eigenvalues, 'v':eigenvectors, 'theta':Circular coordinates,\
+            'thetau':Unwrapped circular coordinates, 'A':Adjacency matrix}
+    """
+    A = np.exp(-D*D/(sigma))
+    np.fill_diagonal(A, 0)
+    NEigs = min(NEigs, A.shape[0])
+    (w, v, L) = getLaplacianEigsDense(A, NEigs)
+    (i1, zcs) = getSlowestEigenvectorIdx(v)
     if doPlot:
         plt.subplot(311)
[…]

### 2018-01-16 PaperFigures.py

@@ -31,10 +31,8 @@ def getSlidingWindow(x, dim, Tau, dT):
         xidx.append(xidx[-1])
     return (X, xidx)
 
-def ReorderingExample1D():
-    np.random.seed(100)
+def ReorderingExample1D(seed, Weighted):
     useGroundTruth = False #Whether to use ground truth circular coordinates in the reordering
-    Weighted = False #Whether to use the weighted graph laplacian
     NPeriods = 20
     SamplesPerPeriod = 12
     N = NPeriods*SamplesPerPeriod
@@ -42,6 +40,7 @@ def ReorderingExample1D():
     t2 = np.linspace(0, 2*np.pi, N)
     cs = [1.0, 1.0, 1.0]
     x = cs[0]*np.cos(t) + cs[1]*np.cos(3*t) + cs[2]*np.cos(5*t)
+    np.random.seed(seed)
     x = x + 0.6*np.random.randn(len(x))
     x2 = cs[0]*np.cos(t2) + cs[1]*np.cos(3*t2) + cs[2]*np.cos(5*t2)
 
@@ -49,7 +48,6 @@ def ReorderingExample1D():
     dim = int(np.round(estimateFundamentalFreq(x, shortBias = 0.0, doPlot = doPlot)[0]))
     if doPlot:
         plt.show()
-    dim = 2*dim
     print("dim = %i"%dim)
     (X, xidx) = getSlidingWindow(x, dim, 1, 1)
 
@@ -60,10 +58,10 @@ def ReorderingExample1D():
     thresh = np.argmax(I[:, 1] - I[:, 0])
     thresh = np.mean(I[thresh, :])
     if Weighted:
-        res = getLapCircularCoordinatesSigma(D, thresh, doPlot = True)
+        res = getLapCircularCoordinatesSigma(D, thresh, NEigs = 10)
     else:
-        res = getLapCircularCoordinatesThresh(D, thresh)
-    [w, v, theta, A] = [res['w'], res['v'], res['theta'], res['A']]
+        res = getLapCircularCoordinatesThresh(D, thresh, NEigs = 10)
+    [w, v, theta, A, idxs] = [res['w'], res['v'], res['theta'], res['A'], res['idxs']]
 
     ##Ground truth
     if useGroundTruth:
@@ -77,7 +75,7 @@ def ReorderingExample1D():
     xresort = x[ridx]
 
[…]

### 2018-01-16 VideoReordering.py

@@ -88,7 +88,7 @@ def getReorderedConsensus1D(X, N, theta, doPlot = False):
         plt.xlabel("Time")
         plt.ylabel("Spline Interpolated Windows")
         plt.show()
-    return np.nanmedian(Z, 0)
+    return (Z, np.nanmedian(Z, 0))
 
 def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, theta, doPlot = False, Verbose = False, lookAtVotes = False):
     """

### 2018-01-16 PaperFigures.py
Making a lot of progress on the concept figure

@@ -8,11 +8,12 @@ from CSMSSMTools import *
 from FundamentalFreq import *
 from sklearn.decomposition import PCA
 from ripser import ripser
+from mpl_toolkits.mplot3d import Axes3D
 
-def drawLineColored(idx, x, C):
+def drawLineColored(idx, x, C, linewidth = 1):
     plt.hold(True)
     for i in range(len(x)-1):
-        plt.plot(idx[i:i+2], x[i:i+2], c=C[i, :])
+        plt.plot(idx[i:i+2], x[i:i+2], c=C[i, :], linewidth = linewidth)
 
 def getSlidingWindow(x, dim, Tau, dT):
     N = len(x)
@@ -31,18 +32,19 @@ def getSlidingWindow(x, dim, Tau, dT):
         xidx.append(xidx[-1])
     return (X, xidx)
 
+def MSE(x1, x2):
+    return np.mean((x1-x2)**2)
+
 def ReorderingExample1D(seed, Weighted):
     useGroundTruth = False #Whether to use ground truth circular coordinates in the reordering
     NPeriods = 20
     SamplesPerPeriod = 12
     N = NPeriods*SamplesPerPeriod
     t = np.linspace(0, 2*np.pi*NPeriods, N)
-    t2 = np.linspace(0, 2*np.pi, N)
     cs = [1.0, 1.0, 1.0]
     x = cs[0]*np.cos(t) + cs[1]*np.cos(3*t) + cs[2]*np.cos(5*t)
     np.random.seed(seed)
     x = x + 0.6*np.random.randn(len(x))
-    x2 = cs[0]*np.cos(t2) + cs[1]*np.cos(3*t2) + cs[2]*np.cos(5*t2)
 
     doPlot = False
     dim = int(np.round(estimateFundamentalFreq(x, shortBias = 0.0, doPlot = doPlot)[0]))
@@ -50,6 +52,10 @@ def ReorderingExample1D(seed, Weighted):
         plt.show()
     print("dim = %i"%dim)
     (X, xidx) = getSlidingWindow(x, dim, 1, 1)
+
+    #Make ground truth cycle
+    t2 = np.linspace(0, 2*np.pi, X.shape[0])
+    xgt = cs[0]*np.cos(t2) + cs[1]*np.cos(3*t2) + cs[2]*np.cos(5*t2)
 
     #Use rips filtration to guide Laplacian
     D = getSSM(X)
[…]

### 2018-01-16 VideoReordering.py

@@ -58,9 +58,9 @@ def getReorderedConsensus1D(X, N, theta, doPlot = False):
     print("NPeriods = %g"%NPeriods)
     print("N/NPeriods = %g"%(float(N)/NPeriods))
     tu = N*np.mod(tu, 2*np.pi)/(2*np.pi)
-    idx = np.argsort(tu)
-    X2 = X[idx, :]
-    t1 = tu[idx]
+    tidx = np.argsort(tu)
+    X2 = X[tidx, :]
+    t1 = tu[tidx]
     
     #Step 2: Go through each window and use it to vote on final samples
     Z = np.ones((M, N))
@@ -88,7 +88,7 @@ def getReorderedConsensus1D(X, N, theta, doPlot = False):
         plt.xlabel("Time")
         plt.ylabel("Spline Interpolated Windows")
         plt.show()
-    return (Z, np.nanmedian(Z, 0))
+    return (Z, np.nanmedian(Z, 0), tidx)
 
 def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, theta, doPlot = False, Verbose = False, lookAtVotes = False):
     """

### 2018-01-16 Paper/paper.tex
Just about finished concept figure

@@
 Similar tricks with the graph Laplacian have been used to re-arrange images around a loop as a pre-processing step for structure from motion (\cite{averbuch2015ringit}) and to re-order the frames of microscope images a developing embryo (\cite{dsilva2015diffusionvecordering}).
-A more topological approach with cohomology circular coordinates was used to parameterize a sliding window embedding of the Lorenz attractor (\cite{de2012topological}).
+A different topological approach with cohomology circular coordinates was used to parameterize a sliding window embedding of the Lorenz attractor (\cite{de2012topological}).
 
@@
 As shown in , the sliding window embeddings of periodic signals form a topological loop.
-This implies that, at the right scale, a mutual nearest neighbor graph (Definition~\ref{eq:csmbinarymutual}) built on the sliding window point cloud should be a circle graph, which means the first two nonzero eigenvectors should be a sine and cosine, or orthogonal linear combinations therein.
+This implies that, at the right scale, a mutual nearest neighbor graph built on the sliding window point cloud should be a circle graph, which means the first two nonzero eigenvectors should be a sine and cosine, or orthogonal linear combinations therein.
 When plotted against each other, they make an approximate circle, and the arctangent of the two eigenvector coordinates at every window can be used to determine the {\em phase} of the corresponding window in the periodic signal.

### 2018-01-16 PaperFigures.py

@@ -35,8 +35,7 @@ def getSlidingWindow(x, dim, Tau, dT):
 def MSE(x1, x2):
     return np.mean((x1-x2)**2)
 
-def ReorderingExample1D(seed, Weighted):
-    useGroundTruth = False #Whether to use ground truth circular coordinates in the reordering
+def ReorderingExample1D(seed):
     NPeriods = 20
     SamplesPerPeriod = 12
     N = NPeriods*SamplesPerPeriod
@@ -53,6 +52,11 @@ def ReorderingExample1D(seed, Weighted):
     print("dim = %i"%dim)
     (X, xidx) = getSlidingWindow(x, dim, 1, 1)
 
+    #Make color array
+    c = plt.get_cmap('Spectral')
+    C = c(np.array(np.round(np.linspace(0, 255, X.shape[0])), dtype=np.int32))
+    C = C[:, 0:3]
+
     #Make ground truth cycle
     t2 = np.linspace(0, 2*np.pi, X.shape[0])
     xgt = cs[0]*np.cos(t2) + cs[1]*np.cos(3*t2) + cs[2]*np.cos(5*t2)
@@ -63,41 +67,16 @@ def ReorderingExample1D(seed, Weighted):
     I = Is[1]
     thresh = np.argmax(I[:, 1] - I[:, 0])
     thresh = np.mean(I[thresh, :])
-    if Weighted:
-        res = getLapCircularCoordinatesSigma(D, thresh, NEigs = 10)
-    else:
-        res = getLapCircularCoordinatesThresh(D, thresh, NEigs = 10)
-    [w, v, theta, A, idxs] = [res['w'], res['v'], res['theta'], res['A'], res['idxs']]
+    
+    #Do both weighted and unweighted Laplacian
+    resw = getLapCircularCoordinatesSigma(D, thresh, NEigs = 10)
+    resu = getLapCircularCoordinatesThresh(D, thresh, NEigs = 10)
+    ress = {'Weighted':resw, 'Unweighted':resu}
 
-    ##Ground truth
-    if useGroundTruth:
-        theta = np.mod(t[0:len(theta)], 2*np.pi)
-
-    tu = np.unwrap(theta)
-    if tu[-1] - tu[0] < 0:
-        tu = -tu
-    tu = tu - np.min(tu)
-    ridx = np.argsort(np.mod(tu, 2*np.pi))
-    xresort = x[ridx]
-
-    #Do denoising
[…]

### 2018-01-17 Paper/paper.tex
Wrote a little over half of the paper text now

--- 2017-12-20 Paper/paper.tex
@@
 \documentclass{article}
-\usepackage{spconf,amsmath,graphicx}
+\usepackage{spconf,amsmath,amssymb,amsfonts,amsthm,graphicx}
+\usepackage{algorithm}% http://ctan.org/pkg/algorithms
+\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
 
-% Example definitions.
-% --------------------
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
+\graphicspath{{Figures/}}
+\newcommand{\argmin}{\operatornamewithlimits{argmin}}
+\newcommand{\argmax}{\operatornamewithlimits{argmax}}
 
-% Title.
-% ------
-\title{AUTHOR GUIDELINES FOR ICIP 2018 PROCEEDINGS MANUSCRIPTS}
+\title{Synthesizing Slow Motion Periodic Videos via Circular Coordinate Reshuffling And Voting}
+
 %
@@
 %
+
 \begin{abstract}
@@
 
+\section{Introduction}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\columnwidth]{1DExample.pdf}
+\caption{An illustration of our technique on a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).
+We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.
+From this, we use the mean of the birth and death time of the largest persistence dot (row 2, column 2) to autotune the spatial bandwidth for the graph Laplacian (upper right two figures for the weighted and unweighted Laplacian), from which we derive a map to the circle (middle, right two plots).
+From this, we derive circular coordinates, which we can use to do a simple reordering (row 3 column 2) or median consensus (row 3, column 3), using interpolated votes from all windows interleaved by the coordinates (row 3, column 2).
+}
+\label{fig:ConceptFigure}
+\end{figure}
+
+In this work, we aim to find slow motion representatives for videos which have periodic motion.
+The result should loop seamlessly and to occur at a higher framerate than the captured framerate, allowing a smooth, high detail view of a single cycle of the motion.
+In the absence of a high framerate camera, recent work has shown it is possible to boost the framerate of an ordinary camera by inserting a coded aperture in front of the lens \cite{llull2013coded}.
+By contrast, in our work, we take a purely signal processing approach which avoids any specialized hardware.
+
+Our approach is {\em Eulerian}; that is, we process the video pixel by pixel with no tracking.
+Unlike Fourier-based Eulerian motion video processing tools (\cite{wu2012eulerian, wadhwa2013phase}), however, we take a {\em geometric} approach by quantifying {\em sliding window embeddings} of our videos (Section~\ref{sec:slidingwindow}).
+Sliding window embeddings of periodic time series form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data \cite{traliehigh, tralie2017quasi}.
+This implies that, at the right scale, a nearest neighbor graph built on the sliding window point cloud should be approximately a circle graph, even if the overall extrinsic geometry is quite complicated.
+Bearing this in mind, we use Laplacian eigenmaps \cite{belkin2003laplacian} of this embedding to construct maps from these point clouds to the circle, or {\em circular coordinates} (Section~\ref{sec:laplacian}).
+In particular, each sliding window is assigned a phase $\phi \in [0, 2\pi]$.
+To autotune the scale at which Laplacian eigenmaps are built, we use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} to automatically find the scale at which the most prominent loop in the data occurs.
+
+Once we have extracted a phase for each window, we use this information to reorder the content of the video.
+We also exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template (Section~\ref{sec:cyclereordering}).
+As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled periodic time series (i.e.
+single pixel grayscale video).
+There are only 12 samples per period in the original signal, so the details of each period coarse and noisy.
+However, once they are re-sorted, we get a nice, fine-detailed representation of one period.
+The extension of this technique to videos will be described in detail in Section~\ref{sec:methods}.
+
+\section{Releated Work}
+Our technique unifies many disparate ideas that have appeared before in different contexts, in addition to the references we mentioned in the introduction.
+Sliding window embeddings, or ``delay reconstructions,'' have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{schodl2000video, tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
+
+The graph Laplacian has been used to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and vector diffusion maps have been used to re-order the frames of microscope images a developing embryo \cite{dsilva2015diffusionvecordering}.
+A different topological approach with cohomology circular coordinates\cite{de2011persistent} was used to parameterize a sliding window embedding of the Lorenz attractor \cite{de2012topological} and periodic activites in motion capture data \cite{vejdemo2015cohomological}.
+Neural networks have also been trained to find circular coordinates \cite{levy2015live,anafi2017cyclops}, though this is no longer unsupervised.
+
+There has also been some related work on sliding window embeddings to synthesize ``video textures,'' or videos that repeat dynamics indefinitely \cite{schodl2000video}, and there has been work synthesizing seamless video loops by clustering pixels into different periods and adjusting them to loop through a common period \cite{Liao2013VideoLoops,Liao2015VideoLoops}.
+
+\section{Methods}
+\label{sec:methods}
+
+\begin{algorithm}[t]
+  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
+  \begin{algorithmic}[1]
+    \Procedure{ReorderVideo}{$X$, weighted, median} \\
+    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames}
+    \State $\hat{X} \gets$ 1D ISOMAP(X)
+    \State $d \gets$ fundamental period estimate of $\hat{X}$
+    \State $Y \gets SW_{d}[X[n]] \in \mathbb{R}^{WHd}$, with $M = N-d+1$ frames
+    \State Perform SVD $Y = USV^T$, $\hat{Y} \gets V^TY$
+    \State $I \gets dgm_1[\hat{Y}] = ((b_1, d_1), ... (b_k, d_k))$
+    \State $i \gets \argmax_{i}[d_i - b_i]$, $\sigma \gets b_i + \frac{1}{2}(d_i - b_i)$
+    \State $d_{ij} \gets ||\hat{Y}_i - \hat{Y}_j||_2$
+    \If {weighted}
+        \State $A_{ij} \gets e^{-d_{ij}^2/\sigma}$
+    \Else
+        \State $A_{ij} \gets \left\{ \begin{array}{cc} 1 & d_{ij} \leq \sigma \\ 0 & \text{otherwise} \end{array} \right\}$
+    \EndIf
+    \State $A_{ii} \gets 0, D_{ii} \gets \sum_{j=1}^M A_{ij}, D_{i, j \neq i} \gets 0$, $L \gets D - A$
+    \State $v_1, v_2 \gets $ adjacent eigenvectors of $L$ with fewest zero-crossings
+    \State $\theta \gets \cos^{-1}(v_2/v_1)$
+    \EndProcedure
+  \end{algorithmic}
+\end{algorithm}
+
+We now describe our algorithm in several stages.
+Throughout our discussion, we assume we are dealing with 3 channel color videos.
+For a frame resolution of $W \times H$, each frame can be thought of as a Euclidean vector in $\mathbb{R}^{W \times H \times 3}$.
+Algorithm~\ref{alg:videoreordering} shows the full algorithm.
+
+\subsection{Sliding Window Embeddings}
+\label{sec:slidingwindow}
+
+Given a $W \times H$ video $X(t) \in \mathbb{R}^{3WH}$ indexed by time, the sliding window video embedding \cite{cao1998dynamics,traliehigh,tralie2017quasi} is defined as
+
+\begin{equation}
+SW_{d, \tau}[X(t)] = \left[ \begin{array}{c} X(t) \\ X(t + \tau) \\ \vdots \\ X(t + (d-1)\tau)  \in \mathbb{R}^{3WHd} \end{array} \right]
+\end{equation}
+
+where $\tau$ is a step size and $d$ is the dimension of the embedding.
+In this work, we fix $\tau = 1$ for simplicity and drop $\tau$ in the subscript, and we also sample times $t$ only at integer frame indices.
+In theory, a sliding window embedding of a single generic observation function of a dynamical system of intrinsic dimension $m$ can be reconstructed \cite{takens1981detecting}.
+Talk about fundamental frequency estimation \cite{Mcleod05asmarter}
+
+\subsection{Laplacian Eigenmaps And Persistent Homology}
+\label{sec:laplacian}
+
+which means the first two nonzero eigenvectors should be a sine and cosine, or orthogonal linear combinations therein.
+When plotted against each other, they make an approximate circle, and the arctangent of the two eigenvector coordinates at every window can be used to determine the {\em phase} of the corresponding window in the periodic signal.
+The first sample of each window can then be re-sorted by phase.
+
+Talk about autotuning with peristent homology, mention that it's the opposite of the approach in \cite{bendich2011improving}.
+
+\subsection{Cycle Reordering}
+\label{sec:cyclereordering}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.8\columnwidth]{XTSlice.pdf}
+\caption{An XT slice of a line of pixels (magenta line, upper left) over time for the original video and for reordered videos with and without median consensus.}
+\label{fig:XTSlice}
+\end{figure}
+
+Figure~\ref{fig:XTSlice} shows the difference between a simple reordering and a median consensus reordering.
+Due to natural variation from cycle to cycle, the simple reordering has many temporal discontinuities when interleaving these cycles.
+By contrast, the median voting is clean, and it has the added benefit of removing nonperiodic background components.
+
+\subsection{Sharpening Postprocessing}
+
+The results of the median recycling are smooth and qualitatively similar to the results in the ``motion denoising'' work by the authors of \cite{rubinstein2011motion} on time lapse videos, though both results tend to be slightly blurry.
+
+\section{Experiments}
+
+Robustness experiments, jumping jacks 2 men, two exercise videos from \cite{levy2015live}, beating heart videos from \cite{traliehigh}, \cite{wu2012eulerian}, and \cite{wadhwa2013phase}.
+
+\section{Discussion}
+
+Since we rely on the theory and constructions in \cite{tralie2017quasi}, we are subject to similar constraints in the allowable motion and drift for our method to work well.
+We note that Eulerian video magnification also degrades in the presence of too much drift \cite{wu2012eulerian, wadhwa2013phase}.
+
 % References should be produced using the bibtex program from suitable

### 2018-01-17 Paper/Figures/convertSVGs.py

@@ -1,0 +1,7 @@
+import glob
+import subprocess
+
+if __name__ == '__main__':
+    for f in glob.glob("*.svg"):
+        fnew = f[0:-4] + ".pdf"
+        subprocess.call(["inkscape", "-D", "-z", "--file=%s"%f, "--export-pdf=%s"%fnew])

### 2018-01-17 PaperFigures.py

@@ -2,13 +2,21 @@ import numpy as np
 import matplotlib.pyplot as plt
 import scipy.io as sio
 import scipy.interpolate as interp
+from VideoTools import *
 from VideoReordering import *
 from Laplacian import *
 from CSMSSMTools import *
 from FundamentalFreq import *
 from sklearn.decomposition import PCA
 from ripser import ripser
-from mpl_toolkits.mplot3d import Axes3D
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+
+def makeColorbar(dim1 = 1, dim2 = 3, k = 3):
+    plt.subplot(dim1, dim2, k)
+    ax = plt.gca()
+    divider = make_axes_locatable(ax)
+    cax = divider.append_axes("right", size="5%", pad = 0.05)
+    plt.colorbar(cax = cax)
 
 def drawLineColored(idx, x, C, linewidth = 1):
     plt.hold(True)
@@ -67,16 +75,16 @@ def ReorderingExample1D(seed):
     I = Is[1]
     thresh = np.argmax(I[:, 1] - I[:, 0])
     thresh = np.mean(I[thresh, :])
-    
+
     #Do both weighted and unweighted Laplacian
     resw = getLapCircularCoordinatesSigma(D, thresh, NEigs = 10)
     resu = getLapCircularCoordinatesThresh(D, thresh, NEigs = 10)
     ress = {'Weighted':resw, 'Unweighted':resu}
 
     fres = 3
-    fig = plt.figure(figsize=(fres*5, fres*3))
+    fig = plt.figure(figsize=(fres*4, fres*3.2))
     ylims = np.array([-3.5, 3.5])
-    plt.subplot(3, 5, 1)
+    plt.subplot2grid((3, 4), (0, 0), colspan = 2)
     drawLineColored(np.arange(len(x)), x, C[xidx, :])
     plt.plot([0, 0], ylims*0.9, 'w')
     plt.plot([dim-1]*2, ylims*0.9, 'w')
@@ -86,17 +94,17 @@ def ReorderingExample1D(seed):
     plotbgcolor = (0.15, 0.15, 0.15)
     ax.set_axis_bgcolor(plotbgcolor)
     plt.ylim(ylims)
-    plt.title("Original Signal, Sliding Window d = %i"%dim)
+    plt.title("$f(t) = \\cos(t 2\\pi/12) + \\cos(t 2\\pi/4) + \\cos(r 10\\pi/12) + 0.6n_t$")
[…]

### 2018-01-17 Paper/paper.tex
Finishing up pseudocode

@@
 \begin{algorithm}[t]
-  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
+    \caption{Laplacian Circular Coordinates}
     \begin{algorithmic}[1]
-    \Procedure{ReorderVideo}{$X$, weighted, median} \\
-    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames}
-    \State $\hat{X} \gets$ 1D ISOMAP(X)
-    \State $d \gets$ fundamental period estimate of $\hat{X}$
-    \State $Y \gets SW_{d}[X[n]] \in \mathbb{R}^{WHd}$, with $M = N-d+1$ frames
-    \State Perform SVD $Y = USV^T$, $\hat{Y} \gets V^TY$
-    \State $I \gets dgm_1[\hat{Y}] = ((b_1, d_1), ... (b_k, d_k))$
+    \Procedure{CircCoords}{$X$, $L$}
+    \State $\hat{X} \gets $ image pyramid level $L$ of $X$
+    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{N \times N}$
+    \State $y \gets$ 1D ISOMAP($Y$)
+    \State $d \gets$ fundamental period estimate of $y$
+    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times Nd}$, $M = N-d+1$
+
+    \State $I \gets dgm_1[Z] = ((b_1, d_1), ... (b_k, d_k))$
     \State $i \gets \argmax_{i}[d_i - b_i]$, $\sigma \gets b_i + \frac{1}{2}(d_i - b_i)$
-    \State $d_{ij} \gets ||\hat{Y}_i - \hat{Y}_j||_2$
+    \State $d_{ij} \gets ||Z_i - Z_j||_2$
     \If {weighted}
@@
     \State $A_{ii} \gets 0, D_{ii} \gets \sum_{j=1}^M A_{ij}, D_{i, j \neq i} \gets 0$, $L \gets D - A$
-    \State $v_1, v_2 \gets $ adjacent eigenvectors of $L$ with fewest zero-crossings
-    \State $\theta \gets \cos^{-1}(v_2/v_1)$
+    \State $v_1, v_2 \gets $ adjacent eigenvectors of $L$ with fewest zcs
+    \State $\theta \gets \cos^{-1}(v_2/v_1)$\\
+    \Return ($\theta$, d)
+    \EndProcedure
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[t]
+  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
+  \begin{algorithmic}[1]
+    \Procedure{ReorderVideo}{$X$, $L$, weighted, median} \\
+    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames, an $N \times 3WH$ matrix}
+    \State ($\theta, d) \gets$ CIRCCOORDS($X, L$)
+    \State Perform SVD $X = USV^T$, $\hat{X} \gets US$
+    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times Nd}$, $M = N-d+1$
+    \If {median}
+        \State Order $\hat{Y}$ by $\theta$, line up each window in time, and linearly interpolate coordinates of $\hat{Y}$
+        \State Do median consensus on aligned pixels of $\hat{Y}V^T$ \label{algline:medianconsensus}
+    \Else
+        \State Order first frames in each window by $\theta$
+    \EndIf
     \EndProcedure
@@
 In this work, we fix $\tau = 1$ for simplicity and drop $\tau$ in the subscript, and we also sample times $t$ only at integer frame indices.
-In theory, a sliding window embedding of a single generic observation function of a dynamical system of intrinsic dimension $m$ can be reconstructed \cite{takens1981detecting}.
+In theory, a sliding window of dimension $2m+1$ of a single generic observation function of a dynamical system of intrinsic dimension $m$ is a topological embedding of the original state space \cite{takens1981detecting}.
+
 Talk about fundamental frequency estimation \cite{Mcleod05asmarter}
@@
 
+Advantage of Eulerian is that everything is linear (can use SVD to compress)
+
+Interpolated windows can be projected back to pixel space one by one to save memory (Line~\ref{algline:medianconsensus} of Algorithm~\ref{alg:videoreordering})
+
 \subsection{Sharpening Postprocessing}

### 2018-01-17 VideoReordering.py
current version

@@ -269,6 +269,6 @@ if __name__ == '__main__':
     print('I shape:',I.shape,'I feat shape:',I_feat.shape)
     #(I, IDims) = getCircleRotatingVideo()
     #saveVideo(I, IDims, "circle.avi")
-    XNew = reorderVideo(I, I_feat, derivWin = 2, Weighted = opt.weighted_laplacian, doSimple = (not opt.median_reorder), doPlot = False, Verbose = True)
+    XNew = reorderVideo(I, I_feat, derivWin = 0, Weighted = opt.weighted_laplacian, doSimple = (not opt.median_reorder), doPlot = False, Verbose = True)
     saveVideo(XNew, IDims, get_out_filename('reordered', (not opt.median_reorder), opt.weighted_laplacian, opt.net_feat, opt.pyr_level, opt.net_depth))
     #saveFrames(XNew, IDims)

### 2018-01-17 Paper/paper.tex

@@
 Sliding window embeddings, or ``delay reconstructions,'' have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{schodl2000video, tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
-
-The graph Laplacian has been used to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and vector diffusion maps have been used to re-order the frames of microscope images a developing embryo \cite{dsilva2015diffusionvecordering}.
+All of these works focus on analysis rather than synthesis, as we do, but there has been work using sliding window embeddings to synthesize ``video textures,'' or videos that repeat dynamics indefinitely \cite{schodl2000video}, which are similar in spirit to our infinitely looping periodic representatives.
+The graph Laplacian, on the other hand, has been used to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and vector diffusion maps have been used to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.
 A different topological approach with cohomology circular coordinates\cite{de2011persistent} was used to parameterize a sliding window embedding of the Lorenz attractor \cite{de2012topological} and periodic activites in motion capture data \cite{vejdemo2015cohomological}.
-Neural networks have also been trained to find circular coordinates \cite{levy2015live,anafi2017cyclops}, though this is no longer unsupervised.
-
-There has also been some related work on sliding window embeddings to synthesize ``video textures,'' or videos that repeat dynamics indefinitely \cite{schodl2000video}, and there has been work synthesizing seamless video loops by clustering pixels into different periods and adjusting them to loop through a common period \cite{Liao2013VideoLoops,Liao2015VideoLoops}.
+Neural networks have also been trained to find circular coordinates \cite{levy2015live,anafi2017cyclops}.
+Finally, perhaps the most related to our goal is work synthesizing seamless video loops by clustering pixels into different periods and adjusting them to loop through a common period \cite{Liao2013VideoLoops,Liao2015VideoLoops}.
+TODO: talk about applications of TDA?
 
@@
 \label{sec:methods}
+
+\begin{algorithm}[t]
+  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
+  \begin{algorithmic}[1]
+    \Procedure{ReorderVideo}{$X$, $L$, weighted, median} \\
+    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames, an $N \times 3WH$ matrix}
+    \State ($\theta, d) \gets$ CIRCCOORDS($X, L$)
+    \State Perform SVD $X = USV^T$, $\hat{X} \gets US \in \mathbb{R}^{N \times (N-1)}$
+    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times (N-1)d}$, $M = N-d+1$
+    \If {median}
+        \State Order $\hat{Y}$ by $\theta$, line up each window in time, and linearly interpolate coordinates of $\hat{Y}$
+        \State Do median consensus on aligned pixels of $\hat{Y}V^T$ \label{algline:medianconsensus}
+    \Else
+        \State Order first frames in each window by $\theta$
+    \EndIf
+    \EndProcedure
+  \end{algorithmic}
+\end{algorithm}
 
@@
     \State $\hat{X} \gets $ image pyramid level $L$ of $X$
-    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{N \times N}$
-    \State $y \gets$ 1D ISOMAP($Y$)
-    \State $d \gets$ fundamental period estimate of $y$
-    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times Nd}$, $M = N-d+1$
+    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{R}^{N \times (N-1)}$
+    \State $y \gets$ 1D ISOMAP($Y$) \cite{tenenbaum2000global}
+    \State $d \gets$ fundamental period estimate of $y$ \cite{Mcleod05asmarter}
+    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times (N-1)d}$, $M = N-d+1$
 
@@
 
-\begin{algorithm}[t]
-  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
-  \begin{algorithmic}[1]
-    \Procedure{ReorderVideo}{$X$, $L$, weighted, median} \\
-    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames, an $N \times 3WH$ matrix}
-    \State ($\theta, d) \gets$ CIRCCOORDS($X, L$)
-    \State Perform SVD $X = USV^T$, $\hat{X} \gets US$
-    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times Nd}$, $M = N-d+1$
-    \If {median}
-        \State Order $\hat{Y}$ by $\theta$, line up each window in time, and linearly interpolate coordinates of $\hat{Y}$
-        \State Do median consensus on aligned pixels of $\hat{Y}V^T$ \label{algline:medianconsensus}
-    \Else
-        \State Order first frames in each window by $\theta$
-    \EndIf
-    \EndProcedure
-  \end{algorithmic}
-\end{algorithm}
-
 We now describe our algorithm in several stages.
@@
 For a frame resolution of $W \times H$, each frame can be thought of as a Euclidean vector in $\mathbb{R}^{W \times H \times 3}$.
-Algorithm~\ref{alg:videoreordering} shows the full algorithm.
+Algorithm~\ref{alg:videoreordering} shows the full details of our method in pseudocode.
 
@@
 In this work, we fix $\tau = 1$ for simplicity and drop $\tau$ in the subscript, and we also sample times $t$ only at integer frame indices.
-In theory, a sliding window of dimension $2m+1$ of a single generic observation function of a dynamical system of intrinsic dimension $m$ is a topological embedding of the original state space \cite{takens1981detecting}.
-
-Talk about fundamental frequency estimation \cite{Mcleod05asmarter}
+As shown by Takens \cite{takens1981detecting}, a sliding window of dimension $d = 2m+1$ of even a single generic observation function (time series) of a dynamical system of intrinsic dimension $m$ is sufficient to reconstruct a topological embedding of the underlying trajectory in the original state space.
+For periodic signals, this state space is a torus, and $d$ should be twice the number of harmonics present to injectively reconstruct loops on that torus \cite{perea2015sliding}.
+The same is true of videos in general \cite{tralie2017quasi}.
+Furthermore, the sliding window length $(d-1) \tau$, or simply $d-1$ in our case, maximizes the roundness of the embeddings when $d-1 = k T$ for some integer $k$, where $T$ is the fundamental period.
+Since we use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that we tune our window size to be an integer multiple of the period.
+To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D ``surrogate signal,'' and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $d$.
+This is quite similar to the diffusion maps + autocorrelation approach in \cite{tralie2017quasi} for analyzing periodic videos.
+This estimation often returns multiples of the fundamental period, which is fine for our purposes.
 

### 2018-01-17 Paper/paper.tex
Committing more changes

@@
     \State ($\theta, d) \gets$ CIRCCOORDS($X, L$)
-    \State Perform SVD $X = USV^T$, $\hat{X} \gets US \in \mathbb{R}^{N \times (N-1)}$
-    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times (N-1)d}$, $M = N-d+1$
+    \State Perform SVD $X = USV^T$, $\hat{X} \gets US \in \mathbb{R}^{N \times N}$
+    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times N \times d}$, $M = N-d+1$
     \If {median}
@@
     \State $\hat{X} \gets $ image pyramid level $L$ of $X$
-    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{R}^{N \times (N-1)}$
+    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{R}^{N \times N}$
     \State $y \gets$ 1D ISOMAP($Y$) \cite{tenenbaum2000global}
     \State $d \gets$ fundamental period estimate of $y$ \cite{Mcleod05asmarter}
-    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times (N-1)d}$, $M = N-d+1$
+    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times N \times d}$, $M = N-d+1$
 
@@
 For a frame resolution of $W \times H$, each frame can be thought of as a Euclidean vector in $\mathbb{R}^{W \times H \times 3}$.
+For a video with $N$ frames, we flatten each frame to a 1D vector and stack them row wise along an $N \times 3WH$ matrix $X$.
+Whenever we perform a linear operation on all of the pixels at once, we can use the SVD $X = USV^T$ to reduce memory and computational costs by working with $US$ in place of $X$, which is in $N$ dimensions instead of $3WH \gg N$ (similar processing was done in \cite{turk1991eigenfaces} and \cite{tralie2017quasi}).
+The only nonlinear operation is the median operation (Section~\ref{sec:cyclereordering}), and we project back into pixel space using $V^T$ before taking the median.
 Algorithm~\ref{alg:videoreordering} shows the full details of our method in pseudocode.
@@
 \begin{equation}
-SW_{d, \tau}[X(t)] = \left[ \begin{array}{c} X(t) \\ X(t + \tau) \\ \vdots \\ X(t + (d-1)\tau)  \in \mathbb{R}^{3WHd} \end{array} \right]
+SW_{d, \tau}[X(t)] = \left[ \begin{array}{c} X(t) \\ X(t + \tau) \\ \vdots \\ X(t + (d-1)\tau)  \end{array} \right] \in \mathbb{R}^{3WHd}
 \end{equation}
@@
 
-\subsection{Cycle Reordering}
+\subsection{Cycle Reordering And Median Voting}
 \label{sec:cyclereordering}

### 2018-01-20 Paper/paper.tex
Working intro a bit

@@
 
-\title{Synthesizing Slow Motion Periodic Videos via Circular Coordinate Reshuffling And Voting}
+\title{Eulerian Synthesis of Slow Motion Periodic Videos}
 
@@
 
-In this work, we aim to find slow motion representatives for videos which have periodic motion.
-The result should loop seamlessly and to occur at a higher framerate than the captured framerate, allowing a smooth, high detail view of a single cycle of the motion.
-In the absence of a high framerate camera, recent work has shown it is possible to boost the framerate of an ordinary camera by inserting a coded aperture in front of the lens \cite{llull2013coded}.
-By contrast, in our work, we take a purely signal processing approach which avoids any specialized hardware.
+Repetitive, periodic motions are ubiquitous in our world, such as animal locomotion (walking/flapping/slithering/swimming), mechanical motions (wheels spinning, pistons oscillating), biological rhythms (heartbeat, breathing), musical rhythms (drumming, feet tapping), etc.
+In this work, we consider videos of periodic motion.
+One avenue of interest is to analyze these videos in fine detail, such as for characterizing subtle progressions of blood flow in the face during a heartbeat for medical diagnostic purposes.
+It may also be important to understand and visualize variations from cycle to cycle, such as in a repetitive automated action on an assembly line, where too much variation could indicate the onset of failure, or in athletic activities for optimizing performance.
 
@@
 
-The results of the median recycling are smooth and qualitatively similar to the results in the ``motion denoising'' work by the authors of \cite{rubinstein2011motion} on time lapse videos, though both results tend to be slightly blurry.
+The results of the median reordering can be blurry
 

### 2018-01-22 Paper/paper.tex
New block diagram, starting to work on robustness experiments

@@
 \usepackage{spconf,amsmath,amssymb,amsfonts,amsthm,graphicx}
-\usepackage{algorithm}% http://ctan.org/pkg/algorithms
-\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
 
@@
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width=\columnwidth]{1DExample.pdf}
-\caption{An illustration of our technique on a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).
-We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.
-From this, we use the mean of the birth and death time of the largest persistence dot (row 2, column 2) to autotune the spatial bandwidth for the graph Laplacian (upper right two figures for the weighted and unweighted Laplacian), from which we derive a map to the circle (middle, right two plots).
-From this, we derive circular coordinates, which we can use to do a simple reordering (row 3 column 2) or median consensus (row 3, column 3), using interpolated votes from all windows interleaved by the coordinates (row 3, column 2).
-}
-\label{fig:ConceptFigure}
-\end{figure}
-
 Repetitive, periodic motions are ubiquitous in our world, such as animal locomotion (walking/flapping/slithering/swimming), mechanical motions (wheels spinning, pistons oscillating), biological rhythms (heartbeat, breathing), musical rhythms (drumming, feet tapping), etc.
@@
 
-\begin{algorithm}[t]
-  \caption{Sliding Window Video Loops}\label{alg:videoreordering}
-  \begin{algorithmic}[1]
-    \Procedure{ReorderVideo}{$X$, $L$, weighted, median} \\
-    \Comment{$X$ is a $W \times H$ video $X$ with $N$ frames, an $N \times 3WH$ matrix}
-    \State ($\theta, d) \gets$ CIRCCOORDS($X, L$)
-    \State Perform SVD $X = USV^T$, $\hat{X} \gets US \in \mathbb{R}^{N \times N}$
-    \State $\hat{Y} \gets SW_d[\hat{X}[n]] \in \mathbb{R}^{M \times N \times d}$, $M = N-d+1$
-    \If {median}
-        \State Order $\hat{Y}$ by $\theta$, line up each window in time, and linearly interpolate coordinates of $\hat{Y}$
-        \State Do median consensus on aligned pixels of $\hat{Y}V^T$ \label{algline:medianconsensus}
-    \Else
-        \State Order first frames in each window by $\theta$
-    \EndIf
-    \EndProcedure
-  \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[t]
-    \caption{Laplacian Circular Coordinates}
-    \begin{algorithmic}[1]
-    \Procedure{CircCoords}{$X$, $L$}
-    \State $\hat{X} \gets $ image pyramid level $L$ of $X$
-    \State Perform SVD $\hat{X} = USV^T$, $Y \gets US \in \mathbb{R}^{N \times N}$
-    \State $y \gets$ 1D ISOMAP($Y$) \cite{tenenbaum2000global}
-    \State $d \gets$ fundamental period estimate of $y$ \cite{Mcleod05asmarter}
-    \State $Z \gets SW_{d}[Y[n]] \in \mathbb{R}^{M \times N \times d}$, $M = N-d+1$
-
-    \State $I \gets dgm_1[Z] = ((b_1, d_1), ... (b_k, d_k))$
-    \State $i \gets \argmax_{i}[d_i - b_i]$, $\sigma \gets b_i + \frac{1}{2}(d_i - b_i)$
-    \State $d_{ij} \gets ||Z_i - Z_j||_2$
-    \If {weighted}
-        \State $A_{ij} \gets e^{-d_{ij}^2/\sigma}$
-    \Else
-        \State $A_{ij} \gets \left\{ \begin{array}{cc} 1 & d_{ij} \leq \sigma \\ 0 & \text{otherwise} \end{array} \right\}$
-    \EndIf
-    \State $A_{ii} \gets 0, D_{ii} \gets \sum_{j=1}^M A_{ij}, D_{i, j \neq i} \gets 0$, $L \gets D - A$
-    \State $v_1, v_2 \gets $ adjacent eigenvectors of $L$ with fewest zcs
-    \State $\theta \gets \cos^{-1}(v_2/v_1)$\\
-    \Return ($\theta$, d)
-    \EndProcedure
-  \end{algorithmic}
-\end{algorithm}
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{BlockDiagram.pdf}
+\caption{An block diagram of our technique, illustrated by a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).
+We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.
+From this, we use the mean of the birth and death time of the largest persistence dot to autotune the scale $\sigma$ for the graph Laplacian, from which we derive circular coordinates $\sigma$, which can be used to reorder the sliding windows and use them to vote on a final slow motion template.}
+\label{fig:ConceptFigure}
+\end{figure*}
 

### 2018-01-22 FundamentalFreq.py

@@ -62,7 +62,7 @@ def estimateFundamentalFreq(x, shortBias = 0.1, doPlot = False):
         plt.scatter(maxidx, corr[maxidx])
         plt.scatter([maxTau], [corr[maxTau]], 100, 'r')
         plt.title("Max Tau = %i, Clarity = %g"%(maxTau, corr[maxTau]))
-    return (maxTau, corr)
+    return {'maxTau':maxTau, 'corr':corr, 'maxidx':maxidx}
 
 if __name__ == '__main__':
     T = 60

### 2018-01-22 Laplacian.py

@@ -124,6 +124,35 @@ def getLapCircularCoordinatesThresh(pD, thresh, NEigs = 20, doPlot = False):
     (theta, thetau) = getLapThetas(v, 1, 2)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
 
+def getLapCircularCoordinatesKNN(D, Kappa, NEigs = 20, doPlot = False):
+    """
+    Get circular coordinates using a weighted laplacian 
+    :param pD: Distance matrix
+    :param Kappa: Percentage of mutual nearest neighbors
+    :param NEigs: Maximum number of eigenvectors to compute
+    :return {'w':eigenvalues, 'v':eigenvectors, 'theta':Circular coordinates,\
+            'thetau':Unwrapped circular coordinates, 'A':Adjacency matrix}
+    """
+    A = CSMToBinaryMutual(D, Kappa)
+    np.fill_diagonal(A, 0)
+    NEigs = min(NEigs, A.shape[0])
+    (w, v, L) = getLaplacianEigsDense(A, NEigs)
+    (i1, zcs) = getSlowestEigenvectorIdx(v)
+    if doPlot:
+        plt.subplot(311)
+        plt.imshow(v, cmap = 'afmhot', interpolation = 'nearest', aspect = 'auto')
+        plt.xlim([0, v.shape[1]])
+        plt.title("Eigenvectors")
+        plt.subplot(312)
+        plt.plot(zcs)
+        plt.title("Zero Crossings, Smallest = (%i, %i)"%(i1, i1+1))
+        plt.xlim([0, v.shape[1]])
+        plt.subplot(313)
+        plt.plot(v[:, [i1, i1+1]])
+        plt.legend(["%i"%i1, "%i"%(i1+1)])
+    (theta, thetau) = getLapThetas(v, i1, i1+1)
+    return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
+
 def getLineLaplacian(NPoints):
     I = np.arange(NPoints-1).tolist()
     J = np.arange(NPoints-1)

### 2018-01-22 VideoReordering.py

@@ -11,6 +11,7 @@ import matplotlib.image as mpimage
 import scipy.sparse as sparse
 import scipy.interpolate as interp
 from sklearn import manifold
+import time
 
 import argparse
 
@@ -32,7 +33,7 @@ parser.set_defaults(net_feat=False)
 
 opt = parser.parse_args()
 
-def getReorderedConsensus1D(X, N, theta, doPlot = False):
+def getReorderedConsensus1D(X, N, thetau, doPlot = False):
     """
     Given an array of sliding windows and circular coordinates,
     reorder the sliding windows to go through one period
@@ -42,7 +43,7 @@ def getReorderedConsensus1D(X, N, theta, doPlot = False):
     each window
     :param X: An Mxd array of windows
     :param N: The original signal length
-    :param theta: The circular coordinates
+    :param theta: The unwrapped, increasing circular coordinates
     :param doPlot: Whether to make a plot showing all of the windows
     :return z: An N-length 1D consensus signal going through one period
     """
@@ -50,14 +51,10 @@ def getReorderedConsensus1D(X, N, theta, doPlot = False):
     #goes through
     M = X.shape[0]
     d = X.shape[1]
-    tu = np.unwrap(theta)
-    if tu[-1] - tu[0] < 0:
-        tu = -tu
-    tu = tu - np.min(tu)
-    NPeriods = (float(N)/M)*np.max(tu)/(2*np.pi)
+    NPeriods = (float(N)/M)*np.max(thetau)/(2*np.pi)
     print("NPeriods = %g"%NPeriods)
     print("N/NPeriods = %g"%(float(N)/NPeriods))
-    tu = N*np.mod(tu, 2*np.pi)/(2*np.pi)
+    tu = N*np.mod(thetau, 2*np.pi)/(2*np.pi)
     tidx = np.argsort(tu)
     X2 = X[tidx, :]
     t1 = tu[tidx]
@@ -90,7 +87,7 @@ def getReorderedConsensus1D(X, N, theta, doPlot = False):
         plt.show()
     return (Z, np.nanmedian(Z, 0), tidx)
 
-def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, theta, doPlot = False, Verbose = False, lookAtVotes = False):
+def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, thetau, doPlot = False, Verbose = False, lookAtVotes = False):
     """
     Given an array of sliding window videos and circular coordinates,
[…]

### 2018-01-22 VideoTools.py

@@ -393,6 +393,97 @@ def getGradientVideo(I, IDims, sigma = 1):
         GV[i, :] = F.flatten()
     return GV
 
+def makeRandomWalkCurve(res, NPoints, dim):
+    #Enumerate all neighbors in hypercube via base 3 counting between [-1, 0, 1]
+    Neighbs = np.zeros((3**dim, dim))
+    Neighbs[0, :] = -np.ones((1, dim))
+    idx = 1
+    for ii in range(1, 3**dim):
+        N = np.copy(Neighbs[idx-1, :])
+        N[0] += 1
+        for kk in range(dim):
+            if N[kk] > 1:
+                N[kk] = -1
+                N[kk+1] += 1
+        Neighbs[idx, :] = N
+        idx += 1
+    #Exclude the neighbor that's in the same place
+    Neighbs = Neighbs[np.sum(np.abs(Neighbs), 1) > 0, :]
+
+    #Pick a random starting point
+    X = np.zeros((NPoints, dim))
+    X[0, :] = np.random.choice(res, dim)
+    
+    #Trace out a random path
+    for ii in range(1, NPoints):
+        prev = np.copy(X[ii-1, :])
+        N = np.tile(prev, (Neighbs.shape[0], 1)) + Neighbs
+        #Pick a random next point that is in bounds
+        idx = np.sum(N > 0, 1) + np.sum(N < res, 1)
+        N = N[idx == 2*dim, :]
+        X[ii, :] = N[np.random.choice(N.shape[0], 1), :]
+    return X
+
+def smoothCurve(X, Fac):
+    import scipy.interpolate as interp
+    NPoints = X.shape[0]
+    dim = X.shape[1]
+    idx = range(NPoints)
+    idxx = np.linspace(0, NPoints, NPoints*Fac)
+    Y = np.zeros((NPoints*Fac, dim))
+    NPointsOut = 0
+    for ii in range(dim):
+        Y[:, ii] = interp.spline(idx, X[:, ii], idxx)
+        #Smooth with box filter
+        y = (0.5/Fac)*np.convolve(Y[:, ii], np.ones(Fac*2), mode='same')
+        Y[0:len(y), ii] = y
+        NPointsOut = len(y)
+    Y = Y[0:NPointsOut-1, :]
+    Y = Y[2*Fac:-2*Fac, :]
[…]

### 2018-01-22 Paper/paper.tex
Whoops

@@
 We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.
-From this, we use the mean of the birth and death time of the largest persistence dot to autotune the scale $\sigma$ for the graph Laplacian, from which we derive circular coordinates $\sigma$, which can be used to reorder the sliding windows and use them to vote on a final slow motion template.}
+From this, we use the mean of the birth and death time of the largest persistence dot to autotune the scale $\sigma$ for the graph Laplacian, from which we derive circular coordinates $\phi$, which can be used to reorder the sliding windows and use them to vote on a final slow motion template.}
 \label{fig:ConceptFigure}

### 2018-01-22 VideoReordering.py
bug with resnet

@@ -345,7 +345,7 @@ if __name__ == '__main__':
     #(I, IDims) = getCircleRotatingVideo()
     #saveVideo(I, IDims, "circle.avi")
     fileprefix = get_out_fileprefix('reordered', opt.filename, (not opt.median_reorder), opt.weighted_laplacian, opt.net_feat, opt.pyr_level, opt.net_depth)
-    XNew = reorderVideo(I, I_feat, IDims, derivWin = 2, Weighted = opt.weighted_laplacian, \
+    XNew = reorderVideo(I, I_feat, IDims, derivWin = 0, Weighted = opt.weighted_laplacian, \
                         doSimple = (not opt.median_reorder), doPlot = opt.doPlot, Verbose = True, \
                         doImageAnalogies = opt.image_analogies, fileprefix = fileprefix)
     saveVideo(XNew, IDims, fileprefix+".avi")

### 2018-01-22 VideoTools.py

@@ -178,6 +178,7 @@ def loadVideoResNetFeats(path, depth=0):
         print('unknown depth?',depth)
         shallow_layers = ['conv1','bn1','relu','maxpool']
     net = models.__dict__['resnet18'](pretrained=True)
+    net.eval()
     resnet_module = net.modules().__next__()
     resnet_modules = resnet_module.named_children()
     shallow_nn = []

### 2018-01-23 Laplacian.py
Finished code for batch cluster robustness tests

@@ -153,6 +153,38 @@ def getLapCircularCoordinatesKNN(D, Kappa, NEigs = 20, doPlot = False):
     (theta, thetau) = getLapThetas(v, i1, i1+1)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
 
+def getLapCircularCoordinatesKNNWeighted(D, Kappa, NEigs = 20, doPlot = False):
+    """
+    Get circular coordinates using a weighted laplacian 
+    :param pD: Distance matrix
+    :param Kappa: Percentage of mutual nearest neighbors
+    :param NEigs: Maximum number of eigenvectors to compute
+    :return {'w':eigenvalues, 'v':eigenvectors, 'theta':Circular coordinates,\
+            'thetau':Unwrapped circular coordinates, 'A':Adjacency matrix}
+    """
+    K = int(Kappa*D.shape[0])
+    dNN = np.mean(np.sort(D, 1)[:, 0:K], 1)
+    sigma = 0.5*(dNN[:, None] + dNN[None, :])
+    A = np.exp(-D*D/(sigma))
+    np.fill_diagonal(A, 0)
+    NEigs = min(NEigs, A.shape[0])
+    (w, v, L) = getLaplacianEigsDense(A, NEigs)
+    (i1, zcs) = getSlowestEigenvectorIdx(v)
+    if doPlot:
+        plt.subplot(311)
+        plt.imshow(v, cmap = 'afmhot', interpolation = 'nearest', aspect = 'auto')
+        plt.xlim([0, v.shape[1]])
+        plt.title("Eigenvectors")
+        plt.subplot(312)
+        plt.plot(zcs)
+        plt.title("Zero Crossings, Smallest = (%i, %i)"%(i1, i1+1))
+        plt.xlim([0, v.shape[1]])
+        plt.subplot(313)
+        plt.plot(v[:, [i1, i1+1]])
+        plt.legend(["%i"%i1, "%i"%(i1+1)])
+    (theta, thetau) = getLapThetas(v, i1, i1+1)
+    return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
+
 def getLineLaplacian(NPoints):
     I = np.arange(NPoints-1).tolist()
     J = np.arange(NPoints-1)

### 2018-01-23 RobustnessTests.py

@@ -2,6 +2,8 @@ from VideoTools import *
 from VideoReordering import *
 import numpy as np
 import matplotlib.pyplot as plt
+import scipy.io as sio
+import argparse
 
 def getVideoPyramid(I, IDims, pyr_level):
     """
@@ -18,62 +20,127 @@ def getVideoPyramid(I, IDims, pyr_level):
         IRet.append(feat_frame.flatten())
     return np.array(IRet)
 
-def getKendallTau(order1, order2):
+def getCircleDist(x, y):
+    return np.minimum(np.abs(x - y), 2*np.pi-np.abs(x - y))
+
+def getKendallTauCircle(rank1, rank2):
     """
     Given two global rankings, return the Kendall Tau Score
+    on the circle
     """
-    N = len(order1)
-    rank1 = np.zeros(N)
-    rank1[order1] = np.arange(N)
-    rank2 = np.zeros(N)
-    rank2[order2] = np.arange(N)
-    A = np.sign(rank1[None, :] - rank1[:, None])
-    B = np.sign(rank2[None, :] - rank2[:, None])
+    N = len(rank1)
+    diff = rank1[None, :] - rank1[:, None]
+    A = np.sign(diff)
+    A[np.abs(A) > np.pi] *= -1 #Wrap around
+    diff = rank2[None, :] - rank2[:, None]
+    B = np.sign(diff)
+    B[np.abs(B) > np.pi] *= -1
     return np.sum(A*B)/float(N*(N-1))
 
-def getCycles(NCycles, NFinal):
-    I, I_feat, IDims = loadImageIOVideo('Videos/SlowMotionTemplate.avi')
+def getCycles(NCycles, NFinal, filename):
+    I, I_feat, IDims = loadImageIOVideo(filename)
     N = I.shape[0]
     theta = np.linspace(0, 2*np.pi, N)
     idx = np.mod(NCycles*np.arange(N), N)
     if NFinal == -1:
         NFinal = N
-    idx = idx[0:NFinal]
+    starti = np.random.randint(len(idx)-NFinal)
+    idx = idx[starti:starti+NFinal]
     theta = theta[idx]
+    theta = np.unwrap(theta)
+    theta = theta - np.min(theta)
+    theta = np.mod(theta, 2*np.pi)
     return {'I':I[idx, :], 'IDims':IDims, 'idx':idx, 'theta':theta}
 
-def doTest():
[…]

### 2018-01-23 VideoReordering.py

@@ -12,26 +12,7 @@ import scipy.sparse as sparse
 import scipy.interpolate as interp
 from sklearn import manifold
 import time
-
 import argparse
-
-parser = argparse.ArgumentParser()
-parser.add_argument('--show-plots', dest='doPlot', action='store_true', help='Show plots of circular coordinates')
-parser.add_argument('--do-image-analogies', dest='image_analogies', action='store_true', help='use image analogies to sharpen')
-parser.add_argument('--is-median-reorder', dest='median_reorder', action='store_true', help='enable median reordering')
-parser.add_argument('--is-simple-reorder', dest='median_reorder', action='store_false', help='enable simple reordering')
-parser.add_argument('--is-weighted-laplacian', dest='weighted_laplacian', action='store_true', help='enable weighted laplacian')
-parser.add_argument('--is-unweighted-laplacian', dest='weighted_laplacian', action='store_false', help='enable unweighted laplacian')
-parser.add_argument('--is-net-feat', dest='net_feat', action='store_true', help='enable resnet features')
-parser.add_argument('--is-pyr-feat', dest='net_feat', action='store_false', help='enable gaussian pyramid features')
-parser.add_argument('--pyr_level', type=int, default=0, help="pyramid level")
-parser.add_argument('--net_depth', type=int, default=0, help="at what layer do we extract features")
-parser.add_argument('--filename', default='jumpingjacks2menlowres.ogg', help="video filename")
-parser.set_defaults(median_reorder=False)
-parser.set_defaults(weighted_laplacian=False)
-parser.set_defaults(net_feat=False)
-
-opt = parser.parse_args()
 
 def getReorderedConsensus1D(X, N, thetau, doPlot = False):
     """
@@ -199,7 +180,7 @@ def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = 20):
 
 def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
                 doSimple = False, doImageAnalogies = False, doPlot = True, \
-                Verbose = False, fileprefix = "", Kappa = -1, p = 2):
+                Verbose = False, fileprefix = "", Kappa = -1, p = 41):
     """
     Reorder the video based on circular coordinates of a sliding
[…]

### 2018-01-23 RobustnessTests.py
Adding resnet features to batch tests

@@ -4,6 +4,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import scipy.io as sio
 import argparse
+import os
 
 def getVideoPyramid(I, IDims, pyr_level):
     """
@@ -18,6 +19,49 @@ def getVideoPyramid(I, IDims, pyr_level):
         frame = np.reshape(I[i, :], IDims)
         feat_frame = tuple(pyramid_gaussian(frame, pyr_level, downscale = 2))[-1]
         IRet.append(feat_frame.flatten())
+    return np.array(IRet)
+
+def getVideoResNet(IOrig, IDims, depth):
+    import torch
+    import torch.nn as nn
+    import torch.backends.cudnn as cudnn
+    import torchvision.transforms as transforms
+    import torchvision.models as models
+    from torch.autograd import Variable
+
+    # get first layers of network - we can try out different things here
+    if depth == 0:
+        shallow_layers = ['conv1','bn1','relu','maxpool']
+    elif depth == 1:
+        shallow_layers = ['conv1','bn1','relu','maxpool','layer1']
+    else:
+        print('unknown depth?',depth)
+        shallow_layers = ['conv1','bn1','relu','maxpool']
+    net = models.__dict__['resnet18'](pretrained=True)
+    net.eval()
+    resnet_module = net.modules().__next__()
+    resnet_modules = resnet_module.named_children()
+    shallow_nn = []
+    for module_name,module in resnet_modules:
+        if module_name in shallow_layers:
+            shallow_nn.append(module)
+
+    # preprocessing for network
+    full_transform = transforms.Compose([transforms.ToTensor(),transforms.Normalize(mean=[0.485, 0.456, 0.406], std=[0.229, 0.224, 0.225])])
+
+    NFrames = IOrig.shape[0]
+    IRet = []
+    for i in range(0, NFrames):
+        frame = np.array(255.0*np.reshape(IOrig[i, :], IDims), dtype = np.uint8)
+        frame_th = full_transform(Image.fromarray(frame)) # easiest to convert to PIL, then apply torch transforms
+        frame_mb = frame_th.view(1,frame_th.size()[0],frame_th.size()[1],frame_th.size()[2])
+        frame_var = Variable(frame_mb,requires_grad=False)
+        for module in shallow_nn:
+            frame_var = module(frame_var)
+        th_data = frame_var.data
[…]

### 2018-01-24 AllExperiments.py
Switching to GUDHI, fixing bug in unweighted Laplacian, adding lots of command line options for different tests

@@ -13,11 +13,12 @@ pyrLevel = 2
 for V in Videos:
     for medianReorder in [0, 1]:
         for weighted in [0, 1]:
-            strs = [MedianOpt[medianReorder], LapOpt[weighted]]
-            fileprefix = get_out_fileprefix('reordered', V, not medianReorder, weighted, opt.net_feat, pyrLevel, opt.net_depth)
-            print(fileprefix)
-            if os.path.exists("%s.avi"%fileprefix):
-                print("Skipping %s..."%fileprefix)
-                continue
-            cmd = ["python", "VideoReordering.py", "--filename", V, "--show-plots", "--pyr_level", "%i"%pyrLevel] + strs
-            subprocess.call(cmd)
+            for Kappa in [0, 0.05, 0.1, 0.15]:
+                strs = [MedianOpt[medianReorder], LapOpt[weighted]]
+                fileprefix = get_out_fileprefix('reordered', V, not medianReorder, weighted, False, pyrLevel, 0, Kappa=Kappa)
+                print(fileprefix)
+                if os.path.exists("%s.avi"%fileprefix):
+                    print("Skipping %s..."%fileprefix)
+                    continue
+                cmd = ["python", "VideoReordering.py", "--filename", V, "--show-plots", "--pyr_level", "%i"%pyrLevel, "--Kappa", "%g"%Kappa] + strs
+                subprocess.call(cmd)

### 2018-01-24 CSMSSMTools.py

@@ -7,6 +7,8 @@ def getSSM(X):
     D = XSqr[:, None] + XSqr[None, :] - 2*X.dot(X.T)
     D[D < 0] = 0 #Numerical precision
     D = np.sqrt(D)
+    np.fill_diagonal(D, 0)
+    D = 0.5*(D + D.T)
     return D
 
 def getCSM(X, Y):

### 2018-01-24 Laplacian.py

@@ -121,7 +121,7 @@ def getLapCircularCoordinatesThresh(pD, thresh, NEigs = 20, doPlot = False):
         plt.subplot(313)
         plt.plot(v[:, [i1, i1+1]])
         plt.legend(["%i"%i1, "%i"%(i1+1)])
-    (theta, thetau) = getLapThetas(v, 1, 2)
+    (theta, thetau) = getLapThetas(v, i1, i1+1)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
 
 def getLapCircularCoordinatesKNN(D, Kappa, NEigs = 20, doPlot = False):

### 2018-01-24 RobustnessTests.py

@@ -1,5 +1,6 @@
 from VideoTools import *
 from VideoReordering import *
+from multiprocessing import Pool as PPool
 import numpy as np
 import matplotlib.pyplot as plt
 import scipy.io as sio
@@ -81,15 +82,16 @@ def getKendallTauCircle(rank1, rank2):
     B[np.abs(B) > np.pi] *= -1
     return np.sum(A*B)/float(N*(N-1))
 
-def getCycles(NCycles, NFinal, filename):
+def getCycles(NCycles, filename, NFinal = -1):
     I, I_feat, IDims = loadImageIOVideo(filename)
     N = I.shape[0]
     theta = np.linspace(0, 2*np.pi, N)
     idx = np.mod(NCycles*np.arange(N), N)
-    if NFinal == -1:
-        NFinal = N
-    starti = np.random.randint(len(idx)-NFinal)
-    idx = idx[starti:starti+NFinal]
+    if NFinal > 0:
+        starti = np.random.randint(len(idx)-NFinal)
+        idx = idx[starti:starti+NFinal]
+    #Circularly permute indices
+    idx = np.roll(idx, np.random.randint(len(idx)))
     theta = theta[idx]
     theta = np.unwrap(theta)
     theta = theta - np.min(theta)
@@ -102,15 +104,17 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
         doPlot = True
     doSimple = True
     #Range over: Period, Noise Amount, Shake Amount
-    res = getCycles(NCycles = NCycles, NFinal = 300, filename = filename)
+    res = getCycles(NCycles = NCycles, filename = filename)
     [I, IDims, thetagt] = [res['I'], res['IDims'], res['theta']]
     I += noise*np.random.randn(I.shape[0], I.shape[1])
     if shake > 0:
-        I = simulateCameraShake(I, IDims, shake)
+        simulateCameraShake(I, IDims, shake)
     if saveVideos:
         saveVideo(I, IDims, "%s_simulated.avi"%fileprefix)
     ret = {}
     for pyr_level in range(-2, 4):
+        if Verbose:
+            print("pyr_level = %i"%pyr_level)
         if pyr_level >= 0:
             I_feat = getVideoPyramid(I, IDims, pyr_level)
         else:
@@ -121,7 +125,8 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
[…]

### 2018-01-24 VideoReordering.py

@@ -1,10 +1,10 @@
 from VideoTools import *
-from ripser import ripser
 from CSMSSMTools import *
 from Laplacian import *
 from FundamentalFreq import *
 from PatchTools import *
 from ImageAnalogies import *
+from TDA import *
 import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib.image as mpimage
@@ -180,7 +180,7 @@ def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = 20):
 
 def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
                 doSimple = False, doImageAnalogies = False, doPlot = True, \
-                Verbose = False, fileprefix = "", Kappa = -1, p = 41):
+                Verbose = False, fileprefix = "", Kappa = -1, p = 41, returnAnswer = True):
     """
     Reorder the video based on circular coordinates of a sliding
     window embedding
@@ -240,8 +240,10 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
         else:
             res = getLapCircularCoordinatesKNN(D, Kappa)
     else:
+        if Verbose:
+            print("Computing H1 on point cloud of size %i..."%D.shape[0])
         tic = time.time()
-        Is = ripser.doRipsFiltrationDM(D, 1, coeff=p)
+        Is = doRipsFiltrationDMGUDHI(D, 1, coeff=p)
         if Verbose:
             print("Elapsed Time Ripser: %g"%(time.time() - tic))
         I = Is[1]
@@ -268,7 +270,7 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
         plt.title("Adjacency Matrix")
         plt.subplot(233)
         if not (Kappa > 0 and Kappa < 1):
-            ripser.plotDGM(I)
+            plotDGM(I)
             plt.title("H1, Thresh = %g"%thresh)
         plt.subplot(234)
         plt.imshow(v, cmap = 'afmhot', interpolation = 'nearest', aspect = 'auto')
@@ -283,7 +285,8 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
     XRet = None
     if doSimple:
         idx = np.argsort(np.mod(thetau, 2*np.pi))
-        XRet = XOrig[idx, :]
+        if returnAnswer:
+            XRet = XOrig[idx, :]
     else:
         # done for the original video
[…]

### 2018-01-24 VideoTools.py

@@ -473,17 +473,17 @@ def getRandomMotionBlurMask(extent):
     return (Y, I)
 
 def simulateCameraShake(I, IDims, shakeMag):
-    J = np.zeros(I.shape)
-    for i in range(J.shape[0]):
-        print("Blurring frame %i of %i"%(i, J.shape[0]))
+    """
+    Do the blur in place to save memory
+    """
+    for i in range(I.shape[0]):
+        print("Blurring frame %i of %i"%(i, I.shape[0]))
         X = np.reshape(I[i, :], IDims)
         (_, mask) = getRandomMotionBlurMask(shakeMag)
         IBlur = 0*X
         for k in range(X.shape[2]):
             IBlur[:, :, k] = scipy.signal.fftconvolve(X[:, :, k], mask, 'same')
-        #IBlur = np.array(IBlur, dtype=np.uint8)
-        J[i, :] = IBlur.flatten()
-    return J
+        I[i, :] = IBlur.flatten()
 
 if __name__ == '__main__2':
     (I, IDims) = loadVideo("VocalCordsVideos/LTR_ED_MucusBiphonCrop.avi")

### 2018-01-24 Videos/makeHarmonic.py

@@ -1,0 +1,19 @@
+import numpy as np
+import sys
+sys.path.append("..")
+from VideoTools import *
+
+def makeHarmonicVideo(filename):
+    I, _, IDims = loadImageIOVideo(filename)
+    INew = []
+    for i in range(I.shape[0]):
+        F1 = np.reshape(I[i, :], IDims)
+        F2 = np.reshape(I[i*2%I.shape[0], :], IDims)
+        F = np.concatenate((F1, F2), 1)
+        INew.append(F.flatten())
+    IDims = (IDims[0], IDims[1]*2, IDims[2])
+    return (np.array(INew), IDims)
+
+if __name__ == '__main__':
+    (I, IDims) = makeHarmonicVideo('SlowMotionTemplateSimple.avi')
+    saveVideo(I, IDims, "harmonic.avi")

### 2018-01-24 RobustnessTests.py
Fixing bug in Kendall Tau, adding sliding window vs not sliding window, changing threshold on TDA weighted to be birth time

@@ -74,12 +74,14 @@ def getKendallTauCircle(rank1, rank2):
     on the circle
     """
     N = len(rank1)
-    diff = rank1[None, :] - rank1[:, None]
+    r1 = rank1/float(N)
+    r2 = rank2/float(N)
+    diff = r1[None, :] - r1[:, None]
     A = np.sign(diff)
-    A[np.abs(A) > np.pi] *= -1 #Wrap around
-    diff = rank2[None, :] - rank2[:, None]
+    A[np.abs(diff) > 0.5] *= -1 #Wrap around
+    diff = r2[None, :] - r2[:, None]
     B = np.sign(diff)
-    B[np.abs(B) > np.pi] *= -1
+    B[np.abs(diff) > 0.5] *= -1
     return np.sum(A*B)/float(N*(N-1))
 
 def getCycles(NCycles, filename, NFinal = -1):
@@ -122,32 +124,34 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
             I_feat = getVideoResNet(I, IDims, depth)
         for Kappa in [0, 0.05, 0.1, 0.15]:
             for Weighted in [True, False]:
-                thisprefix = "%i_%g_%i"%(pyr_level, Kappa, Weighted)
-                res = reorderVideo(I, I_feat, IDims, derivWin = 0, Weighted = Weighted, \
-                                    doSimple = doSimple, doPlot = doPlot, Verbose = Verbose, \
-                                    doImageAnalogies = False, Kappa = Kappa, \
-                                    fileprefix = fileprefix+thisprefix, returnAnswer = False)
-                theta = np.mod(res['thetau'], 2*np.pi)
-                thetagt = thetagt[0:len(theta)]
-                theta = theta[0:len(thetagt)]
-                circErr = np.mean(getCircleDist(theta, thetagt))
-                rank1 = 0*thetagt
-                rank1[np.argsort(thetagt)] = np.arange(len(rank1))
-                rank2 = 0*rank1
-                rank2[np.argsort(theta)] = np.arange(len(rank2))
-                kendTau = getKendallTauCircle(rank1, rank2)
-                ret[thisprefix] = [circErr, kendTau]
-                if doPlot:
-                    plt.figure(figsize=(8, 6))
-                    plt.subplot(211)
-                    plt.scatter(thetagt, theta)
-                    plt.title("err = %.3g"%circErr)
-                    plt.subplot(212)
[…]

### 2018-01-24 VideoReordering.py

@@ -180,7 +180,8 @@ def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = 20):
 
 def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
                 doSimple = False, doImageAnalogies = False, doPlot = True, \
-                Verbose = False, fileprefix = "", Kappa = -1, p = 41, returnAnswer = True):
+                Verbose = False, fileprefix = "", Kappa = -1, p = 41, \
+                returnAnswer = True, doSlidingWindow = True):
     """
     Reorder the video based on circular coordinates of a sliding
     window embedding
@@ -217,17 +218,20 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
     XIso = manifold.Isomap(10, 2).fit_transform(X)
     if doPlot:
         plt.figure(figsize=(18, 12))
-    dim = int(np.round(estimateFundamentalFreq(XIso[:, 0], doPlot = doPlot)['maxTau']))
-    for k in range(2):
-        #Make window size larger, within reason
-        if dim*2 < int(0.25*XOrig.shape[0]):
-            dim *= 2
-    if doPlot:
-        plt.subplot(211)
-        plt.title("Chosen Dim = %i"%dim)
-        plt.savefig("%s_FundamentalFreq.svg"%fileprefix, bbox_inches = 'tight')
-    #Do sliding window
-    XS = getSlidingWindowVideoInteger(X, dim)
+    dim = 0
+    XS = X
+    if doSlidingWindow:
+        dim = int(np.round(estimateFundamentalFreq(XIso[:, 0], doPlot = doPlot)['maxTau']))
+        for k in range(2):
+            #Make window size larger, within reason
+            if dim*2 < int(0.25*XOrig.shape[0]):
+                dim *= 2
+        if doPlot:
+            plt.subplot(211)
+            plt.title("Chosen Dim = %i"%dim)
+            plt.savefig("%s_FundamentalFreq.svg"%fileprefix, bbox_inches = 'tight')
+        #Do sliding window
+        XS = getSlidingWindowVideoInteger(X, dim)
 
     #Mean-center and normalize sliding window
     Y = XS - np.mean(XS, 1)[:, None]
@@ -245,10 +249,15 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
         tic = time.time()
         Is = doRipsFiltrationDMGUDHI(D, 1, coeff=p)
[…]

### 2018-01-30 VideoReordering.py
Dealing properly with collisions in video, and adding threshold beyond which not to interpolate in the median consensus

@@ -68,7 +68,8 @@ def getReorderedConsensus1D(X, N, thetau, doPlot = False):
         plt.show()
     return (Z, np.nanmedian(Z, 0), tidx)
 
-def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, thetau, doPlot = False, Verbose = False, lookAtVotes = False):
+def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, thetau, tdifflim = -1, \
+                                doPlot = False, Verbose = False, lookAtVotes = False):
     """
     Given an array of sliding window videos and circular coordinates,
     reorder the sliding windows to go through one period
@@ -84,7 +85,9 @@ def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, thetau, doPlot = False, Ve
     :param VT: The right singular vectors transposed, to get from PCA\
         back to video.  Dimensions NFrames x (NPixels*NChannels)
     :param dim: The sliding window length
-    :param theta: The unwrapped circular coordinates
+    :param thetau: The unwrapped circular coordinates
+    :param tdifflim: The maximum distance away from a nearest frame to interpolate\
+                    (default -1: interpolate all frames)
     :param doPlot: Whether to make a plot showing all of the windows
     :param Verbose: Whether to print out debugging info
     :param lookAtVotes: Whether to output a video for all of the votes\
@@ -92,7 +95,8 @@ def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, thetau, doPlot = False, Ve
     """
     N = X.shape[0]
     M = len(thetau)
-   
+    print("tdifflim = ", tdifflim)
+
     #Step 1: Figure out the number of periods that the signal
     #goes through
     NPeriods = (float(N)/M)*np.max(thetau)/(2*np.pi)
@@ -102,7 +106,7 @@ def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, thetau, doPlot = False, Ve
     
     #Step 2: Go through each window and use it to vote on final samples
     #in projected coordinates
-    XInterp = np.nan*np.ones((M, X.shape[0], X.shape[1]))
+    XInterp = np.zeros((M, X.shape[0], X.shape[1]))
     pix = np.arange(X.shape[1])
     for i in range(M):
         if Verbose:
[…]

### 2018-01-30 Paper/paper.tex
Finished code for batch cluster robustness tests
Major reworking of the intro of the paper, fixing block diagram, and adding an XT slice for the fan video

@@
 
-\title{Eulerian Synthesis of Slow Motion Periodic Videos}
+\title{Topological Eulerian Synthesis of Slow Motion Periodic Videos}
 
@@
 \begin{abstract}
-Abstract
+
+The majority of our pipeline is fully automated, using tools from topological data analysis in concert with nonlinear dimenison reduction to autotune the spatial and temporal scales of the period.
+
 \end{abstract}
@@
 \section{Introduction}
+%Background, drift, noise, large motion, static pixels, scale finding, overall automation [fundamental frequency, etc].  Sliding window "time regularization"
 
 Repetitive, periodic motions are ubiquitous in our world, such as animal locomotion (walking/flapping/slithering/swimming), mechanical motions (wheels spinning, pistons oscillating), biological rhythms (heartbeat, breathing), musical rhythms (drumming, feet tapping), etc.
-In this work, we consider videos of periodic motion.
-One avenue of interest is to analyze these videos in fine detail, such as for characterizing subtle progressions of blood flow in the face during a heartbeat for medical diagnostic purposes.
-It may also be important to understand and visualize variations from cycle to cycle, such as in a repetitive automated action on an assembly line, where too much variation could indicate the onset of failure, or in athletic activities for optimizing performance.
+In this work, we consider the problem of synthesizing a fine detail, ``slow motion'' template cycle of motion from a video of such a motion with many periods.
+This fine detailed analysis can be applied, for example, to characterize subtle progressions of blood flow in the face during a heartbeat \cite{kumar2015distanceppg}.
+Having access to a consensus template can also be used to visualize variations from cycle to cycle, such as in a repetitive automated action on an assembly line, where too much variation could indicate the onset of failure (TODO: citation), or in athletic activities for optimizing performance.
 
-Our approach is {\em Eulerian}; that is, we process the video pixel by pixel with no tracking.
-Unlike Fourier-based Eulerian motion video processing tools (\cite{wu2012eulerian, wadhwa2013phase}), however, we take a {\em geometric} approach by quantifying {\em sliding window embeddings} of our videos (Section~\ref{sec:slidingwindow}).
-Sliding window embeddings of periodic time series form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data \cite{traliehigh, tralie2017quasi}.
-This implies that, at the right scale, a nearest neighbor graph built on the sliding window point cloud should be approximately a circle graph, even if the overall extrinsic geometry is quite complicated.
-Bearing this in mind, we use Laplacian eigenmaps \cite{belkin2003laplacian} of this embedding to construct maps from these point clouds to the circle, or {\em circular coordinates} (Section~\ref{sec:laplacian}).
-In particular, each sliding window is assigned a phase $\phi \in [0, 2\pi]$.
-To autotune the scale at which Laplacian eigenmaps are built, we use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} to automatically find the scale at which the most prominent loop in the data occurs.
+Our approach to slow motion templates is {\em Eulerian}; that is, we process the video pixel by pixel with no tracking.
+Eulerian approaches for video synthesis are attractive due to their ease of implementation.
+For instance, a simple Fourier bandpass filtering and amplifying pixels can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.
+Additionally, time domain Eulerian approaches have been used to synthesize infinitely playing ``video textures'' using random walks \cite{schodl2000video}, or to synthesize perfectly looping video templates after grouping pixels with similar periods together and devising a common period for all groups \cite{Liao2013VideoLoops,Liao2015VideoLoops}.
+There are some pitfalls with Eulerian techniques, however.
+Purely Eulerian amplification techniques are known to fail for large motions, and they also require the user to manually specify frequencies of interest \cite{wu2012eulerian, wadhwa2013phase}.
+Furthermore, drift from period to period due to shaking and varying motions from cycle to cycle can present a problem, as can unrelated motion in the background \cite{stauffer1999adaptive}.
 
-Once we have extracted a phase for each window, we use this information to reorder the content of the video.
-We also exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template (Section~\ref{sec:cyclereordering}).
+To address the problems with an Eulerian representation, we devise a geometric/topological Eulerian framework byconstructing {\em sliding window embeddings} of our videos (Section~\ref{sec:slidingwindow}).
+Sliding window embeddings, or ``delay reconstructions,'' have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
+Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data \cite{traliehigh, tralie2017quasi}.
+We autotune the sliding window size using fundamental frequency estimation \cite{Mcleod05asmarter}, and we use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} to find the appropriate spatial scale of the loop.
+We then parameterize the video by assigning each window a phase $\phi \in [0, 2\pi]$ using Laplacian Eigenmaps \cite{belkin2003laplacian}.
+We then re-order the sliding windows by phase and exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template, which helps with drift (Section~\ref{sec:cyclereordering}).
 As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled periodic time series (i.e.
@@
 
-\section{Releated Work}
-Our technique unifies many disparate ideas that have appeared before in different contexts, in addition to the references we mentioned in the introduction.
-Sliding window embeddings, or ``delay reconstructions,'' have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{schodl2000video, tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
-All of these works focus on analysis rather than synthesis, as we do, but there has been work using sliding window embeddings to synthesize ``video textures,'' or videos that repeat dynamics indefinitely \cite{schodl2000video}, which are similar in spirit to our infinitely looping periodic representatives.
-The graph Laplacian, on the other hand, has been used to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and vector diffusion maps have been used to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.
-A different topological approach with cohomology circular coordinates\cite{de2011persistent} was used to parameterize a sliding window embedding of the Lorenz attractor \cite{de2012topological} and periodic activites in motion capture data \cite{vejdemo2015cohomological}.
+Many prior works use a combination of sliding window embeddings and topological data analysis, such as detecting the Lorenz attractor \cite{de2012topological}, quantifying circadian rhythms in gene expression data \cite{perea2015sliding}, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, quantifying vocal fold anomalies in video \cite{tralie2017quasi}.
+As shown by the authors of \cite{tralie2017quasi}, sliding window embeddings on Eulerian videos provide a sort of ``time regularization,'' which can mitigate the effects of drift, leading to a cleaner loop,
+
+%The graph Laplacian, on the other hand, has been used to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and vector diffusion maps have been used to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.
+A different topological approach with cohomology circular coordinates\cite{de2011persistent} was used to parameterize a sliding window embedding of the .
 Neural networks have also been trained to find circular coordinates \cite{levy2015live,anafi2017cyclops}.
-Finally, perhaps the most related to our goal is work synthesizing seamless video loops by clustering pixels into different periods and adjusting them to loop through a common period \cite{Liao2013VideoLoops,Liao2015VideoLoops}.
-TODO: talk about applications of TDA?
 
-\section{Methods}
+\section{Slow Motion Templates}
 \label{sec:methods}
@@
 We now describe our algorithm in several stages.
-Throughout our discussion, we assume we are dealing with 3 channel color videos.
-For a frame resolution of $W \times H$, each frame can be thought of as a Euclidean vector in $\mathbb{R}^{W \times H \times 3}$.
+Throughout our discussion, we assume we are given 3 channel color videos with $W \times H$ resolution frames, so that each frame is a Euclidean vector in $\mathbb{R}^{W \times H \times 3}$.
 For a video with $N$ frames, we flatten each frame to a 1D vector and stack them row wise along an $N \times 3WH$ matrix $X$.
@@
 The only nonlinear operation is the median operation (Section~\ref{sec:cyclereordering}), and we project back into pixel space using $V^T$ before taking the median.
-Algorithm~\ref{alg:videoreordering} shows the full details of our method in pseudocode.
 
@@
 Furthermore, the sliding window length $(d-1) \tau$, or simply $d-1$ in our case, maximizes the roundness of the embeddings when $d-1 = k T$ for some integer $k$, where $T$ is the fundamental period.
-Since we use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that we tune our window size to be an integer multiple of the period.
+Since we will use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that we tune our window size to be an integer multiple of the period.
 To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D ``surrogate signal,'' and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $d$.
 This is quite similar to the diffusion maps + autocorrelation approach in \cite{tralie2017quasi} for analyzing periodic videos.
-This estimation often returns multiples of the fundamental period, which is fine for our purposes.
+This estimation often returns integer multiples of the fundamental period, which is fine for our purposes.
 
@@
 \label{sec:laplacian}
+
+TDA addresses problems of scale
 
@@
 
+Talk about how it can pick up on harmonics (e.g. jumping jacks), which is why this is important
+
 \subsection{Cycle Reordering And Median Voting}
@@
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.8\columnwidth]{XTSlice.pdf}
-\caption{An XT slice of a line of pixels (magenta line, upper left) over time for the original video and for reordered videos with and without median consensus.}
-\label{fig:XTSlice}
-\end{figure}
-
-Figure~\ref{fig:XTSlice} shows the difference between a simple reordering and a median consensus reordering.
-Due to natural variation from cycle to cycle, the simple reordering has many temporal discontinuities when interleaving these cycles.
-By contrast, the median voting is clean, and it has the added benefit of removing nonperiodic background components.
-
 Advantage of Eulerian is that everything is linear (can use SVD to compress)
 
-Interpolated windows can be projected back to pixel space one by one to save memory (Line~\ref{algline:medianconsensus} of Algorithm~\ref{alg:videoreordering})
+Interpolated windows can be projected back to pixel space one by one to save memory
 
@@
 
-Robustness experiments, jumping jacks 2 men, two exercise videos from \cite{levy2015live}, beating heart videos from \cite{traliehigh}, \cite{wu2012eulerian}, and \cite{wadhwa2013phase}.
+\subsection{Robustness Tests}
+Robustness experiments
+
+\subsection{Qualitative Results}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\columnwidth]{XTSliceJumpingJacks.pdf}
+\caption{An XT slice of a line of pixels (magenta line, upper left) over time for an input video of two men doing jumping jacks and for reordered videos with and without median consensus.}
+\label{fig:XTSliceJumpingJacks}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\columnwidth]{XTSliceFan.pdf}
+\caption{An XT slice of a line of pixels (magenta line, upper left) over time for an input video of a fan with only 6 frames per period and the corresponding median consensus reordered video.}
+\label{fig:XTSliceFan}
+\end{figure}
+
+Figure~\ref{fig:XTSliceJumpingJacks} shows the difference between a simple reordering and a median consensus reordering.
+Due to natural variation from cycle to cycle, the simple reordering has many temporal discontinuities when interleaving these cycles.
+By contrast, the median voting is clean, and it has the added benefit of removing nonperiodic background components.
+
+umping jacks 2 men, two exercise videos from \cite{levy2015live}, beating heart videos from \cite{traliehigh}, \cite{wu2012eulerian}, and \cite{wadhwa2013phase}.
 

### 2018-01-30 Laplacian.py

@@ -64,7 +64,7 @@ def getSlowestEigenvectorIdx(v):
             i1 = i
     return (i1, zcs)
 
-def getLapCircularCoordinatesSigma(D, sigma, NEigs = 20, doPlot = False):
+def getLapCircularCoordinatesSigma(D, sigma, NEigs = 10, doPlot = False):
     """
     Get circular coordinates using a weighted laplacian 
     :param pD: Distance matrix
@@ -93,7 +93,7 @@ def getLapCircularCoordinatesSigma(D, sigma, NEigs = 20, doPlot = False):
     (theta, thetau) = getLapThetas(v, i1, i1+1)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
 
-def getLapCircularCoordinatesThresh(pD, thresh, NEigs = 20, doPlot = False):
+def getLapCircularCoordinatesThresh(pD, thresh, NEigs = 10, doPlot = False):
     """
     Get circular coordinates using an unweighted laplacian based
     on binarizing a distance matrix below a certain threshold
@@ -124,7 +124,7 @@ def getLapCircularCoordinatesThresh(pD, thresh, NEigs = 20, doPlot = False):
     (theta, thetau) = getLapThetas(v, i1, i1+1)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
 
-def getLapCircularCoordinatesKNN(D, Kappa, NEigs = 20, doPlot = False):
+def getLapCircularCoordinatesKNN(D, Kappa, NEigs = 10, doPlot = False):
     """
     Get circular coordinates using a weighted laplacian 
     :param pD: Distance matrix
@@ -153,7 +153,7 @@ def getLapCircularCoordinatesKNN(D, Kappa, NEigs = 20, doPlot = False):
     (theta, thetau) = getLapThetas(v, i1, i1+1)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
 
-def getLapCircularCoordinatesKNNWeighted(D, Kappa, NEigs = 20, doPlot = False):
+def getLapCircularCoordinatesKNNWeighted(D, Kappa, NEigs = 10, doPlot = False):
     """
     Get circular coordinates using a weighted laplacian 
     :param pD: Distance matrix

### 2018-01-30 PaperFigures.py

@@ -202,9 +202,8 @@ def getAllImageSlices(I, IDims, xlims, ylims, line):
         XT.append(F[line, :, :])
     return np.array(XT)
 
-def makeXTSliceSimpleAndMedian():
-    plt.figure(figsize=(6, 5))
-    filename = 'Results/jumpingjacks2menlowres-reordered--%s-unweighted-img-2.avi'
+def makeXTSliceSimpleAndMedianJumpingJacks():
+    plt.figure(figsize=(12, 2))
     [IOrig, _, IDims] = loadImageIOVideo('jumpingjacks2menlowres.ogg')
     xlims = [55, 348]
     ylims = [0, 200]
@@ -213,12 +212,13 @@ def makeXTSliceSimpleAndMedian():
 
     line = 50
     FOrig = getAllImageSlices(IOrig, IDims, xlims, ylims, line)
-    [ISimple, _, _] = loadImageIOVideo(filename%"simple")
+    #NOTE: These videos were done with weighted laplacian
+    [ISimple, _, _] = loadImageIOVideo("Results/JumpingJacks_Simple.avi")
     FSimple = getAllImageSlices(ISimple, IDims, xlims, ylims, line)
-    [IMedian, _, _] = loadImageIOVideo(filename%"median")
+    [IMedian, _, _] = loadImageIOVideo("Results/JumpingJacks_AllMedian.avi")
     FMedian = getAllImageSlices(IMedian, IDims, xlims, ylims, line)
 
-    plt.subplot(221)
+    plt.subplot(141)
     plt.imshow(FRef)
     plt.plot([0, FRef.shape[1]], [line, line], color = [0.7, 0, 0.7])
     plt.axis('equal')
@@ -226,24 +226,59 @@ def makeXTSliceSimpleAndMedian():
     plt.xlabel("X")
     plt.ylabel("Y")
     plt.title("Original Frame")
-    plt.subplot(222)
+    plt.subplot(142)
     plt.imshow(FOrig)
     plt.axis('equal')
     plt.axis('off')
     plt.title("Original Video")
-    plt.subplot(223)
+    plt.subplot(143)
     plt.imshow(FSimple)
     plt.axis('equal')
     plt.axis('off')
     plt.title("Reordered Simple")
-    plt.subplot(224)
+    plt.subplot(144)
     plt.imshow(FMedian)
     plt.axis('equal')
     plt.axis('off')
[…]

### 2018-01-30 RobustnessTests.py

@@ -168,7 +168,7 @@ def writeBatchHeaderCSV(fout, filename):
 
 def doBatchTests(filename, fout, batchidx = -1):
     idx = 0
-    for NCycles in [3, 5, 10, 20, 30, 50, 70, 100, 200]:
+    for NCycles in [3, 5, 10, 20, 30, 50, 70, 100, 200]: #[3, 5, 10, 15, 20, 25, 30, 40, 50]
         for noise in [0, 1, 2, 3]:
             for shake in [0, 20, 40, 80]:
                 for trial in range(10):
@@ -198,7 +198,7 @@ if __name__ == '__main__':
     parser.add_argument('--batch', type=int, default=0, help="batch")
     parser.add_argument('--nthreads', type=int, default=3, help="Number of threads in parallel pool")
     parser.add_argument('--out_dir', type=str, default=".", help="out directory")
-    parser.add_argument('--videofile', type=str, default='Videos/SlowMotionTemplateHarmonic.avi', help="Template video")
+    parser.add_argument('--videofile', type=str, default='Videos/SlowMotionTemplateSimple.avi', help="Template video")
     parser.add_argument('--NCycles', type=int, default=0, help = "Number of cycles")
     parser.add_argument('--shake', type=int, default=0, help = "Shake by pixels")
     parser.add_argument('--noise', type=float, default=0, help = "AWGN coefficient")

### 2018-01-31 Paper/paper.tex
Some more paper edits

@@
 Sliding window embeddings, or ``delay reconstructions,'' have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
-Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data \cite{traliehigh, tralie2017quasi}.
-We autotune the sliding window size using fundamental frequency estimation \cite{Mcleod05asmarter}, and we use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} to find the appropriate spatial scale of the loop.
-We then parameterize the video by assigning each window a phase $\phi \in [0, 2\pi]$ using Laplacian Eigenmaps \cite{belkin2003laplacian}.
-We then re-order the sliding windows by phase and exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template, which helps with drift (Section~\ref{sec:cyclereordering}).
+Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data, regardless of the type of motion present \cite{traliehigh, tralie2017quasi}.
+Furthermore, as shown by the authors of \cite{tralie2017quasi}, sliding window embeddings on Eulerian videos provide a sort of ``time regularization,'' which can mitigate the effects of drift, leading to a cleaner loop.
+Our geometric framework also allows us to use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} and fundamental frequency estimation \cite{Mcleod05asmarter} to autotune the temporal and spatial scales of the periodic motion, respectively, so that no user intervention is required.
+Our embedding also makes it easy to assign each window a circular phase $\phi \in [0, 2\pi]$ using Laplacian Eigenmaps \cite{belkin2003laplacian}.
+We then re-order the sliding windows by phase and exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template, which further mitigates drift (Section~\ref{sec:cyclereordering}).
 As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled periodic time series (i.e.
@@
 
-Many prior works use a combination of sliding window embeddings and topological data analysis, such as detecting the Lorenz attractor \cite{de2012topological}, quantifying circadian rhythms in gene expression data \cite{perea2015sliding}, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, quantifying vocal fold anomalies in video \cite{tralie2017quasi}.
-As shown by the authors of \cite{tralie2017quasi}, sliding window embeddings on Eulerian videos provide a sort of ``time regularization,'' which can mitigate the effects of drift, leading to a cleaner loop,
-
-%The graph Laplacian, on the other hand, has been used to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and vector diffusion maps have been used to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.
-A different topological approach with cohomology circular coordinates\cite{de2011persistent} was used to parameterize a sliding window embedding of the .
-Neural networks have also been trained to find circular coordinates \cite{levy2015live,anafi2017cyclops}.
+Many prior works use a combination of sliding window embeddings and topological data analysis, such as detecting the Lorenz attractor \cite{de2012topological}, quantifying circadian rhythms in gene expression data \cite{perea2015sliding}, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, quantifying vocal fold anomalies in video \cite{tralie2017quasi}, though we believe we are the first to use a sliding window + TDA framework to {\em synthesize} a new result.
+Our use of the graph Laplcian to parameterize time series is also unique, though we are inspired by works that have used it to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and works which use vector diffusion maps to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.
+We use the combination of TDA + Laplacian eigenmaps as a simple alternative to the more complicated alternative cohomology circular coordinates \cite{de2011persistent}.
 
@@
 
-Talk about autotuning with peristent homology, mention that it's the opposite of the approach in \cite{bendich2011improving}.
+Talk about autotuning with peristent homology, mention that it's the opposite of the approach in \cite{bendich2011improving}
 

### 2018-01-31 Paper/paper.tex
More writing

@@
 Our approach to slow motion templates is {\em Eulerian}; that is, we process the video pixel by pixel with no tracking.
-Eulerian approaches for video synthesis are attractive due to their ease of implementation.
+Eulerian approaches for video synthesis are attractive due to their simplicity and ease of implementation.
 For instance, a simple Fourier bandpass filtering and amplifying pixels can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.
@@
 Our embedding also makes it easy to assign each window a circular phase $\phi \in [0, 2\pi]$ using Laplacian Eigenmaps \cite{belkin2003laplacian}.
-We then re-order the sliding windows by phase and exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template, which further mitigates drift (Section~\ref{sec:cyclereordering}).
+We then re-order the sliding windows by $\phi$ and exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template, which further mitigates drift (Section~\ref{sec:cyclereordering}).
 As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled periodic time series (i.e.
@@
 
-Many prior works use a combination of sliding window embeddings and topological data analysis, such as detecting the Lorenz attractor \cite{de2012topological}, quantifying circadian rhythms in gene expression data \cite{perea2015sliding}, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, quantifying vocal fold anomalies in video \cite{tralie2017quasi}, though we believe we are the first to use a sliding window + TDA framework to {\em synthesize} a new result.
+Many prior works use a combination of sliding window embeddings and topological data analysis, such as detecting the Lorenz attractor \cite{de2012topological}, quantifying circadian rhythms in gene expression data \cite{perea2015sliding}, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, and quantifying vocal fold anomalies in video \cite{tralie2017quasi}, though we believe we are the first to use a sliding window + TDA framework to {\em synthesize} a new result.
 Our use of the graph Laplcian to parameterize time series is also unique, though we are inspired by works that have used it to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and works which use vector diffusion maps to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.
-We use the combination of TDA + Laplacian eigenmaps as a simple alternative to the more complicated alternative cohomology circular coordinates \cite{de2011persistent}.
+We use the combination of TDA + Laplacian eigenmaps as a simple alternative to the more complicated cohomology circular coordinates proposed by the authors of \cite{de2011persistent} and used on motion capture data \cite{vejdemo2015cohomological}.
 
@@
 We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.
-From this, we use the mean of the birth and death time of the largest persistence dot to autotune the scale $\sigma$ for the graph Laplacian, from which we derive circular coordinates $\phi$, which can be used to reorder the sliding windows and use them to vote on a final slow motion template.}
+From this, we use the mean of the birth and death time of the largest persistence dot to autotune the scale $\sigma$ for the graph Laplacian, from which we derive circular coordinates $\phi$, which can be used to reorder the sliding windows and use them to vote on a final slow motion template.
+The result is shown in the bottom rightmost plot, superimposed with a ground truth period shows as an orange dotted line.}
 \label{fig:ConceptFigure}
@@
 
-TDA addresses problems of scale
+Since sliding window embeddings of periodic videos lie on a topological loop (a manifold which is an ``intrinsic circle''), this means that, at an appropriate scale, a nearest neighbors graph built on the sliding window point cloud will approximately be a circle graph.
+To parameterize this graph, we turn to the graph Laplacian \cite{chung1997spectral}.
+For a graph $G$ with $N$ vertices and an $N \times N$ symmetric adjacency matrix $A$, the graph Laplacian is defined as
+\begin{equation}
+L = D-A
+\end{equation}
+where $D_{ii} = \sum_{j = 1}^N A_{ij}, D_{i \neq j} = 0$ is the diagonal matrix.
+Now let $d_{ij}: V \rightarrow \mathbb{R}^+$ be a nonnegative scalar function on the vertices of $G$.
+Then the adjacency matrix correponding to the {\em unweighted} graph Laplacain, $A_{\epsilon}^u(d)$, is
+
+\begin{equation}
+A_{\epsilon}^u(d)_{ij} = \left\{ \begin{array}{cc} 1 & i \neq j, d_{ij} \leq \epsilon \\ 0 & \text{otherwise} \end{array} \right\}
+\end{equation}
+
+For a circle graph, where the $A_{ij} = 1$ if $|i-j| = 1$, $i=1, j=N$, and $j=1, i=N$, or zero otherwise, the eigenvectors spanning the image of the graph laplacian are
+
+\begin{equation}
+v_{2k}[n] = \cos(2 \pi k n / N), v_{2k-1}[n] = \sin(2 \pi k n / N), k \geq 1
+\end{equation}
+
+%In other words, the graph Laplacian of an $N$-point circle graph recovers the $N$-dimensional discrete Fourier transform.
+
+with corresponding eigenvalues $\lambda_k = 2 - 2 \cos(2 \pi k / N)$ (and $\lambda_0 = 0$ with corresponding eigenvector $v_0[n] = 1$).
+When computing the eigenvectors of a circle graph numerically, therefore, $v_1$ and $v_2$ should be a sine and cosine, or orthogonal linear combinations therein.
+
+TODO: Talk about circulant graphs instead
 
@@
 
-Talk about how it can pick up on harmonics (e.g. jumping jacks), which is why this is important
+Talk about how it can pick up on harmonics (e.g. jumping jacks), which is why this is important (talk about using prime 49)
 

### 2018-02-01 Paper/paper.tex
Narrowing down interesting parameter regions for robustness tests, adding figures that show Laplacian for my model of a perfect unweighted periodic adjacency matrix

@@
 This fine detailed analysis can be applied, for example, to characterize subtle progressions of blood flow in the face during a heartbeat \cite{kumar2015distanceppg}.
-Having access to a consensus template can also be used to visualize variations from cycle to cycle, such as in a repetitive automated action on an assembly line, where too much variation could indicate the onset of failure (TODO: citation), or in athletic activities for optimizing performance.
+Having access to a consensus template can also be used to visualize variations from cycle to cycle, such as in a repetitive automated action on an assembly line, where too much variation could indicate the onset of failure, in repetitive human motions to assess the stress of those motions \cite{greene2017visualizing}, and in athletic activities for optimizing performance.
 
@@
 
-\begin{figure*}
+\begin{figure*}[h!]
 \centering
@@
 From this, we use the mean of the birth and death time of the largest persistence dot to autotune the scale $\sigma$ for the graph Laplacian, from which we derive circular coordinates $\phi$, which can be used to reorder the sliding windows and use them to vote on a final slow motion template.
-The result is shown in the bottom rightmost plot, superimposed with a ground truth period shows as an orange dotted line.}
+The result is shown in the bottom rightmost plot, superimposed with a ground truth period shown as an orange dotted line.}
 \label{fig:ConceptFigure}
@@
 \begin{equation}
-SW_{d, \tau}[X(t)] = \left[ \begin{array}{c} X(t) \\ X(t + \tau) \\ \vdots \\ X(t + (d-1)\tau)  \end{array} \right] \in \mathbb{R}^{3WHd}
+SW_{\text{dim}, \tau}[X(t)] = \left[ \begin{array}{c} X(t) \\ X(t + \tau) \\ \vdots \\ X(t + (\text{dim}-1)\tau)  \end{array} \right] \in \mathbb{R}^{3WH(\text{dim})}
 \end{equation}
 
-where $\tau$ is a step size and $d$ is the dimension of the embedding.
+where $\tau$ is a step size and ``dim'' is the dimension of the embedding.
 In this work, we fix $\tau = 1$ for simplicity and drop $\tau$ in the subscript, and we also sample times $t$ only at integer frame indices.
-As shown by Takens \cite{takens1981detecting}, a sliding window of dimension $d = 2m+1$ of even a single generic observation function (time series) of a dynamical system of intrinsic dimension $m$ is sufficient to reconstruct a topological embedding of the underlying trajectory in the original state space.
+As shown by Takens \cite{takens1981detecting}, a sliding window of dimension $2m+1$ of even a single generic observation function (time series) of a dynamical system of intrinsic dimension $m$ is sufficient to reconstruct a topological embedding of the underlying trajectory in the original state space.
 For periodic signals, this state space is a torus, and $d$ should be twice the number of harmonics present to injectively reconstruct loops on that torus \cite{perea2015sliding}.
 The same is true of videos in general \cite{tralie2017quasi}.
-Furthermore, the sliding window length $(d-1) \tau$, or simply $d-1$ in our case, maximizes the roundness of the embeddings when $d-1 = k T$ for some integer $k$, where $T$ is the fundamental period.
+Furthermore, the sliding window length $(\text{dim}-1) \tau$, or simply $\text{dim}-1$ in our case, maximizes the roundness of the embeddings when $\text{dim}-1 = k T$ for some integer $k$, where $T$ is the fundamental period.
 Since we will use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that we tune our window size to be an integer multiple of the period.
-To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D ``surrogate signal,'' and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $d$.
+To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D ``surrogate signal,'' and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate dim.
 This is quite similar to the diffusion maps + autocorrelation approach in \cite{tralie2017quasi} for analyzing periodic videos.
@@
 
-\subsection{Laplacian Eigenmaps And Persistent Homology}
+\subsection{Laplacian Eigenmaps}
 \label{sec:laplacian}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=\columnwidth]{CirculantExample.pdf}
+\caption{An example of the unweighted graph Laplacian on an ideal adjacency matrix corresponding to 6 periods of length 14 (top row), and the adjacency matrix from a sliding window embedding of two men doing jumping jacks (bottom row).
+The two eigenvectors corresponding the smallest nonzero eigenvalues of the graph Laplacian span sinusoids that are 90 degrees out of phase, and which reconstruct a circle when plotted against each other.}
+\label{fig:CirculantExample}
+\end{figure}
 
@@
 
-For a circle graph, where the $A_{ij} = 1$ if $|i-j| = 1$, $i=1, j=N$, and $j=1, i=N$, or zero otherwise, the eigenvectors spanning the image of the graph laplacian are
-
-\begin{equation}
-v_{2k}[n] = \cos(2 \pi k n / N), v_{2k-1}[n] = \sin(2 \pi k n / N), k \geq 1
-\end{equation}
-
-%In other words, the graph Laplacian of an $N$-point circle graph recovers the $N$-dimensional discrete Fourier transform.
-
-with corresponding eigenvalues $\lambda_k = 2 - 2 \cos(2 \pi k / N)$ (and $\lambda_0 = 0$ with corresponding eigenvector $v_0[n] = 1$).
-When computing the eigenvectors of a circle graph numerically, therefore, $v_1$ and $v_2$ should be a sine and cosine, or orthogonal linear combinations therein.
-
-TODO: Talk about circulant graphs instead
+Now suppose we have performed a sliding window $SW_{\text{dim}}[X[n]]$ for a video $X$, where $X[n] = X[n+kT]$ for some integers $l, k$ so that there are $kT$ points in the sliding window (that is, $X$ repeats itself exactly every $T$ frames $k$ times total), and that $d_{ij} = ||SW_{\text{dim}}[X[i]] - SW_{\text{dim}}[X[n]]||_2$.
+In this case, for any $\epsilon > 0$ and $|i - j| = kT$ for some integer $k$, $A_{ij} = 1$.
 
@@
 The first sample of each window can then be re-sorted by phase.
+
+In practice, look for the pair of eigenvectors within the first 10 with smallest zerocrossings
+
+\subsection{Persistent Homology}
 
@@
 
-\subsection{Sharpening Postprocessing}
-
-The results of the median reordering can be blurry
-
 \section{Experiments}
@@
 \subsection{Qualitative Results}
-\begin{figure}[h!]
+\begin{figure}
 \centering
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \centering

### 2018-02-01 PaperFigures.py

@@ -43,6 +43,69 @@ def getSlidingWindow(x, dim, Tau, dT):
 def MSE(x1, x2):
     return np.mean((x1-x2)**2)
 
+def getCirculantMatrix(c):
+    N = len(c)
+    A = np.zeros((N, N))
+    for i in range(N):
+        A[i] = np.roll(c, i)
+    return A
+
+def makeCirculantExample():
+    
+    #First do a synthetic example
+    T = 14
+    k = 6
+    N = k*T
+    c = np.zeros(N)
+    c[np.arange(k)*T+1] = 1
+    c[np.arange(k)*T] = 1
+    c[np.arange(k)*T-1] = 1
+    c[0] = 0
+    A = getCirculantMatrix(c)
+    w, v, L = getLaplacianEigsDense(A, A.shape[0])
+
+    plt.figure(figsize=(12, 6))
+    plt.subplot(241)
+    plt.imshow(1-A, interpolation = 'nearest', cmap = 'gray')
+    plt.title("Ideal Adj Matrix")
+    plt.xlabel("Sliding Window Frame")
+    plt.ylabel("Sliding Window Frame")
+    plt.subplot2grid((2, 4), (0, 1), colspan = 2)
+    plt.plot(v[:, 1:3])
+    plt.xlabel("Sliding Window Frame")
+    plt.title("Ideal Laplacian Eigenvectors")
+    plt.legend(['eig1', 'eig2'])
+    plt.subplot(244)
+    plt.scatter(v[:, 1], v[:, 2])
+    plt.axis('equal')
+    plt.title("Joint Plot Ideal")
+    plt.xlabel("eig 1")
+    plt.ylabel("eig 2")
+
+    #Now do an example in real video
+    I, I_feat, IDims = loadImageIOVideo('jumpingjacks2menlowres.ogg')
+    res = reorderVideo(I, I_feat, IDims, doSimple = True, Weighted = False, doPlot = False)
+    [v, A] = [res['v'], res['A']]
+    plt.subplot(245)
+    plt.imshow(1-A, interpolation = 'nearest', cmap = 'gray')
+    plt.title("Jumping SW Adj Matrix")
+    plt.xlabel("Sliding Window Frame")
+    plt.ylabel("Sliding Window Frame")
+    plt.subplot2grid((2, 4), (1, 1), colspan = 2)
+    plt.plot(v[:, 1:3])
+    plt.xlabel("Sliding Window Frame")
[…]

### 2018-02-01 RobustnessTests.py

@@ -105,7 +105,6 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
     if len(fileprefix) > 1:
         doPlot = True
     doSimple = True
-    #Range over: Period, Noise Amount, Shake Amount
     res = getCycles(NCycles = NCycles, filename = filename)
     [I, IDims, thetagt] = [res['I'], res['IDims'], res['theta']]
     I += noise*np.random.randn(I.shape[0], I.shape[1])
@@ -114,7 +113,7 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
     if saveVideos:
         saveVideo(I, IDims, "%s_simulated.avi"%fileprefix)
     ret = {}
-    for pyr_level in range(-2, 4):
+    for pyr_level in [3]:#range(-2, 4):
         if Verbose:
             print("pyr_level = %i"%pyr_level)
         if pyr_level >= 0:
@@ -123,7 +122,7 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
             depth = -pyr_level - 1
             I_feat = getVideoResNet(I, IDims, depth)
         for Kappa in [0, 0.05, 0.1, 0.15]:
-            for Weighted in [True, False]:
+            for Weighted in [False]:
                 for doSlidingWindow in [True, False]:
                     thisprefix = "%i_%i_%g_%i"%(doSlidingWindow, pyr_level, Kappa, Weighted)
                     res = reorderVideo(I, I_feat, IDims, derivWin = 0, Weighted = Weighted, \
@@ -168,19 +167,18 @@ def writeBatchHeaderCSV(fout, filename):
 
 def doBatchTests(filename, fout, batchidx = -1):
     idx = 0
-    for NCycles in [3, 5, 10, 20, 30, 50, 70, 100, 200]: #[3, 5, 10, 15, 20, 25, 30, 40, 50]
-        for noise in [0, 1, 2, 3]:
-            for shake in [0, 20, 40, 80]:
-                for trial in range(10):
-                    if idx == batchidx:
-                        np.random.seed(idx)
-                        ret = doTest(filename, NCycles, noise, shake, Verbose = True)
-                        for item in ret:
-                            fout.write("%i,%g,%i,%i,"%(NCycles, noise, shake, trial))
-                            fout.write(("%s,"*4)%tuple(item.split("_")))
[…]

### 2018-02-01 VideoReordering.py

@@ -337,7 +337,7 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
         else:
             XRet = getReorderedConsensusVideo(X_proj, IDims, Mu_orig, VT_orig, dim, thetau, \
                 doPlot=doPlot, Verbose=Verbose, lookAtVotes = False, tdifflim = tdifflim)
-    return {'X':XRet, 'IDims':IDims, 'theta':theta, 'thetau':thetau}
+    return {'X':XRet, 'IDims':IDims, 'theta':theta, 'thetau':thetau, 'A':A, 'v':v}
 
 def get_out_fileprefix(base_filename, inputfilename, do_simple, is_weighted, \
                         is_net_feat, pyr_level=0, layer=0, Kappa=0):

### 2018-02-02 Paper/paper.tex
Finally wrote up the correct equation for the eigenvalues in my model

@@
 Our use of the graph Laplcian to parameterize time series is also unique, though we are inspired by works that have used it to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and works which use vector diffusion maps to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.
-We use the combination of TDA + Laplacian eigenmaps as a simple alternative to the more complicated cohomology circular coordinates proposed by the authors of \cite{de2011persistent} and used on motion capture data \cite{vejdemo2015cohomological}.
+One can also view the combination of TDA + Laplacian eigenmaps as a simple alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} in the special case of periodic data.
 
@@
 To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D ``surrogate signal,'' and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate dim.
-This is quite similar to the diffusion maps + autocorrelation approach in \cite{tralie2017quasi} for analyzing periodic videos.
+This is similar to the diffusion maps + autocorrelation approach in \cite{tralie2017quasi} for analyzing periodic videos.
 This estimation often returns integer multiples of the fundamental period, which is fine for our purposes.
@@
 \caption{An example of the unweighted graph Laplacian on an ideal adjacency matrix corresponding to 6 periods of length 14 (top row), and the adjacency matrix from a sliding window embedding of two men doing jumping jacks (bottom row).
-The two eigenvectors corresponding the smallest nonzero eigenvalues of the graph Laplacian span sinusoids that are 90 degrees out of phase, and which reconstruct a circle when plotted against each other.}
+}
 \label{fig:CirculantExample}
 \end{figure}
+%The two eigenvectors corresponding the smallest nonzero eigenvalues of the graph Laplacian span sinusoids that are 90 degrees out of phase, and which reconstruct a circle when plotted against each other.
 
@@
 
-Now suppose we have performed a sliding window $SW_{\text{dim}}[X[n]]$ for a video $X$, where $X[n] = X[n+kT]$ for some integers $l, k$ so that there are $kT$ points in the sliding window (that is, $X$ repeats itself exactly every $T$ frames $k$ times total), and that $d_{ij} = ||SW_{\text{dim}}[X[i]] - SW_{\text{dim}}[X[n]]||_2$.
-In this case, for any $\epsilon > 0$ and $|i - j| = kT$ for some integer $k$, $A_{ij} = 1$.
+Now suppose we have performed a sliding window $SW_{\text{dim}}[X[n]]$ for a video $X$, where $X[n] = X[n+kT]$ for some integers $l, k$ so that there are $kT$ points in the sliding window (that is, $SW_{\text{dim}}[X[i]]$ repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows), and that $d_{ij} = ||SW_{\text{dim}}[X[i]] - SW_{\text{dim}}[X[j]]||_2$.
+In this case, for any $\epsilon > 0$ and $|i - j| = kT$ for some integer $k$, $A^u_{\epsilon}(d)_{ij} = 1$.
+Let us further suppose it is possible to choose an $\epsilon$ so that each window is connected to the window directly before and after it in time, as well as the windows directly before and after its repetitions, but none others; that is, the unweighted adjacency matrix is a symmetric, {\em circulant matrix}, with the first row $A_{\epsilon}^u(d)_{1j} = 1$ if $j = 1, N-1,$ or $lT, 1 \leq l \leq (k-1)$.
+Thus, the Laplacian is also circulant with first row
+
+\begin{equation}
+\label{eq:modellaplacian}
+L_{1j} = \left\{ \begin{array}{cc} 3k-1 & j = 1 \\ -1 & j = lT, 1 \leq l \leq (k-1) \\ -1 & j = 1, N-1 \\ 0 & \text{otherwise} \end{array} \right\}
+\end{equation}
+
+Circulant matrices are diagonalized by the Discrete Fourier Transform \cite{godsil2013algebraic}, and their eigenvalues come in pairs with multiplicity two, with corresopnding eigenvectors $v_1[n] = 1$, $v_{2m}[n] = \cos(2 \pi mn / N)$, $v_{2m+1}[n] = \sin(2 \pi m n / N)$, $m \geq 1$.
+In the case of Equation~\ref{eq:modellaplacian}, it can be shown using the DFT that the eigenvalues are $\lambda_1 = 0$ and
+
+\begin{equation}
+\begin{array}{cc}\lambda_{2m},\\\lambda_{2m+1}\end{array} = \left\{ \begin{array}{cc} 3k - k\left( 1 + 2 \cos \left( \frac{2 \pi}{kT} m \right) \right) & m = lk, l \in \mathbb{Z}^+ \\ 3k & \text{otherwise}  \end{array} \right\}
+\end{equation}
+
+The smallest two nonzero eigenvalues occur when $m = k$, corresponding to the eigenvectors $v_{2k} = \cos(2 \pi n / T), v_{2k+1} = \sin(2 \pi n / T)$
 

### 2018-02-03 Paper/paper.tex
Finished the majority of the writing, and added robustness tests bar graphs

@@
 Furthermore, as shown by the authors of \cite{tralie2017quasi}, sliding window embeddings on Eulerian videos provide a sort of ``time regularization,'' which can mitigate the effects of drift, leading to a cleaner loop.
-Our geometric framework also allows us to use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} and fundamental frequency estimation \cite{Mcleod05asmarter} to autotune the temporal and spatial scales of the periodic motion, respectively, so that no user intervention is required.
+Our geometric framework also allows us to use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} and fundamental frequency estimation \cite{Mcleod05asmarter} to autotune the spatial and temporal scales of the periodic motion, respectively, so that no user intervention is required.
 Our embedding also makes it easy to assign each window a circular phase $\phi \in [0, 2\pi]$ using Laplacian Eigenmaps \cite{belkin2003laplacian}.
@@
 Our use of the graph Laplcian to parameterize time series is also unique, though we are inspired by works that have used it to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and works which use vector diffusion maps to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.
-One can also view the combination of TDA + Laplacian eigenmaps as a simple alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} in the special case of periodic data.
+One can also view the combination of TDA + Laplacian eigenmaps as a simpler alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} for the special case of periodic data.
+It is also the opposite of the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA.
 
@@
 Now let $d_{ij}: V \rightarrow \mathbb{R}^+$ be a nonnegative scalar function on the vertices of $G$.
-Then the adjacency matrix correponding to the {\em unweighted} graph Laplacain, $A_{\epsilon}^u(d)$, is
+Then the adjacency matrix correponding to the unweighted graph Laplacain, $A_{\epsilon}^u(d)$, is
 
@@
 
+Alternatively, the weighted adjacency matrix is defined as $A_{\epsilon}^w(d)_{ij} = \exp(-d_{ij}^2/\epsilon)$ \cite{belkin2003laplacian}, but everything else is the same.
 Now suppose we have performed a sliding window $SW_{\text{dim}}[X[n]]$ for a video $X$, where $X[n] = X[n+kT]$ for some integers $l, k$ so that there are $kT$ points in the sliding window (that is, $SW_{\text{dim}}[X[i]]$ repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows), and that $d_{ij} = ||SW_{\text{dim}}[X[i]] - SW_{\text{dim}}[X[j]]||_2$.
 In this case, for any $\epsilon > 0$ and $|i - j| = kT$ for some integer $k$, $A^u_{\epsilon}(d)_{ij} = 1$.
-Let us further suppose it is possible to choose an $\epsilon$ so that each window is connected to the window directly before and after it in time, as well as the windows directly before and after its repetitions, but none others; that is, the unweighted adjacency matrix is a symmetric, {\em circulant matrix}, with the first row $A_{\epsilon}^u(d)_{1j} = 1$ if $j = 1, N-1,$ or $lT, 1 \leq l \leq (k-1)$.
+Let us further suppose it is possible to choose an $\epsilon$ so that each window is also connected to the window directly before and after it in time, as well as the windows directly before and after its repetitions, but none others; that is, the unweighted adjacency matrix is a symmetric, {\em circulant matrix}, with the first row $A_{\epsilon}^u(d)_{1j} = 1$ if $j = 1, N-1,$ or $lT, 1 \leq l \leq (k-1)$.
 Thus, the Laplacian is also circulant with first row
@@
 
-Circulant matrices are diagonalized by the Discrete Fourier Transform \cite{godsil2013algebraic}, and their eigenvalues come in pairs with multiplicity two, with corresopnding eigenvectors $v_1[n] = 1$, $v_{2m}[n] = \cos(2 \pi mn / N)$, $v_{2m+1}[n] = \sin(2 \pi m n / N)$, $m \geq 1$.
+Circulant matrices are diagonalized by the Discrete Fourier Transform \cite{godsil2013algebraic}, and their nonzero eigenvalues come in pairs with multiplicity two, with corresopnding eigenvectors $v_1[n] = 1$, $v_{2m}[n] = \cos(2 \pi mn / N)$, $v_{2m+1}[n] = \sin(2 \pi m n / N)$, $m \geq 1$.
 In the case of Equation~\ref{eq:modellaplacian}, it can be shown using the DFT that the eigenvalues are $\lambda_1 = 0$ and
@@
 
-The smallest two nonzero eigenvalues occur when $m = k$, corresponding to the eigenvectors $v_{2k} = \cos(2 \pi n / T), v_{2k+1} = \sin(2 \pi n / T)$
+The smallest two nonzero eigenvalues occur when $m = k$, corresponding to the eigenvectors \footnote{This generalizes the circle graph used in \cite{averbuch2015ringit}, in which $T = N, k = 1$} 
+\begin{equation}
+v_{2k}[n] = \cos(2 \pi n / T), v_{2k+1}[n] = \sin(2 \pi n / T)
+\end{equation}
+When computing the smallest two nonzero eigenvalues numerically, therefore, one coresponds to a sinusoid with period $T$, and the other to an orthogonal sinusoid with period $T$.
+When plotted against each other, they form a circle, with an arbitrary phase offset.
+Therefore, we compute the circular phase numerically $\phi = \tan^{-1}(\hat{v_1}[n] / \hat{v_2}[n])$, where $\hat{v_i}$ is the eigenvector corresponding to the $i^\text{th}$ smallest nonzero numerical eigenvalue.
+In practice, the graphs we get from sliding window may deviate from the ideal Laplacian model in Equation~\ref{eq:modellaplacian}, though they do so gracefully.
+Figure~\ref{fig:CirculantExample} shows an example of $\hat{v_1}[n]$ and $\hat{v_2}[n]$ for an ideal graph and for an imperfect graph corresponding to the sliding window embedding of a real video.
 
-which means the first two nonzero eigenvectors should be a sine and cosine, or orthogonal linear combinations therein.
-When plotted against each other, they make an approximate circle, and the arctangent of the two eigenvector coordinates at every window can be used to determine the {\em phase} of the corresponding window in the periodic signal.
-The first sample of each window can then be re-sorted by phase.
-
-In practice, look for the pair of eigenvectors within the first 10 with smallest zerocrossings
+Note that for both the unweighted and weighted cases in practice, we have observed that harmonics of the actual frequency of interest occasionally have smaller eigenvalues.
+To mitigate this, we use the pair of eigenvectors with the smallest number of zero crossings within the eigenvectors corresponding to the 10 smallest nonzero eigenvalues.
 
 \subsection{Persistent Homology}
-
-Talk about autotuning with peristent homology, mention that it's the opposite of the approach in \cite{bendich2011improving}
-
-Talk about how it can pick up on harmonics (e.g. jumping jacks), which is why this is important (talk about using prime 49)
+Our discussion so far has assumed we can find the appropriate $\epsilon$ for the (un)weighted graph Laplacian, but this is data dependent.
+The authors of \cite{averbuch2015ringit} use $k$-nearest neighbors, which helps with scale, but which still requires an arbitrary parameter $k$.
+To adapt to the data, we 1D leverage persistent homology from topological data analysis \cite{edelsbrunner2010computational}.
+Roughly, this framework allows one to find the scale at which topological features exist in point cloud data.
+Specifically, we compute the ``1D Vietoris Rips Filtration'' on our sliding window data $X$, which tracks equivalence classes of loops, known as {\em homology classes} \cite{Hatcher}, as edges and triangles are gradually added between sliding window points.
+The algorithm returns a ``persistence diagram,'' which is a multiset of points on a 2D birth/death grid, with each point corresponding a loop class.
+The birth value $b_i$ indicates the scale $\epsilon$ at which the $i^{\text{th}}$ loop class forms, and the death value $d_i$ indicates the scale at which that class is ``filled in'' (expressible as a formal sum of triangle boundaries with coefficients in some field).
+$d_i - b_i$ is known as the {\em persistence} of the $i^{\text{th}}$ class.
+For sliding window periodic time series, one point in the diagram should have a much larger persistence than the others (e.g.
+Figure~\ref{fig:ConceptFigure}) \cite{perea2015sliding,tralie2017quasi}.
+We take our scale to be $\frac{1}{2}(b_i + d_i)$ for the largest $d_i - b_i$.
+Finally, note that we compute homology using $\mathbb{Z}_{49}$ coefficients to handle cases where a period has strong harmonics, since, choosing a field which is not relatively prime to a harmonic leads to lowered persistence \cite{perea2015sliding, traliemoebius}.
+For instance, a jumping jacks motion has a second harmonic, since an individual jumps twice per cycle, so the common persistence algorithm with $\mathbb{Z}_2$ coefficients would lead to ``M{\"o}bius splitting'' \cite{traliemoebius}.
 
@@
 
+Mention the ``F'' parameter in the pipeline
+
 \section{Experiments}
@@
 \subsection{Robustness Tests}
-Robustness experiments
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{RobustnessTests.pdf}
+\caption{Robustness tests.}
+\label{fig:RobustnessTests}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{RobustnessTestsNoSW.pdf}
+\caption{Robustness tests without sliding window.}
+\label{fig:RobustnessTestsNoSW}
+\end{figure}
+
+We now experimentally quantify the accuracy of our circular coordinate inference, since we cannot hope to get a good slow motion template unless our circular coordinates are accurate.
+We generate 3 different 600 frame synthetic periodic videos for which we know the ground truth circular coordinates, using software from \cite{jacobson2012fast}.
+We vary the number of cycles that the videos undergo between 3, 5, 10, 15, 20, 25, 30, 40, and 50, and we also vary the ``shake'' of the video (width of a motion blur kernel) from 0, $20 \times 20$, $40 \times 40$, and $80 \times 80$, to assess the effect of drift.
+We also compare different fractions $\kappa$ of mutual nearest neighbors to tune the threshold at which the unweighted Laplacian is built to TDA for aututuning the scale.
+Figure~\ref{fig:RobustnessTests} shows the average angular error in degrees for our entire pipeline, and Figure~\ref{fig:RobustnessTests}.
+The errors are overall quite low for moderate shake with a sliding window, though they increase as more shake is introduced.
+Without a sliding window, the only video that performs reasonably well is the ``crowd'' videom, though the errors increase with shake much more rapidly than with the sliding window, supporting the ``time regularization'' properties of the sliding window.
 
@@
 
+We now qualitatively examine the results of our slow motion templates on some examples.
 Figure~\ref{fig:XTSliceJumpingJacks} shows the difference between a simple reordering and a median consensus reordering.
@@
 By contrast, the median voting is clean, and it has the added benefit of removing nonperiodic background components.
-
-umping jacks 2 men, two exercise videos from \cite{levy2015live}, beating heart videos from \cite{traliehigh}, \cite{wu2012eulerian}, and \cite{wadhwa2013phase}.
+Figure~\ref{fig:XTSliceFan} shows an extreme example in which an original spinning fan video has only 6 frames per period at framerate.
+In addition to these examples, in our supplementary material, we show results from jumping jacks 2 men, two exercise videos from \cite{levy2015live}, and beating heart videos from \cite{traliehigh}, \cite{wu2012eulerian}, and \cite{wadhwa2013phase}.
 

### 2018-02-03 PaperFigures.py

@@ -73,7 +73,7 @@ def makeCirculantExample():
     plt.subplot2grid((2, 4), (0, 1), colspan = 2)
     plt.plot(v[:, 1:3])
     plt.xlabel("Sliding Window Frame")
-    plt.title("Ideal Laplacian Eigenvectors")
+    plt.title("Numerical Ideal Laplacian Eigenvectors")
     plt.legend(['eig1', 'eig2'])
     plt.subplot(244)
     plt.scatter(v[:, 1], v[:, 2])

### 2018-02-03 Paper/paper.tex
pass on intro

@@
 
+\usepackage{tikz}
+
 \graphicspath{{Figures/}}
@@
 \newcommand{\argmax}{\operatornamewithlimits{argmax}}
+\newcommand{\matt}[1]{{\color{purple}[MSB: #1]}}
 
@@
 
-Repetitive, periodic motions are ubiquitous in our world, such as animal locomotion (walking/flapping/slithering/swimming), mechanical motions (wheels spinning, pistons oscillating), biological rhythms (heartbeat, breathing), musical rhythms (drumming, feet tapping), etc.
-In this work, we consider the problem of synthesizing a fine detail, ``slow motion'' template cycle of motion from a video of such a motion with many periods.
+Repetitive, periodic behavior is ubiquitous in our world.
+Animal locomotion, mechanical motion, biological rhythms, and musical rhythms can all be characterized as periodic phenomena.
+In this work, we consider the problem of taking a video that contains such repetitive motion of many periods, and synthesizing a single fine detail, slow motion template cycle.
 This fine detailed analysis can be applied, for example, to characterize subtle progressions of blood flow in the face during a heartbeat \cite{kumar2015distanceppg}.
-Having access to a consensus template can also be used to visualize variations from cycle to cycle, such as in a repetitive automated action on an assembly line, where too much variation could indicate the onset of failure, in repetitive human motions to assess the stress of those motions \cite{greene2017visualizing}, and in athletic activities for optimizing performance.
+Having access to a consensus template can also be used to visualize variations from cycle to cycle.
+This could be used to indicate the onset of failure in a repetitive automated action on an assembly line, to assess the stress of motions in repetitive human actions~\cite{greene2017visualizing}, and to optimize performance in athletic activities.
 
@@
 There are some pitfalls with Eulerian techniques, however.
-Purely Eulerian amplification techniques are known to fail for large motions, and they also require the user to manually specify frequencies of interest \cite{wu2012eulerian, wadhwa2013phase}.
-Furthermore, drift from period to period due to shaking and varying motions from cycle to cycle can present a problem, as can unrelated motion in the background \cite{stauffer1999adaptive}.
+They are known to fail for large motions, and also require the user to manually specify frequencies of interest \cite{wu2012eulerian, wadhwa2013phase}.
+Furthermore, period-to-period drift that is due to a moving camera or small variation in motion can be problematic, as well as unrelated motion in the background \cite{stauffer1999adaptive}.
 
-To address the problems with an Eulerian representation, we devise a geometric/topological Eulerian framework byconstructing {\em sliding window embeddings} of our videos (Section~\ref{sec:slidingwindow}).
-Sliding window embeddings, or ``delay reconstructions,'' have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
+% MSB: opportunity to slim paper by cutting examples 
+To address the problems with an Eulerian representation, we devise a geometric/topological Eulerian framework by constructing {\em sliding window embeddings} of videos (Section~\ref{sec:slidingwindow}).
+Sliding window embeddings, or delay reconstructions, have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
 Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data, regardless of the type of motion present \cite{traliehigh, tralie2017quasi}.
-Furthermore, as shown by the authors of \cite{tralie2017quasi}, sliding window embeddings on Eulerian videos provide a sort of ``time regularization,'' which can mitigate the effects of drift, leading to a cleaner loop.
+Furthermore, the sliding window embedding of an Eulerian video provides a form of regularization that mitigates the effects of drift and leads to a cleaner loop~\cite{tralie2017quasi}.
 Our geometric framework also allows us to use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} and fundamental frequency estimation \cite{Mcleod05asmarter} to autotune the spatial and temporal scales of the periodic motion, respectively, so that no user intervention is required.
-Our embedding also makes it easy to assign each window a circular phase $\phi \in [0, 2\pi]$ using Laplacian Eigenmaps \cite{belkin2003laplacian}.
-We then re-order the sliding windows by $\phi$ and exploit the sliding window structure to have different windows vote on the final pixels in each frame of the template, which further mitigates drift (Section~\ref{sec:cyclereordering}).
+We use Laplacian Eigenmaps~\cite{belkin2003laplacian} computed on the sliding window embedding to obtain a circular phase $\phi \in [0, 2\pi]$ for each point in the embedding.
+The video is re-ordered by using $\phi$ and exploiting the sliding window structure, where different windows vote on the final pixels in each frame of the template, helping to further mitigate drift (Section~\ref{sec:cyclereordering}).
 As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled periodic time series (i.e.
 single pixel grayscale video).
-There are only 12 samples per period in the original signal, so the details of each period coarse and noisy.
-However, once they are re-sorted, we get a nice, fine-detailed representation of one period.
+There are only 12 samples per period in the original signal, so the details of each period are coarse and noisy.
+However, once they are re-sorted, we get a fine-detailed representation of one period.
 The extension of this technique to videos will be described in detail in Section~\ref{sec:methods}.
 
+% MSB: opportunity to slim paper by cutting examples 
 Many prior works use a combination of sliding window embeddings and topological data analysis, such as detecting the Lorenz attractor \cite{de2012topological}, quantifying circadian rhythms in gene expression data \cite{perea2015sliding}, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, and quantifying vocal fold anomalies in video \cite{tralie2017quasi}, though we believe we are the first to use a sliding window + TDA framework to {\em synthesize} a new result.
-Our use of the graph Laplcian to parameterize time series is also unique, though we are inspired by works that have used it to re-arrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and works which use vector diffusion maps to re-order the frames of microscope images a developing embryo around a loop \cite{dsilva2015diffusionvecordering}.
+Related works have used the graph Laplacian to rearrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and to reorder the frames of microscope images from a developing embryo around a loop using vector diffusion maps~\cite{dsilva2015diffusionvecordering}.
+However, our use of the graph Laplacian to instead {\em parameterize} time series is unique.
 One can also view the combination of TDA + Laplacian eigenmaps as a simpler alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} for the special case of periodic data.
 It is also the opposite of the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA.
+\matt{unclear what ''It'' refers to in this last sentence}
 

### 2018-02-04 Paper/paper.tex
revised forematter of section 2

@@
 Our geometric framework also allows us to use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} and fundamental frequency estimation \cite{Mcleod05asmarter} to autotune the spatial and temporal scales of the periodic motion, respectively, so that no user intervention is required.
-We use Laplacian Eigenmaps~\cite{belkin2003laplacian} computed on the sliding window embedding to obtain a circular phase $\phi \in [0, 2\pi]$ for each point in the embedding.
+We use Laplacian Eigenmaps~\cite{belkin2003laplacian} computed on the sliding window embedding to obtain a circular phase $\phi \in [0, 2\pi]$ for each window.
 The video is re-ordered by using $\phi$ and exploiting the sliding window structure, where different windows vote on the final pixels in each frame of the template, helping to further mitigate drift (Section~\ref{sec:cyclereordering}).
@@
 
-We now describe our algorithm in several stages.
+Figure~\ref{fig:ConceptFigure} depicts an overview of our method.
+First we estimate the period of the cycle, and use this to compute the sliding window embedding (a).
+Next we estimate the spatial scale of the embedding using persistent homology (b).
+Given the scale, we then compute a single-cycle reordering of the embedding using Laplacian Eigenmaps (c).
+Last, we use the reordered embedding to reorder the original video through median voting of windows (d).
+
+\textbf{Preprocessing.} The input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$.
+We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mathbf{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$.
+The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}(a-c), however, do not rely on the {\em extrinsic} geometry of the set of points $\mathbf{X}(t)$, only its set of {\em pairwise distances}.
+Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that the projection preserves pairwise distances.
+Since $N \ll (3 \cdot W \cdot H)$, we can easily project all frames into a $N-1$-dimensional space such that all distances are preserved.
+Denoting this projection by $\mathbf{P} \in \mathbb{R}^{(3 \cdot W \cdot H) \times (N-1)}$, our method for steps (a)-(c) operates on $\mathbf{Z}(t) = \mathbf{P} \mathbf{X}(t)$.
+
+%We now describe our algorithm in several stages.
 Throughout our discussion, we assume we are given 3 channel color videos with $W \times H$ resolution frames, so that each frame is a Euclidean vector in $\mathbb{R}^{W \times H \times 3}$.

### 2018-02-04 Paper/paper.tex
small tweak

@@
 The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}(a-c), however, do not rely on the {\em extrinsic} geometry of the set of points $\mathbf{X}(t)$, only its set of {\em pairwise distances}.
-Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that the projection preserves pairwise distances.
-Since $N \ll (3 \cdot W \cdot H)$, we can easily project all frames into a $N-1$-dimensional space such that all distances are preserved.
+Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that pairwise distances are preserved.
+Since $N \ll (3 \cdot W \cdot H)$, the frames can be projected into a $N-1$-dimensional space such that all distances are preserved.
 Denoting this projection by $\mathbf{P} \in \mathbb{R}^{(3 \cdot W \cdot H) \times (N-1)}$, our method for steps (a)-(c) operates on $\mathbf{Z}(t) = \mathbf{P} \mathbf{X}(t)$.

### 2018-02-04 Laplacian.py
Updating figure, doing robustness experiments with weighted percentile

@@ -124,16 +124,22 @@ def getLapCircularCoordinatesThresh(pD, thresh, NEigs = 10, doPlot = False):
     (theta, thetau) = getLapThetas(v, i1, i1+1)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
 
-def getLapCircularCoordinatesKNN(D, Kappa, NEigs = 10, doPlot = False):
+def getLapCircularCoordinatesKNN(D, Kappa, NEigs = 10, percentile = True, doPlot = False):
     """
     Get circular coordinates using a weighted laplacian 
     :param pD: Distance matrix
     :param Kappa: Percentage of mutual nearest neighbors
     :param NEigs: Maximum number of eigenvectors to compute
+    :param percentile: Whether to use percentile or tuned mutual nearest neighbors
     :return {'w':eigenvalues, 'v':eigenvectors, 'theta':Circular coordinates,\
             'thetau':Unwrapped circular coordinates, 'A':Adjacency matrix}
     """
-    A = CSMToBinaryMutual(D, Kappa)
+    if percentile:
+        ds = np.sort(D.flatten())
+        sigma = ds[int(Kappa*len(ds))]
+        A = D <= sigma
+    else:
+        A = CSMToBinaryMutual(D, Kappa)
     np.fill_diagonal(A, 0)
     NEigs = min(NEigs, A.shape[0])
     (w, v, L) = getLaplacianEigsDense(A, NEigs)
@@ -153,18 +159,23 @@ def getLapCircularCoordinatesKNN(D, Kappa, NEigs = 10, doPlot = False):
     (theta, thetau) = getLapThetas(v, i1, i1+1)
     return {'w':w, 'v':v, 'theta':theta, 'thetau':thetau, 'A':A, 'idxs':[i1, i1+1]}
 
-def getLapCircularCoordinatesKNNWeighted(D, Kappa, NEigs = 10, doPlot = False):
+def getLapCircularCoordinatesKNNWeighted(D, Kappa, NEigs = 10, percentile = True, doPlot = False):
     """
     Get circular coordinates using a weighted laplacian 
     :param pD: Distance matrix
     :param Kappa: Percentage of mutual nearest neighbors
     :param NEigs: Maximum number of eigenvectors to compute
[…]

### 2018-02-04 RobustnessTests.py

@@ -122,35 +122,38 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
             depth = -pyr_level - 1
             I_feat = getVideoResNet(I, IDims, depth)
         for Kappa in [0, 0.05, 0.1, 0.15]:
-            for Weighted in [False]:
-                for doSlidingWindow in [True, False]:
-                    thisprefix = "%i_%i_%g_%i"%(doSlidingWindow, pyr_level, Kappa, Weighted)
-                    res = reorderVideo(I, I_feat, IDims, derivWin = 0, Weighted = Weighted, \
-                                        doSimple = doSimple, doPlot = doPlot, Verbose = Verbose, \
-                                        doImageAnalogies = False, Kappa = Kappa, \
-                                        fileprefix = fileprefix+thisprefix, returnAnswer = False, \
-                                        doSlidingWindow = doSlidingWindow)
-                    theta = np.mod(res['thetau'], 2*np.pi)
-                    thetagt = thetagt[0:len(theta)]
-                    theta = theta[0:len(thetagt)]
-                    circErr = np.mean(getCircleDist(theta, thetagt))
-                    rank1 = 0*thetagt
-                    rank1[np.argsort(thetagt)] = np.arange(len(rank1))
-                    rank2 = 0*rank1
-                    rank2[np.argsort(theta)] = np.arange(len(rank2))
-                    kendTau = getKendallTauCircle(rank1, rank2)
-                    ret[thisprefix] = [circErr, kendTau]
-                    if doPlot:
-                        plt.figure(figsize=(8, 6))
-                        plt.subplot(211)
-                        plt.scatter(thetagt, theta)
-                        plt.title("err = %.3g"%circErr)
-                        plt.subplot(212)
-                        plt.scatter(rank1, rank2)
-                        plt.title("$\\tau = %.3g$"%kendTau)
-                        plt.savefig("%s_CircCoordsCorr.svg"%(fileprefix+thisprefix), bbox_inches = 'tight')
-                    if saveVideos:
-                        saveVideo(res['X'], IDims, (fileprefix+thisprefix)+".avi")
+            for Weighted in [True]:
+                for percentile in [False, True]:
+                    for doSlidingWindow in [True, False]:
+                        thisprefix = "%i_%i_%g_%i_%i"%(doSlidingWindow, pyr_level, Kappa, Weighted, percentile)
[…]

### 2018-02-04 VideoReordering.py

@@ -197,8 +197,8 @@ def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = 20):
 
 def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
                 doSimple = False, doImageAnalogies = False, doPlot = True, \
-                Verbose = False, fileprefix = "", Kappa = -1, p = 41, \
-                returnAnswer = True, doSlidingWindow = True, \
+                Verbose = False, fileprefix = "", Kappa = -1, percentile = True,
+                p = 41, returnAnswer = True, doSlidingWindow = True, \
                 expandWindow = False, tdifflim = -1):
     """
     Reorder the video based on circular coordinates of a sliding
@@ -259,9 +259,9 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
 
     if Kappa > 0 and Kappa < 1:
         if Weighted:
-            res = getLapCircularCoordinatesKNNWeighted(D, Kappa)
+            res = getLapCircularCoordinatesKNNWeighted(D, Kappa, percentile = percentile)
         else:
-            res = getLapCircularCoordinatesKNN(D, Kappa)
+            res = getLapCircularCoordinatesKNN(D, Kappa, percentile = percentile)
     else:
         if Verbose:
             print("Computing H1 on point cloud of size %i..."%D.shape[0])
@@ -270,8 +270,12 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
         if Verbose:
             print("Elapsed Time H1: %g"%(time.time() - tic))
         I = Is[1]
-        thresh = np.argmax(I[:, 1] - I[:, 0])
-        thresh = np.mean(I[thresh, :])
+        imax = np.argmax(I[:, 1] - I[:, 0])
+        if Weighted:
+            thresh = I[imax, 0]
+        else:
+            alpha = 0.5
+            thresh = alpha*I[imax, 0] + (1-alpha)*I[imax, 1]
         tic = time.time()
         if Weighted:
             if doPlot:
@@ -293,7 +297,13 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
         plt.title("Adjacency Matrix")
         plt.subplot(233)
         if not (Kappa > 0 and Kappa < 1):
-            plotDGM(I)
[…]

### 2018-02-04 Laplacian.py
Updating Laplacian plots to include eigenvalues

@@ -79,15 +79,19 @@ def getLapCircularCoordinatesSigma(D, sigma, NEigs = 10, doPlot = False):
     (w, v, L) = getLaplacianEigsDense(A, NEigs)
     (i1, zcs) = getSlowestEigenvectorIdx(v)
     if doPlot:
-        plt.subplot(311)
+        plt.subplot(411)
         plt.imshow(v, cmap = 'afmhot', interpolation = 'nearest', aspect = 'auto')
-        plt.xlim([0, v.shape[1]])
+        plt.xlim([0, v.shape[1]-1])
         plt.title("Eigenvectors")
-        plt.subplot(312)
+        plt.subplot(412)
+        plt.stem(w)
+        plt.xlim([0, v.shape[1]-1])
+        plt.title("Eigenvalues")
+        plt.subplot(413)
         plt.plot(zcs)
+        plt.xlim([0, v.shape[1]-1])
         plt.title("Zero Crossings, Smallest = (%i, %i)"%(i1, i1+1))
-        plt.xlim([0, v.shape[1]])
-        plt.subplot(313)
+        plt.subplot(414)
         plt.plot(v[:, [i1, i1+1]])
         plt.legend(["%i"%i1, "%i"%(i1+1)])
     (theta, thetau) = getLapThetas(v, i1, i1+1)
@@ -110,15 +114,19 @@ def getLapCircularCoordinatesThresh(pD, thresh, NEigs = 10, doPlot = False):
     (w, v, L) = getLaplacianEigsDense(A, NEigs)
     (i1, zcs) = getSlowestEigenvectorIdx(v)
     if doPlot:
-        plt.subplot(311)
+        plt.subplot(411)
         plt.imshow(v, cmap = 'afmhot', interpolation = 'nearest', aspect = 'auto')
-        plt.xlim([0, v.shape[1]])
+        plt.xlim([0, v.shape[1]-1])
         plt.title("Eigenvectors")
-        plt.subplot(312)
+        plt.subplot(412)
+        plt.stem(w)
+        plt.xlim([0, v.shape[1]-1])
+        plt.title("Eigenvalues")
+        plt.subplot(413)
         plt.plot(zcs)
+        plt.xlim([0, v.shape[1]-1])
         plt.title("Zero Crossings, Smallest = (%i, %i)"%(i1, i1+1))
-        plt.xlim([0, v.shape[1]])
-        plt.subplot(313)
[…]

### 2018-02-04 RobustnessTests.py
Adding GUDHI reference, changing batch tests to go through Alpha instead of Kappa

@@ -121,39 +121,36 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
         else:
             depth = -pyr_level - 1
             I_feat = getVideoResNet(I, IDims, depth)
-        for Kappa in [0, 0.05, 0.1, 0.15]:
+        for Alpha in [0, 0.25, 0.5, 0.75, 1.0]:
             for Weighted in [True]:
-                for percentile in [False, True]:
-                    for doSlidingWindow in [True, False]:
-                        thisprefix = "%i_%i_%g_%i_%i"%(doSlidingWindow, pyr_level, Kappa, Weighted, percentile)
-                        res = reorderVideo(I, I_feat, IDims, derivWin = 0, Weighted = Weighted, \
-                                            doSimple = doSimple, doPlot = doPlot, Verbose = Verbose, \
-                                            doImageAnalogies = False, Kappa = Kappa, percentile = percentile, \
-                                            fileprefix = fileprefix+thisprefix, returnAnswer = False, \
-                                            doSlidingWindow = doSlidingWindow)
-                        if percentile and Kappa == 0:
-                            continue #Percentile means nothing for TDA
-                        theta = np.mod(res['thetau'], 2*np.pi)
-                        thetagt = thetagt[0:len(theta)]
-                        theta = theta[0:len(thetagt)]
-                        circErr = np.mean(getCircleDist(theta, thetagt))
-                        rank1 = 0*thetagt
-                        rank1[np.argsort(thetagt)] = np.arange(len(rank1))
-                        rank2 = 0*rank1
-                        rank2[np.argsort(theta)] = np.arange(len(rank2))
-                        kendTau = getKendallTauCircle(rank1, rank2)
-                        ret[thisprefix] = [circErr, kendTau]
-                        if doPlot:
-                            plt.figure(figsize=(8, 6))
-                            plt.subplot(211)
-                            plt.scatter(thetagt, theta)
-                            plt.title("err = %.3g"%circErr)
-                            plt.subplot(212)
-                            plt.scatter(rank1, rank2)
-                            plt.title("$\\tau = %.3g$"%kendTau)
-                            plt.savefig("%s_CircCoordsCorr.svg"%(fileprefix+thisprefix), bbox_inches = 'tight')
[…]

### 2018-02-04 Paper/paper.tex
Adding GUDHI reference, changing batch tests to go through Alpha instead of Kappa
probably conflicts

@@
 \newcommand{\matt}[1]{{\color{purple}[MSB: #1]}}
+\newcommand{\mb}{\mathbf}
 
@@
 \textbf{Preprocessing.} The input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$.
-We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mathbf{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$.
-The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}(a-c), however, do not rely on the {\em extrinsic} geometry of the set of points $\mathbf{X}(t)$, only its set of {\em pairwise distances}.
+We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mb{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$.
+The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}(a-c), however, do not rely on the {\em extrinsic} geometry of the set of points $\mb{X}(t)$, only its set of {\em pairwise distances}.
 Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that pairwise distances are preserved.
 Since $N \ll (3 \cdot W \cdot H)$, the frames can be projected into a $N-1$-dimensional space such that all distances are preserved.
-Denoting this projection by $\mathbf{P} \in \mathbb{R}^{(3 \cdot W \cdot H) \times (N-1)}$, our method for steps (a)-(c) operates on $\mathbf{Z}(t) = \mathbf{P} \mathbf{X}(t)$.
+Denoting this projection by $\mb{P} \in \mathbb{R}^{(N-1) \times (3 \cdot W \cdot H)}$, our method for steps (a)-(c) operates on $\mb{Z}(t) = \mb{P} \mb{X}(t)$.
 
@@
 
-Given a $W \times H$ video $X(t) \in \mathbb{R}^{3WH}$ indexed by time, the sliding window video embedding \cite{cao1998dynamics,traliehigh,tralie2017quasi} is defined as
-
+The sliding window video embedding \cite{cao1998dynamics,traliehigh,tralie2017quasi} for $\mb{Z}$ can defined as
 \begin{equation}
-SW_{\text{dim}, \tau}[X(t)] = \left[ \begin{array}{c} X(t) \\ X(t + \tau) \\ \vdots \\ X(t + (\text{dim}-1)\tau)  \end{array} \right] \in \mathbb{R}^{3WH(\text{dim})}
+	SW_{D}[\mb{Z}(t)] = \left[ \begin{array}{c} \mb{Z}(t) \\ \mb{Z}(t + 1) \\ \vdots \\ \mb{Z}(t + (D-1))  \end{array} \right] \in \mathbb{R}^{(N-1)\cdot(D)},
 \end{equation}
-
-where $\tau$ is a step size and ``dim'' is the dimension of the embedding.
-In this work, we fix $\tau = 1$ for simplicity and drop $\tau$ in the subscript, and we also sample times $t$ only at integer frame indices.
-As shown by Takens \cite{takens1981detecting}, a sliding window of dimension $2m+1$ of even a single generic observation function (time series) of a dynamical system of intrinsic dimension $m$ is sufficient to reconstruct a topological embedding of the underlying trajectory in the original state space.
+where D is the dimension of the embedding.
+As shown by Takens~\cite{takens1981detecting}, a sliding window of dimension $2m+1$ of even a single generic observation function of a dynamical system of intrinsic dimension $m$ is sufficient to reconstruct a topological embedding of the underlying trajectory in the original state space.
 For periodic signals, this state space is a torus, and $d$ should be twice the number of harmonics present to injectively reconstruct loops on that torus \cite{perea2015sliding}.
 The same is true of videos in general \cite{tralie2017quasi}.
-Furthermore, the sliding window length $(\text{dim}-1) \tau$, or simply $\text{dim}-1$ in our case, maximizes the roundness of the embeddings when $\text{dim}-1 = k T$ for some integer $k$, where $T$ is the fundamental period.
+Furthermore, the sliding window length $(D-1)$ maximizes the roundness of the embeddings when $(D-1) = k T$ for some integer $k$, where $T$ is the fundamental period.
 Since we will use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that we tune our window size to be an integer multiple of the period.
-To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D ``surrogate signal,'' and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate dim.
+To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D surrogate signal, and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $D$.
 This is similar to the diffusion maps + autocorrelation approach in \cite{tralie2017quasi} for analyzing periodic videos.
 This estimation often returns integer multiples of the fundamental period, which is fine for our purposes.
+% MSB: could probably remove the diffusion maps + autocorrelation approach sentence if we need space
 
@@
 
-Since sliding window embeddings of periodic videos lie on a topological loop (a manifold which is an ``intrinsic circle''), this means that, at an appropriate scale, a nearest neighbors graph built on the sliding window point cloud will approximately be a circle graph.
+Since sliding window embeddings of periodic videos lie on a topological loop, this means that, at an appropriate scale, a nearest neighbors graph built on the sliding window point cloud will approximately be a graph representing a circle.
 To parameterize this graph, we turn to the graph Laplacian \cite{chung1997spectral}.
-For a graph $G$ with $N$ vertices and an $N \times N$ symmetric adjacency matrix $A$, the graph Laplacian is defined as
+To define the graph Laplacian, we first construct an adjacency matrix $\mb{A}$ in which the entry at $\mb{A}_{ij}$ represents the similarity between windows at times $i$ and $j$: $\mb{A}_{ij} = exp(-||SW_{D}[\mb{Z}(i)] - SW_{D}[\mb{Z}(j)]||_2/\epsilon)$.
+The graph Laplacian then follows as:
 \begin{equation}
-L = D-A
+	\mb{L} = \mb{D}-\mb{A}
 \end{equation}
-where $D_{ii} = \sum_{j = 1}^N A_{ij}, D_{i \neq j} = 0$ is the diagonal matrix.
+where $\mb{D}_{ii} = \sum_{j = 1}^N \mb{A}_{ij}, \mb{D}_{i \neq j} = 0$ is the diagonal matrix.
 Now let $d_{ij}: V \rightarrow \mathbb{R}^+$ be a nonnegative scalar function on the vertices of $G$.
@@
 Alternatively, the weighted adjacency matrix is defined as $A_{\epsilon}^w(d)_{ij} = \exp(-d_{ij}^2/\epsilon)$ \cite{belkin2003laplacian}, but everything else is the same.
-Now suppose we have performed a sliding window $SW_{\text{dim}}[X[n]]$ for a video $X$, where $X[n] = X[n+kT]$ for some integers $l, k$ so that there are $kT$ points in the sliding window (that is, $SW_{\text{dim}}[X[i]]$ repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows), and that $d_{ij} = ||SW_{\text{dim}}[X[i]] - SW_{\text{dim}}[X[j]]||_2$.
+Now suppose we have performed a sliding window $SW_{D}[X[n]]$ for a video $X$, where $X[n] = X[n+kT]$ for some integers $l, k$ so that there are $kT$ points in the sliding window (that is, $SW_{D}[X[i]]$ repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows), and that $d_{ij} = ||SW_{D}[X[i]] - SW_{D}[X[j]]||_2$.
 In this case, for any $\epsilon > 0$ and $|i - j| = kT$ for some integer $k$, $A^u_{\epsilon}(d)_{ij} = 1$.

### 2018-02-04 Paper/paper.tex
revised persistence section

@@
 Our discussion so far has assumed we can find the appropriate $\epsilon$ for the (un)weighted graph Laplacian, but this is data dependent.
-The authors of \cite{averbuch2015ringit} use $k$-nearest neighbors, which helps with scale, but which still requires an arbitrary parameter $k$.
-To adapt to the data, we 1D leverage persistent homology from topological data analysis \cite{edelsbrunner2010computational}.
-Roughly, this framework allows one to find the scale at which topological features exist in point cloud data.
-Specifically, we compute the ``1D Vietoris Rips Filtration'' on our sliding window data $X$, which tracks equivalence classes of loops, known as {\em homology classes} \cite{Hatcher}, as edges and triangles are gradually added between sliding window points.
-The algorithm returns a ``persistence diagram,'' which is a multiset of points on a 2D birth/death grid, with each point corresponding a loop class.
-The birth value $b_i$ indicates the scale $\epsilon$ at which the $i^{\text{th}}$ loop class forms, and the death value $d_i$ indicates the scale at which that class is ``filled in'' (expressible as a formal sum of triangle boundaries with coefficients in some field).
-$d_i - b_i$ is known as the {\em persistence} of the $i^{\text{th}}$ class.
+%The authors of \cite{averbuch2015ringit} use $k$-nearest neighbors, which helps with scale, but which still requires an arbitrary parameter $k$.
+To adapt to the data, we leverage 1D persistent homology from topological data analysis \cite{edelsbrunner2010computational}.
+This framework allows one to find the scale at which topological features exist in point cloud data.
+Specifically, we compute the 1D Vietoris Rips Filtration on our sliding window data $X$, which tracks equivalence classes of loops, known as {\em homology classes} \cite{Hatcher}, as edges and triangles are gradually added between sliding window points.
+The algorithm returns a so-called persistence diagram, which is a multiset of points on a 2D birth/death grid, with each point corresponding to a loop class.
+The birth value $b_i$ indicates the scale at which the $i^{\text{th}}$ loop class forms, and the death value $d_i$ indicates the scale at which that class no longer exists (expressible as a formal sum of triangle boundaries with coefficients in some field).
+The difference $d_i - b_i$ is known as the {\em persistence} of the $i^{\text{th}}$ class.
 For sliding window periodic time series, one point in the diagram should have a much larger persistence than the others (e.g.
-Figure~\ref{fig:ConceptFigure}) \cite{perea2015sliding,tralie2017quasi}.
+Figure~\ref{fig:ConceptFigure})~\cite{perea2015sliding,tralie2017quasi}, and this ideally reflects the single cycle of motion that we seek.
 We take our scale to be $\frac{1}{2}(b_i + d_i)$ for the largest $d_i - b_i$.
-Finally, note that we compute homology using $\mathbb{Z}_{49}$ coefficients to handle cases where a period has strong harmonics, since, choosing a field which is not relatively prime to a harmonic leads to lowered persistence \cite{perea2015sliding, traliemoebius}.
+% MSB: last sentence might change based on experiments
+
+Finally, homology computation requires the specification of coefficients that belong to a user-given field.
+Coefficients in $\mathbb{Z}_2$ are commonly chosen, however in our scenario this is problematic.
+For instance, the motion of someone performing a jumping jack contains a second harmonic, since an individual jumps twice per cycle, and using coefficients in $\mathbb{Z}_2$ would lead to so-called M{\"o}bius splitting~\cite{traliemoebius}.
+Thus, we use coefficients in the field $\mathbb{Z}_{49}$ in order to capture these types of complex motions.
+% MSB: mention use of software in experiments, not in techniques
+
+%Finally, note that we compute homology using $\mathbb{Z}_{49}$ coefficients to handle cases where a period has strong harmonics, since, choosing a field which is not relatively prime to a harmonic leads to lowered persistence \cite{perea2015sliding, traliemoebius}.
 For instance, a jumping jacks motion has a second harmonic, since an individual jumps twice per cycle, so the common persistence algorithm with $\mathbb{Z}_2$ coefficients would lead to ``M{\"o}bius splitting'' \cite{traliemoebius}.
+We use the GUDHI library\cite{maria2014gudhi} to compute persistent homology quickly with fields other than $\mathbb{Z}_2$.
 

### 2018-02-04 Paper/paper.tex
Doing heavy edits on the Laplacian section

@@
 One can also view the combination of TDA + Laplacian eigenmaps as a simpler alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} for the special case of periodic data.
-It is also the opposite of the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA.
-\matt{unclear what ''It'' refers to in this last sentence}
+Our approach is also the opposite of the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA.
 
@@
 
-The sliding window video embedding \cite{cao1998dynamics,traliehigh,tralie2017quasi} for $\mb{Z}$ can defined as
+The sliding window video embedding \cite{cao1998dynamics,traliehigh,tralie2017quasi} for $\mb{Z}$ is defined as
 \begin{equation}
@@
 
-Since sliding window embeddings of periodic videos lie on a topological loop, this means that, at an appropriate scale, a nearest neighbors graph built on the sliding window point cloud will approximately be a graph representing a circle.
-To parameterize this graph, we turn to the graph Laplacian \cite{chung1997spectral}.
-To define the graph Laplacian, we first construct an adjacency matrix $\mb{A}$ in which the entry at $\mb{A}_{ij}$ represents the similarity between windows at times $i$ and $j$: $\mb{A}_{ij} = exp(-||SW_{D}[\mb{Z}(i)] - SW_{D}[\mb{Z}(j)]||_2/\epsilon)$.
-The graph Laplacian then follows as:
+Since sliding window embeddings of periodic videos lie on a topological loop, this means that, at an appropriate scale, a graph built on the sliding window point cloud will be approximately circular.
+We can then compute the sliding window phase $\phi \in [0, 2\pi]$ from this graph using the {\em graph Laplacian} \cite{chung1997spectral}, which we now describe.
+We first construct an adjacency matrix $\mb{A}$ in which the entry at $\mb{A}_{ij}$ represents the similarity between windows at times $i$ and $j$.
+Given a scale $\sigma$, We define an unweighted version as $\mb{A}_{ij}$ is 1 if $||SW_{D}[\mb{Z}(i)] - SW_{D}[\mb{Z}(j)]||_2 \leq \sigma$ and 0 otherwise.
+We also define a weighted version in which $\mb{A}_{ij} = exp(-||SW_{D}[\mb{Z}(i)] - SW_{D}[\mb{Z}(j)]||_2/2\sigma^2)$.
+In both cases, we define the graph Laplacian as:
 \begin{equation}
@@
 \end{equation}
-where $\mb{D}_{ii} = \sum_{j = 1}^N \mb{A}_{ij}, \mb{D}_{i \neq j} = 0$ is the diagonal matrix.
-Now let $d_{ij}: V \rightarrow \mathbb{R}^+$ be a nonnegative scalar function on the vertices of $G$.
-Then the adjacency matrix correponding to the unweighted graph Laplacain, $A_{\epsilon}^u(d)$, is
+where $\mb{D}_{ii} = \sum_{j = 1}^N \mb{A}_{ij}, \mb{D}_{i \neq j} = 0$ is the degree matrix representing the sum of all outgoing weights on the diagonal.
 
-\begin{equation}
-A_{\epsilon}^u(d)_{ij} = \left\{ \begin{array}{cc} 1 & i \neq j, d_{ij} \leq \epsilon \\ 0 & \text{otherwise} \end{array} \right\}
-\end{equation}
-
-Alternatively, the weighted adjacency matrix is defined as $A_{\epsilon}^w(d)_{ij} = \exp(-d_{ij}^2/\epsilon)$ \cite{belkin2003laplacian}, but everything else is the same.
-Now suppose we have performed a sliding window $SW_{D}[X[n]]$ for a video $X$, where $X[n] = X[n+kT]$ for some integers $l, k$ so that there are $kT$ points in the sliding window (that is, $SW_{D}[X[i]]$ repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows), and that $d_{ij} = ||SW_{D}[X[i]] - SW_{D}[X[j]]||_2$.
-In this case, for any $\epsilon > 0$ and $|i - j| = kT$ for some integer $k$, $A^u_{\epsilon}(d)_{ij} = 1$.
-Let us further suppose it is possible to choose an $\epsilon$ so that each window is also connected to the window directly before and after it in time, as well as the windows directly before and after its repetitions, but none others; that is, the unweighted adjacency matrix is a symmetric, {\em circulant matrix}, with the first row $A_{\epsilon}^u(d)_{1j} = 1$ if $j = 1, N-1,$ or $lT, 1 \leq l \leq (k-1)$.
-Thus, the Laplacian is also circulant with first row
+We now examine the unweighted Laplacain of an ideal model to motivate our approach.
+Suppose we have performed a sliding window $SW_{D}[X[n]]$ for a video $X$ which repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows.
+Let us further suppose it is possible to choose an $\sigma$ so that the unweighted adjacency matrix contains a 1 entry for the edge between window directly before and after it in time, as well as the windows directly before and after its repetitions, but none others; that is, the Laplacian is a symmetric, {\em circulant} matrix defined as
 
@@
 \label{eq:modellaplacian}
-L_{1j} = \left\{ \begin{array}{cc} 3k-1 & j = 1 \\ -1 & j = lT, 1 \leq l \leq (k-1) \\ -1 & j = 1, N-1 \\ 0 & \text{otherwise} \end{array} \right\}
+L_{ij} = \left\{ \begin{array}{cc} 3k-1 & i = j \\ -1 & |i-j| = lT, l \in \mathbb{Z}^+ \\ -1 & |i-j| = lT \pm 1, l \in \mathbb{Z}^+ \\ 0 & \text{otherwise} \end{array} \right\}
 \end{equation}
@@
 \end{equation}
-When computing the smallest two nonzero eigenvalues numerically, therefore, one coresponds to a sinusoid with period $T$, and the other to an orthogonal sinusoid with period $T$.
-When plotted against each other, they form a circle, with an arbitrary phase offset.
+Therefore, the smallest two numerical nonzero eigenvalues each correspond to sinusoids with period $T$ which are mutually orthogonal.
+When plotted against each other, they form a circle with an arbitrary phase offset.
 Therefore, we compute the circular phase numerically $\phi = \tan^{-1}(\hat{v_1}[n] / \hat{v_2}[n])$, where $\hat{v_i}$ is the eigenvector corresponding to the $i^\text{th}$ smallest nonzero numerical eigenvalue.
 In practice, the graphs we get from sliding window may deviate from the ideal Laplacian model in Equation~\ref{eq:modellaplacian}, though they do so gracefully.
-Figure~\ref{fig:CirculantExample} shows an example of $\hat{v_1}[n]$ and $\hat{v_2}[n]$ for an ideal graph and for an imperfect graph corresponding to the sliding window embedding of a real video.
-
-Note that for both the unweighted and weighted cases in practice, we have observed that harmonics of the actual frequency of interest occasionally have smaller eigenvalues.
+Figure~\ref{fig:CirculantExample} shows an example of $\hat{v_1}[n]$ and $\hat{v_2}[n]$ for the unweighted case for an imperfect graph corresponding to the sliding window embedding of a real video.
+To further improve robustness, we default to the weighted Laplacian, since it has nice theoretical roperties for Euclidean point placement matching the adjacency matrix \cite{hall1970r}.
+In this case, harmonics of the actual frequency of interest occasionally have smaller eigenvalues when the corresponding harmonics are strongly present in the video.
 To mitigate this, we use the pair of eigenvectors with the smallest number of zero crossings within the eigenvectors corresponding to the 10 smallest nonzero eigenvalues.

### 2018-02-04 VideoReordering.py

@@ -197,7 +197,7 @@ def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = 20):
 
 def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
                 doSimple = False, doImageAnalogies = False, doPlot = True, \
-                Verbose = False, fileprefix = "", Kappa = -1, Alpha = 0.5, \
+                Verbose = False, fileprefix = "", Kappa = -1, Alpha = 1.0, \
                 percentile = True, p = 41, returnAnswer = True, doSlidingWindow = True, \
                 expandWindow = False, tdifflim = -1):
     """
@@ -274,6 +274,7 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
         I = Is[1]
         imax = np.argmax(I[:, 1] - I[:, 0])
         thresh = Alpha*I[imax, 0] + (1-Alpha)*I[imax, 1]
+        print("Thresh is at %.3g percentile"%(np.sum(D < thresh)/D.size))
         tic = time.time()
         if Weighted:
             if doPlot:

### 2018-02-04 Paper/paper.tex
working copy of abstract

--- 2018-02-04 Paper/paper.tex
@@
 
+In this paper we consider the problem of taking a video that is comprised of multiple periods of repetitive motion, and reordering the frames of the video into a single period, producing a detailed, single cycle, video of motion.
+This problem is challenging to solve, as such videos often contain noise, drift due to camera motion, and irrelevant background motion, and these factors can confound the relevant periodic motion we seek in the video.
+To address these issues in a simple and efficient manner, we introduce an Eulerian approach for synthesizing a single cycle of motion.
+Our approach is geometric: we treat each video frame as a point in a high-dimensional Euclidean space, and analyze the
+{\em sliding window embedding} formed by this sequence of points.
 The majority of our pipeline is fully automated, using tools from topological data analysis in concert with nonlinear dimenison reduction to autotune the spatial and temporal scales of the period.

### 2018-02-04 Paper/paper.tex
pass on abstract

@@
 
-In this paper we consider the problem of taking a video that is comprised of multiple periods of repetitive motion, and reordering the frames of the video into a single period, producing a detailed, single cycle, video of motion.
+In this paper we consider the problem of taking a video that is comprised of multiple periods of repetitive motion, and reordering the frames of the video into a single period, producing a detailed, single cycle video of motion.
 This problem is challenging to solve, as such videos often contain noise, drift due to camera motion, and irrelevant background motion, and these factors can confound the relevant periodic motion we seek in the video.
 To address these issues in a simple and efficient manner, we introduce an Eulerian approach for synthesizing a single cycle of motion.
-Our approach is geometric: we treat each video frame as a point in a high-dimensional Euclidean space, and analyze the
-{\em sliding window embedding} formed by this sequence of points.
-The majority of our pipeline is fully automated, using tools from topological data analysis in concert with nonlinear dimenison reduction to autotune the spatial and temporal scales of the period.
+Our approach is geometric: we treat each video frame as a point in a high-dimensional Euclidean space, and analyze the {\em sliding window embedding} formed by this sequence of points.
+% MSB: would be nice to have a concise description of what this is, but that is tricky to write up.
+Alternatively, we could also state why this embedding is useful for 1-cycle estimation
+Our technique for ordering the embedding combines tools from topological data analysis to determine the appropriate spatial scale, with tools from spectral geometric analysis to estimate the phase of each window.
+% MSB: not mentioning the median voting - should probably mention that in as few words as possible
+We show quantitative results that highlight the robustness of our technique to noise and camera shake, and show qualitative results of single-cycle motion synthesis across a wide variety of scenarios.
 

### 2018-02-04 Paper/paper.tex
revised 2.2

@@
 Since sliding window embeddings of periodic videos lie on a topological loop, this means that, at an appropriate scale, a graph built on the sliding window point cloud will be approximately circular.
-We can then compute the sliding window phase $\phi \in [0, 2\pi]$ from this graph using the {\em graph Laplacian} \cite{chung1997spectral}, which we now describe.
+This permits us to compute the {\em phase} $\phi \in [0, 2\pi]$ of each sliding window from this graph, where we use tools from spectral graph theory~\cite{chung1997spectral}, in particular the {\em graph Laplacian}, for phase estimation.
 We first construct an adjacency matrix $\mb{A}$ in which the entry at $\mb{A}_{ij}$ represents the similarity between windows at times $i$ and $j$.
-Given a scale $\sigma$, We define an unweighted version as $\mb{A}_{ij}$ is 1 if $||SW_{D}[\mb{Z}(i)] - SW_{D}[\mb{Z}(j)]||_2 \leq \sigma$ and 0 otherwise.
+Given a scale $\sigma$, we define the unweighted adjacency as $\mb{A}_{ij} = 1$ if $||SW_{D}[\mb{Z}(i)] - SW_{D}[\mb{Z}(j)]||_2 \leq \sigma$ and 0 otherwise.
 We also define a weighted version in which $\mb{A}_{ij} = exp(-||SW_{D}[\mb{Z}(i)] - SW_{D}[\mb{Z}(j)]||_2/2\sigma^2)$.
@@
 
-We now examine the unweighted Laplacain of an ideal model to motivate our approach.
-Suppose we have performed a sliding window $SW_{D}[X[n]]$ for a video $X$ which repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows.
-Let us further suppose it is possible to choose an $\sigma$ so that the unweighted adjacency matrix contains a 1 entry for the edge between window directly before and after it in time, as well as the windows directly before and after its repetitions, but none others; that is, the Laplacian is a symmetric, {\em circulant} matrix defined as
+We now examine the unweighted Laplacian of an ideal model to motivate our approach.
+Suppose we have extracted a sliding window embedding $SW_{D}$ for a video $\mb{Z}$ which repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows.
+Let us further suppose it is possible to choose an $\sigma$ so that the unweighted adjacency matrix contains an entry of 1 for edges corresponding to windows that are adjacent in time, as well as for windows directly before and after its repetitions, but no others; that is, the Laplacian is a symmetric, {\em circulant} matrix defined as % MSB: "its repetitions": not sure what "its" refers to
 
@@
 
-Circulant matrices are diagonalized by the Discrete Fourier Transform \cite{godsil2013algebraic}, and their nonzero eigenvalues come in pairs with multiplicity two, with corresopnding eigenvectors $v_1[n] = 1$, $v_{2m}[n] = \cos(2 \pi mn / N)$, $v_{2m+1}[n] = \sin(2 \pi m n / N)$, $m \geq 1$.
+Circulant matrices are diagonalized by the Discrete Fourier Transform \cite{godsil2013algebraic}, and their nonzero eigenvalues come in pairs with multiplicity two, with corresponding eigenvectors $v_1[n] = 1$, $v_{2m}[n] = \cos(2 \pi mn / N)$, $v_{2m+1}[n] = \sin(2 \pi m n / N)$, $m \geq 1$.
 In the case of Equation~\ref{eq:modellaplacian}, it can be shown using the DFT that the eigenvalues are $\lambda_1 = 0$ and
@@
 Therefore, we compute the circular phase numerically $\phi = \tan^{-1}(\hat{v_1}[n] / \hat{v_2}[n])$, where $\hat{v_i}$ is the eigenvector corresponding to the $i^\text{th}$ smallest nonzero numerical eigenvalue.
-In practice, the graphs we get from sliding window may deviate from the ideal Laplacian model in Equation~\ref{eq:modellaplacian}, though they do so gracefully.
+
+In practice, graphs of the sliding window embedding may deviate from the ideal Laplacian model in Equation~\ref{eq:modellaplacian}, though they do so gracefully.
 Figure~\ref{fig:CirculantExample} shows an example of $\hat{v_1}[n]$ and $\hat{v_2}[n]$ for the unweighted case for an imperfect graph corresponding to the sliding window embedding of a real video.
-To further improve robustness, we default to the weighted Laplacian, since it has nice theoretical roperties for Euclidean point placement matching the adjacency matrix \cite{hall1970r}.
+To further improve robustness, we default to the weighted Laplacian, due to its theoretical properties for Euclidean point placement matching the adjacency matrix \cite{hall1970r}.
 In this case, harmonics of the actual frequency of interest occasionally have smaller eigenvalues when the corresponding harmonics are strongly present in the video.
 To mitigate this, we use the pair of eigenvectors with the smallest number of zero crossings within the eigenvectors corresponding to the 10 smallest nonzero eigenvalues.
+% MSB: "real video": what video?
+% MSB: what is "point placement"?
 

### 2018-02-04 Paper/paper.tex
Lots of little edits, and finished the median reordering section

@@
 To address these issues in a simple and efficient manner, we introduce an Eulerian approach for synthesizing a single cycle of motion.
-Our approach is geometric: we treat each video frame as a point in a high-dimensional Euclidean space, and analyze the {\em sliding window embedding} formed by this sequence of points.
+Our approach is geometric: we treat each video frame as a point in a high-dimensional Euclidean space, and analyze the {\em sliding window embedding} formed by this sequence of points, which yields points sampled along a topological loop regardless of the type of periodic motion.
 % MSB: would be nice to have a concise description of what this is, but that is tricky to write up.
@@
 % MSB: not mentioning the median voting - should probably mention that in as few words as possible
-We show quantitative results that highlight the robustness of our technique to noise and camera shake, and show qualitative results of single-cycle motion synthesis across a wide variety of scenarios.
+We show quantitative results that highlight the robustness of our technique to camera shake, and show qualitative results of single-cycle motion synthesis across a wide variety of scenarios.
 
@@
 To address the problems with an Eulerian representation, we devise a geometric/topological Eulerian framework by constructing {\em sliding window embeddings} of videos (Section~\ref{sec:slidingwindow}).
-Sliding window embeddings, or delay reconstructions, have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, EEG analysis \cite{stam2005nonlinear, plesnik2014detection}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
+Sliding window embeddings, or delay reconstructions, have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
 Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data, regardless of the type of motion present \cite{traliehigh, tralie2017quasi}.
@@
 % MSB: opportunity to slim paper by cutting examples 
-Many prior works use a combination of sliding window embeddings and topological data analysis, such as detecting the Lorenz attractor \cite{de2012topological}, quantifying circadian rhythms in gene expression data \cite{perea2015sliding}, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, and quantifying vocal fold anomalies in video \cite{tralie2017quasi}, though we believe we are the first to use a sliding window + TDA framework to {\em synthesize} a new result.
+Many prior works use a combination of sliding window embeddings and topological data analysis, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, and quantifying vocal fold anomalies in video \cite{tralie2017quasi}, though we believe we are the first to use a sliding window + TDA framework to {\em synthesize} a new result.
 Related works have used the graph Laplacian to rearrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and to reorder the frames of microscope images from a developing embryo around a loop using vector diffusion maps~\cite{dsilva2015diffusionvecordering}.
@@
 Denoting this projection by $\mb{P} \in \mathbb{R}^{(N-1) \times (3 \cdot W \cdot H)}$, our method for steps (a)-(c) operates on $\mb{Z}(t) = \mb{P} \mb{X}(t)$.
+Furthermore, to mitigate the impact of drift from period to period, we use the third layer of a Gaussian pyramid on each frame in place of the raw frames before applying $P$.
 
@@
 \begin{equation}
-	SW_{D}[\mb{Z}(t)] = \left[ \begin{array}{c} \mb{Z}(t) \\ \mb{Z}(t + 1) \\ \vdots \\ \mb{Z}(t + (D-1))  \end{array} \right] \in \mathbb{R}^{(N-1)\cdot(D)},
+	SW_{d}[\mb{Z}(t)] = \left[ \begin{array}{c} \mb{Z}(t) \\ \mb{Z}(t + 1) \\ \vdots \\ \mb{Z}(t + (d-1))  \end{array} \right] \in \mathbb{R}^{(N-1)\cdot(d)},
 \end{equation}
-where D is the dimension of the embedding.
+where $d$ is the dimension of the embedding.
 As shown by Takens~\cite{takens1981detecting}, a sliding window of dimension $2m+1$ of even a single generic observation function of a dynamical system of intrinsic dimension $m$ is sufficient to reconstruct a topological embedding of the underlying trajectory in the original state space.
@@
 The same is true of videos in general \cite{tralie2017quasi}.
-Furthermore, the sliding window length $(D-1)$ maximizes the roundness of the embeddings when $(D-1) = k T$ for some integer $k$, where $T$ is the fundamental period.
+Furthermore, the sliding window length $(d-1)$ maximizes the roundness of the embeddings when $(d-1) = k T$ for some integer $k$, where $T$ is the fundamental period.
 Since we will use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that we tune our window size to be an integer multiple of the period.
 To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D surrogate signal, and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $D$.
-This is similar to the diffusion maps + autocorrelation approach in \cite{tralie2017quasi} for analyzing periodic videos.
 This estimation often returns integer multiples of the fundamental period, which is fine for our purposes.
-% MSB: could probably remove the diffusion maps + autocorrelation approach sentence if we need space
 
@@
 We first construct an adjacency matrix $\mb{A}$ in which the entry at $\mb{A}_{ij}$ represents the similarity between windows at times $i$ and $j$.
-Given a scale $\sigma$, we define the unweighted adjacency as $\mb{A}_{ij} = 1$ if $||SW_{D}[\mb{Z}(i)] - SW_{D}[\mb{Z}(j)]||_2 \leq \sigma$ and 0 otherwise.
-We also define a weighted version in which $\mb{A}_{ij} = exp(-||SW_{D}[\mb{Z}(i)] - SW_{D}[\mb{Z}(j)]||_2/2\sigma^2)$.
+Given a scale $\sigma$, we define the unweighted adjacency as $\mb{A}_{ij} = 1$ if $||SW_{d}[\mb{Z}(i)] - SW_{d}[\mb{Z}(j)]||_2 \leq \sigma$ and 0 otherwise.
+We also define a weighted version in which $\mb{A}_{ij} = exp(-||SW_{d}[\mb{Z}(i)] - SW_{d}[\mb{Z}(j)]||_2/2\sigma^2)$.
 In both cases, we define the graph Laplacian as:
@@
 We now examine the unweighted Laplacian of an ideal model to motivate our approach.
-Suppose we have extracted a sliding window embedding $SW_{D}$ for a video $\mb{Z}$ which repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows.
-Let us further suppose it is possible to choose an $\sigma$ so that the unweighted adjacency matrix contains an entry of 1 for edges corresponding to windows that are adjacent in time, as well as for windows directly before and after its repetitions, but no others; that is, the Laplacian is a symmetric, {\em circulant} matrix defined as % MSB: "its repetitions": not sure what "its" refers to
+Suppose we have extracted a sliding window embedding $SW_{d}$ for a video $\mb{Z}$ which repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows.
+Let us further suppose it is possible to choose an $\sigma$ so that the unweighted adjacency matrix contains an entry of 1 for edges corresponding to windows that are adjacent in time, as well as for the corresponding windows at, before, and after repetitions of the window at intervals of $T$; that is, the Laplacian is a symmetric, {\em circulant} matrix defined as
 
@@
 In practice, graphs of the sliding window embedding may deviate from the ideal Laplacian model in Equation~\ref{eq:modellaplacian}, though they do so gracefully.
-Figure~\ref{fig:CirculantExample} shows an example of $\hat{v_1}[n]$ and $\hat{v_2}[n]$ for the unweighted case for an imperfect graph corresponding to the sliding window embedding of a real video.
-To further improve robustness, we default to the weighted Laplacian, due to its theoretical properties for Euclidean point placement matching the adjacency matrix \cite{hall1970r}.
+Figure~\ref{fig:CirculantExample} shows an example of $\hat{v_1}[n]$ and $\hat{v_2}[n]$ for the unweighted case for an imperfect graph corresponding to the sliding window embedding of a video of two men doing jumping jacks.
+To further improve robustness, we default to the weighted Laplacian so that small changes in the threshold lead to small changes in $\mb{A}$.
 In this case, harmonics of the actual frequency of interest occasionally have smaller eigenvalues when the corresponding harmonics are strongly present in the video.
 To mitigate this, we use the pair of eigenvectors with the smallest number of zero crossings within the eigenvectors corresponding to the 10 smallest nonzero eigenvalues.
-% MSB: "real video": what video?
-% MSB: what is "point placement"?
 
 \subsection{Persistent Homology}
-Our discussion so far has assumed we can find the appropriate $\epsilon$ for the (un)weighted graph Laplacian, but this is data dependent.
+Our discussion so far has assumed we can find the appropriate $\sigma$ for the (un)weighted graph Laplacian, but this is data dependent.
 %The authors of \cite{averbuch2015ringit} use $k$-nearest neighbors, which helps with scale, but which still requires an arbitrary parameter $k$.
@@
 Figure~\ref{fig:ConceptFigure})~\cite{perea2015sliding,tralie2017quasi}, and this ideally reflects the single cycle of motion that we seek.
-We take our scale to be $\frac{1}{2}(b_i + d_i)$ for the largest $d_i - b_i$.
-% MSB: last sentence might change based on experiments
+We take our scale to be $\alpha b_i + (1-\alpha)d_i$ for the largest $d_i - b_i$, where $\alpha \in [0, 1]$ is a parameter which will be explored experimentally in Section~\ref{sec:experiments}.
 
@@
 Thus, we use coefficients in the field $\mathbb{Z}_{49}$ in order to capture these types of complex motions.
-% MSB: mention use of software in experiments, not in techniques
-
-%Finally, note that we compute homology using $\mathbb{Z}_{49}$ coefficients to handle cases where a period has strong harmonics, since, choosing a field which is not relatively prime to a harmonic leads to lowered persistence \cite{perea2015sliding, traliemoebius}.
-For instance, a jumping jacks motion has a second harmonic, since an individual jumps twice per cycle, so the common persistence algorithm with $\mathbb{Z}_2$ coefficients would lead to ``M{\"o}bius splitting'' \cite{traliemoebius}.
-We use the GUDHI library\cite{maria2014gudhi} to compute persistent homology quickly with fields other than $\mathbb{Z}_2$.
 
@@
 
-Advantage of Eulerian is that everything is linear (can use SVD to compress)
-
-Interpolated windows can be projected back to pixel space one by one to save memory
-
-Mention the ``F'' parameter in the pipeline
+Given the phase estimates $\phi_i$, we can now synthesize the final slow motion template by lining up the $N$ sliding windows $SW_{d}[\mb{X}(i)]$ by $\phi$.
+For a template with $M$ frames, we choose a set of $M$ equally spaced angles $\theta_1, \theta_2, ..., \theta_M$ around the circle at which to sample the template.
+Let $\Phi_i$ be the unwrapped phase of $\phi_i$.
+Based on this, we esimate the number of periods $X(t)$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.
+Assuming $k$ is correct, each sliding window $SW_{d}[\mb{X}(i)]$ consists of stacked frames that span the interval $[\phi_i, \phi_i + 2\pi k d/N (\text{mod} 2 \pi)]$.
+A given $\theta_j$ will potentially be contained in the intervals for many different windows, though it is unlikely to coincide exactly with any of the frames exactly, so we use linear interpolation to fill in a frame corresponding to $\theta_j$ in each window overlapping it.
+We then take a pixel-wise median of all such interpolated frames, and we let that be the final frame at position $j$ in the template.
+In practice, for videos which go through many periods, the gap $2 \pi k/N$ between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.
+We thus add an additional user-defined parameter ``F'' which only includes linearly interpolated frames in the median if the frame to interpolate is at most $F$ frames away from an existing frame in the window.
 
 \section{Experiments}
+\label{sec:experiments}
+
+We now show some experimental results from our pipeline.  We use the GUDHI library\cite{maria2014gudhi} to compute persistent homology quickly with fields other than $\mathbb{Z}_2$.
 
@@
 
-We now experimentally quantify the accuracy of our circular coordinate inference, since we cannot hope to get a good slow motion template unless our circular coordinates are accurate.
+We first experimentally quantify the accuracy of our circular coordinate inference, since we cannot hope to get a good slow motion template unless our circular coordinates are accurate.
 We generate 3 different 600 frame synthetic periodic videos for which we know the ground truth circular coordinates, using software from \cite{jacobson2012fast}.
@@
 \includegraphics[width=\columnwidth]{XTSliceJumpingJacks.pdf}
-\caption{An XT slice of a line of pixels (magenta line, upper left) over time for an input video of two men doing jumping jacks and for reordered videos with and without median consensus.}
+\caption{An XT slice of a line of pixels (magenta line, upper left) over time for an input video of men doing jumping jacks and for reordered videos with and without median consensus.}
 \label{fig:XTSliceJumpingJacks}

### 2018-02-04 Laplacian.py

@@ -73,6 +73,7 @@ def getLapCircularCoordinatesSigma(D, sigma, NEigs = 10, doPlot = False):
     :return {'w':eigenvalues, 'v':eigenvectors, 'theta':Circular coordinates,\
             'thetau':Unwrapped circular coordinates, 'A':Adjacency matrix}
     """
+    #A = 0.5*(1+np.tanh((sigma-D)/sigma**2))
     A = np.exp(-D*D/(2*sigma**2))
     #A = np.exp(-D*D/sigma)
     np.fill_diagonal(A, 0)

### 2018-02-04 VideoReordering.py

@@ -197,7 +197,7 @@ def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = 20):
 
 def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
                 doSimple = False, doImageAnalogies = False, doPlot = True, \
-                Verbose = False, fileprefix = "", Kappa = -1, Alpha = 1.0, \
+                Verbose = False, fileprefix = "", Kappa = -1, Alpha = 0.5, \
                 percentile = True, p = 41, returnAnswer = True, doSlidingWindow = True, \
                 expandWindow = False, tdifflim = -1):
     """
@@ -274,7 +274,7 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
         I = Is[1]
         imax = np.argmax(I[:, 1] - I[:, 0])
         thresh = Alpha*I[imax, 0] + (1-Alpha)*I[imax, 1]
-        print("Thresh is at %.3g percentile"%(np.sum(D < thresh)/D.size))
+        print("Thresh = %g, %.3g percentile"%(thresh, np.sum(D < thresh)/D.size))
         tic = time.time()
         if Weighted:
             if doPlot:
@@ -303,7 +303,7 @@ def reorderVideo(XOrig, X_feat, IDims, derivWin = 10, Weighted = False, \
             plt.plot([lims[0], thresh], [thresh, thresh], 'k', linestyle='--')
             plt.plot([thresh, thresh], [thresh, lims[0]], 'k', linestyle='--')
             plt.plot([I[imax, 0]]*2, I[imax, :], 'r')
-            plt.title("H1, Thresh = %g"%thresh)
+            plt.title("H1, Thresh = %g, Percentile = %.3g"%(thresh, np.sum(D < thresh)/D.size))
         plt.subplot(234)
         plt.imshow(v, cmap = 'afmhot', interpolation = 'nearest', aspect = 'auto')
         plt.subplot(235)

### 2018-02-04 Paper/paper.tex
Trying to make my derivation a little clearer for median voting

@@
 Based on this, we esimate the number of periods $X(t)$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.
-Assuming $k$ is correct, each sliding window $SW_{d}[\mb{X}(i)]$ consists of stacked frames that span the interval $[\phi_i, \phi_i + 2\pi k d/N (\text{mod} 2 \pi)]$.
+Assuming $k$ is correct and that $\phi_i$ has a constant slope over $i$, there is a phase gap of $2 \pi k/N$ between adjacent stacked frames in each sliding window.
+Thus, $SW_{d}[\mb{X}(i)]$ spans the interval $[\phi_i, \phi_i + 2\pi k d/N (\text{mod} 2 \pi)]$.
 A given $\theta_j$ will potentially be contained in the intervals for many different windows, though it is unlikely to coincide exactly with any of the frames exactly, so we use linear interpolation to fill in a frame corresponding to $\theta_j$ in each window overlapping it.
 We then take a pixel-wise median of all such interpolated frames, and we let that be the final frame at position $j$ in the template.
-In practice, for videos which go through many periods, the gap $2 \pi k/N$ between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.
+In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.
 We thus add an additional user-defined parameter ``F'' which only includes linearly interpolated frames in the median if the frame to interpolate is at most $F$ frames away from an existing frame in the window.

### 2018-02-04 Paper/paper.tex
exactly..exactly

@@
 Thus, $SW_{d}[\mb{X}(i)]$ spans the interval $[\phi_i, \phi_i + 2\pi k d/N (\text{mod} 2 \pi)]$.
-A given $\theta_j$ will potentially be contained in the intervals for many different windows, though it is unlikely to coincide exactly with any of the frames exactly, so we use linear interpolation to fill in a frame corresponding to $\theta_j$ in each window overlapping it.
+A given $\theta_j$ will potentially be contained in the intervals for many different windows, though it is unlikely to coincide exactly with any of the frames in each window, so we use linear interpolation to fill in a frame corresponding to $\theta_j$ in each window overlapping it.
 We then take a pixel-wise median of all such interpolated frames, and we let that be the final frame at position $j$ in the template.

### 2018-02-04 Paper/paper.tex
some editing

@@
 For instance, a simple Fourier bandpass filtering and amplifying pixels can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.
-Additionally, time domain Eulerian approaches have been used to synthesize infinitely playing ``video textures'' using random walks \cite{schodl2000video}, or to synthesize perfectly looping video templates after grouping pixels with similar periods together and devising a common period for all groups \cite{Liao2013VideoLoops,Liao2015VideoLoops}.
+Additionally, time-domain Eulerian approaches have been used to synthesize infinitely playing ``video textures''~\cite{schodl2000video}, as well as looping video templates for more general scenarios~\cite{Liao2013VideoLoops,Liao2015VideoLoops}.
 There are some pitfalls with Eulerian techniques, however.
@@
 
-% MSB: opportunity to slim paper by cutting examples 
-To address the problems with an Eulerian representation, we devise a geometric/topological Eulerian framework by constructing {\em sliding window embeddings} of videos (Section~\ref{sec:slidingwindow}).
-Sliding window embeddings, or delay reconstructions, have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, gene expression data \cite{perea2015sw1pers}, audio and music analysis \cite{herzel1994analysis,serra2009cross,bello2011measuring,traliemoebius}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
-Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data, regardless of the type of motion present \cite{traliehigh, tralie2017quasi}.
-Furthermore, the sliding window embedding of an Eulerian video provides a form of regularization that mitigates the effects of drift and leads to a cleaner loop~\cite{tralie2017quasi}.
-Our geometric framework also allows us to use topological data analysis \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} and fundamental frequency estimation \cite{Mcleod05asmarter} to autotune the spatial and temporal scales of the periodic motion, respectively, so that no user intervention is required.
-We use Laplacian Eigenmaps~\cite{belkin2003laplacian} computed on the sliding window embedding to obtain a circular phase $\phi \in [0, 2\pi]$ for each window.
-The video is re-ordered by using $\phi$ and exploiting the sliding window structure, where different windows vote on the final pixels in each frame of the template, helping to further mitigate drift (Section~\ref{sec:cyclereordering}).
-As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled periodic time series (i.e.
-single pixel grayscale video).
-There are only 12 samples per period in the original signal, so the details of each period are coarse and noisy.
-However, once they are re-sorted, we get a fine-detailed representation of one period.
-The extension of this technique to videos will be described in detail in Section~\ref{sec:methods}.
-
-% MSB: opportunity to slim paper by cutting examples 
-Many prior works use a combination of sliding window embeddings and topological data analysis, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, detecting wheezing in audio \cite{emrani2014real}, quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}, and quantifying vocal fold anomalies in video \cite{tralie2017quasi}, though we believe we are the first to use a sliding window + TDA framework to {\em synthesize} a new result.
-Related works have used the graph Laplacian to rearrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and to reorder the frames of microscope images from a developing embryo around a loop using vector diffusion maps~\cite{dsilva2015diffusionvecordering}.
-However, our use of the graph Laplacian to instead {\em parameterize} time series is unique.
-One can also view the combination of TDA + Laplacian eigenmaps as a simpler alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} for the special case of periodic data.
-Our approach is also the opposite of the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA.
-
-\section{Slow Motion Templates}
-\label{sec:methods}
-
-\begin{figure*}[h!]
+\begin{figure*}[t!]
 \centering
 \includegraphics[width=\textwidth]{BlockDiagram.pdf}
-\caption{An block diagram of our technique, illustrated by a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).
+	\caption{Overview of our technique for a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).
+We first estimate the signal's period and extract a sliding window embedding (a), followed by estimating the spatial scale (b) via TDA, which is used to compute the phase $\phi$ via the graph Laplacian (c).
+The single-period motion template is then synthesized by having reordered windows vote on individual pixels (d).
+On the right we show the result superimposed with ground truth (in orange).}
+%\caption{An block diagram of our technique, illustrated by a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).
 We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.
@@
 
-Figure~\ref{fig:ConceptFigure} depicts an overview of our method.
+% MSB: opportunity to slim paper by cutting examples 
+To address the problems with an Eulerian representation, we devise a geometric/topological Eulerian framework by constructing {\em sliding window embeddings} of videos (Section~\ref{sec:slidingwindow}).
+Sliding window embeddings, or delay reconstructions, have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
+Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data, regardless of the type of motion present \cite{traliehigh, tralie2017quasi}.
+Furthermore, the sliding window embedding of an Eulerian video provides a form of regularization that mitigates the effects of drift and leads to a cleaner loop~\cite{tralie2017quasi}.
+Our geometric framework also allows us to use topological data analysis (TDA) \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} and fundamental frequency estimation \cite{Mcleod05asmarter} to autotune the spatial and temporal scales of the periodic motion, respectively, so that no user intervention is required.
+We use Laplacian Eigenmaps~\cite{belkin2003laplacian} computed on the sliding window embedding to obtain a circular phase $\phi \in [0, 2\pi]$ for each window.
+We then reorder the embedding using $\phi$, and reorder the video by having windows that overlap in time vote on final pixels in each frame of the template, helping to further mitigate drift (Section~\ref{sec:cyclereordering}).
+As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled 1D periodic time series.
+There are only 12 samples per period in the original signal, so the details of each period are coarse and noisy.
+However, once resorted, we get a fine-detailed representation of one period.
+
+% MSB: opportunity to slim paper by cutting examples 
+Many prior works use a combination of sliding window embeddings and topological data analysis, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, and quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}.
+However, our approach in using a sliding window jointly with TDA to {\em synthesize} a new result is novel.
+Related works have used the graph Laplacian to rearrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and to reorder the frames of microscope images from a developing embryo around a loop using vector diffusion maps~\cite{dsilva2015diffusionvecordering}.
+However, our use of the graph Laplacian to instead {\em parameterize} time series is unique.
+One can also view the combination of TDA and Laplacian eigenmaps as a simpler alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} for the special case of periodic data.
+%Our approach is also the opposite of the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA. - MSB: this is related work, not opposite work :)
+
+\section{Slow Motion Templates}
+\label{sec:methods}
+
+%Figure~\ref{fig:ConceptFigure} depicts an overview of our method.
 First we estimate the period of the cycle, and use this to compute the sliding window embedding (a).
@@
 
-\textbf{Preprocessing.} The input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$.
+Figure~\ref{fig:ConceptFigure} shows the different parts of our method for a 1D periodic signal for illustration purposes.
+However, our technique applies to multivariate time series data as well, such as video.
+More specifically, the input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$.
 We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mb{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$.
@@
 Denoting this projection by $\mb{P} \in \mathbb{R}^{(N-1) \times (3 \cdot W \cdot H)}$, our method for steps (a)-(c) operates on $\mb{Z}(t) = \mb{P} \mb{X}(t)$.
-Furthermore, to mitigate the impact of drift from period to period, we use the third layer of a Gaussian pyramid on each frame in place of the raw frames before applying $P$.
+Furthermore, to mitigate the impact of drift from period to period, we use the third layer of a Gaussian pyramid on each frame in place of the raw frames before applying $\mb{P}$.
 

### 2018-02-05 Paper/paper.tex
Adding new shake results (may need some resolution/font tweaking
Labeling sections of pipeline as anaysis (a) and synthesis (b)

@@
 Figure~\ref{fig:ConceptFigure} shows the different parts of our method for a 1D periodic signal for illustration purposes.
-However, our technique applies to multivariate time series data as well, such as video.
-More specifically, the input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$.
+In general, the actual input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$.
 We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mb{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$.
-The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}(a-c), however, do not rely on the {\em extrinsic} geometry of the set of points $\mb{X}(t)$, only its set of {\em pairwise distances}.
+The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}, which we split into two parts: an analysis part (a) and a synthesis part (b).
+For the analysis part, we do not rely on the {\em extrinsic} geometry of the set of points $\mb{X}(t)$, only its set of {\em pairwise distances}.
 Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that pairwise distances are preserved.
 Since $N \ll (3 \cdot W \cdot H)$, the frames can be projected into a $N-1$-dimensional space such that all distances are preserved.
-Denoting this projection by $\mb{P} \in \mathbb{R}^{(N-1) \times (3 \cdot W \cdot H)}$, our method for steps (a)-(c) operates on $\mb{Z}(t) = \mb{P} \mb{X}(t)$.
-Furthermore, to mitigate the impact of drift from period to period, we use the third layer of a Gaussian pyramid on each frame in place of the raw frames before applying $\mb{P}$.
+Denoting this projection by $\mb{P} \in \mathbb{R}^{(N-1) \times (3 \cdot W \cdot H)}$, our method for the steps in (a) operates on $\mb{Z}(t) = \mb{P} \mb{X}(t)$.
+We also use the third layer of a Gaussian pyramid on each frame in place of the raw frames before applying $\mb{P}$ to mitigate drift.
 
@@
 Since we will use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that we tune our window size to be an integer multiple of the period.
-To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D surrogate signal, and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $D$.
+To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D surrogate signal, and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $d$.
 This estimation often returns integer multiples of the fundamental period, which is fine for our purposes.
@@
 \centering
-\includegraphics[width=\columnwidth]{RobustnessTests.pdf}
+\includegraphics[width=\columnwidth]{RobustnessTestsShake.pdf}
 \caption{Robustness tests.}
-\label{fig:RobustnessTests}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{RobustnessTestsNoSW.pdf}
-\caption{Robustness tests without sliding window.}
-\label{fig:RobustnessTestsNoSW}
+\label{fig:RobustnessTestsShake}
 \end{figure}
@@
 We generate 3 different 600 frame synthetic periodic videos for which we know the ground truth circular coordinates, using software from \cite{jacobson2012fast}.
-We vary the number of cycles that the videos undergo between 3, 5, 10, 15, 20, 25, 30, 40, and 50, and we also vary the ``shake'' of the video (width of a motion blur kernel) from 0, $20 \times 20$, $40 \times 40$, and $80 \times 80$, to assess the effect of drift.
+We vary the number of cycles that the videos undergo between 3, 5, 10, 15, 20, 25, 30, 40, and 50, and we also vary the ``shake'' of the video (width of a motion blur kernel) from $0 \times0 $ to $50 \times 50$ pixels, in increments of 10, to assess the effect of drift.
 We also compare different fractions $\kappa$ of mutual nearest neighbors to tune the threshold at which the unweighted Laplacian is built to TDA for aututuning the scale.
-Figure~\ref{fig:RobustnessTests} shows the average angular error in degrees for our entire pipeline, and Figure~\ref{fig:RobustnessTests}.
+Figure~\ref{fig:RobustnessTestsShake} shows the average angular error in degrees for our entire pipeline under different amounts of shake.
 The errors are overall quite low for moderate shake with a sliding window, though they increase as more shake is introduced.
@@
 \includegraphics[width=\columnwidth]{XTSliceFan.pdf}
-\caption{An XT slice of a line of pixels (magenta line, upper left) over time for an input video of a fan with only 6 frames per period and the corresponding median consensus reordered video.}
+\caption{An XT slice of a line of pixels (magenta line, upper left) over time for an input video of a fan with only 6 frames per period and the corresponding reorderd template.}
 \label{fig:XTSliceFan}

### 2018-02-05 Paper/paper.tex
Clarifying further

@@
 We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mb{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$.
-The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}, which we split into two parts: an analysis part (a) and a synthesis part (b).
+The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}, which we split into two parts: an analysis part (a), which culminates in phase estimates $\phi$, and a synthesis part (b), in which the template is created based on information in (a).
 For the analysis part, we do not rely on the {\em extrinsic} geometry of the set of points $\mb{X}(t)$, only its set of {\em pairwise distances}.

### 2018-02-05 Paper/paper.tex
small edits to 2.4

--- 2018-02-04 Paper/paper.tex
@@
 A given $\theta_j$ will potentially be contained in the intervals for many different windows, though it is unlikely to coincide exactly with any of the frames in each window, so we use linear interpolation to fill in a frame corresponding to $\theta_j$ in each window overlapping it.
-We then take a pixel-wise median of all such interpolated frames, and we let that be the final frame at position $j$ in the template.
-In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.
+The frame at angle $\phi_j$ is taken as the median of all interpolated frames.
+In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ghosting artifacts in linear interpolation \cite{meyer2015phase}.
 We thus add an additional user-defined parameter ``F'' which only includes linearly interpolated frames in the median if the frame to interpolate is at most $F$ frames away from an existing frame in the window.
+% MSB: I do not understand this last sentence..
 
@@
 We also compare different fractions $\kappa$ of mutual nearest neighbors to tune the threshold at which the unweighted Laplacian is built to TDA for aututuning the scale.
-Figure~\ref{fig:RobustnessTests} shows the average angular error in degrees for our entire pipeline, and Figure~\ref{fig:RobustnessTests}.
+Figure~\ref{fig:RobustnessTestsShake} shows the average angular error in degrees for our entire pipeline under different amounts of shake.
 The errors are overall quite low for moderate shake with a sliding window, though they increase as more shake is introduced.

### 2018-02-05 Paper/paper.tex
another small change
pass on paper

@@
 Eulerian approaches for video synthesis are attractive due to their simplicity and ease of implementation.
-For instance, a simple Fourier bandpass filtering and amplifying pixels can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.
+For instance, a Fourier bandpass filtering can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.
 Additionally, time-domain Eulerian approaches have been used to synthesize infinitely playing ``video textures''~\cite{schodl2000video}, as well as looping video templates for more general scenarios~\cite{Liao2013VideoLoops,Liao2015VideoLoops}.
@@
 % MSB: opportunity to slim paper by cutting examples 
-To address the problems with an Eulerian representation, we devise a geometric/topological Eulerian framework by constructing {\em sliding window embeddings} of videos (Section~\ref{sec:slidingwindow}).
+To address the problems with an Eulerian representation, we devise a geometric and topological Eulerian framework by constructing {\em sliding window embeddings} of videos.
 Sliding window embeddings, or delay reconstructions, have found a diverse array of applications in activity recognition \cite{frank2010activity,venkataraman2016shape}, video analysis \cite{tralie2017quasi}, and motion capture analysis \cite{venkataraman2016shape}.
 Sliding window embeddings of periodic time series, in particular, form samples of a topological loop \cite{perea2015sliding}, as do generalized multivariate sliding windows on periodic video data, regardless of the type of motion present \cite{traliehigh, tralie2017quasi}.
-Furthermore, the sliding window embedding of an Eulerian video provides a form of regularization that mitigates the effects of drift and leads to a cleaner loop~\cite{tralie2017quasi}.
+Furthermore, the sliding window embedding of an Eulerian video provides a form of regularization that mitigates the effects of drift~\cite{tralie2017quasi}.
 Our geometric framework also allows us to use topological data analysis (TDA) \cite{edelsbrunner2000topological,edelsbrunner2008persistent,edelsbrunner2010computational,carlsson2009topology,ghrist2014elementary} and fundamental frequency estimation \cite{Mcleod05asmarter} to autotune the spatial and temporal scales of the periodic motion, respectively, so that no user intervention is required.
 We use Laplacian Eigenmaps~\cite{belkin2003laplacian} computed on the sliding window embedding to obtain a circular phase $\phi \in [0, 2\pi]$ for each window.
-We then reorder the embedding using $\phi$, and reorder the video by having windows that overlap in time vote on final pixels in each frame of the template, helping to further mitigate drift (Section~\ref{sec:cyclereordering}).
-As an illustration, Figure~\ref{fig:ConceptFigure} shows an example of our technique on a sampled 1D periodic time series.
+We then reorder the embedding using $\phi$, and reorder the video by having windows that overlap in time vote on final pixels in each frame of the template, further mitigating drift.
+Figure~\ref{fig:ConceptFigure} highlights the steps of our technique for a sampled 1D periodic time series.
 There are only 12 samples per period in the original signal, so the details of each period are coarse and noisy.
@@
 % MSB: opportunity to slim paper by cutting examples 
-Many prior works use a combination of sliding window embeddings and topological data analysis, detecting chatter in mechanical systems \cite{khasawneh2016chatter}, and quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}.
+Many prior works use a combination of sliding window embeddings and topological data analysis, for instance detecting chatter in mechanical systems \cite{khasawneh2016chatter} and quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}.
 However, our approach in using a sliding window jointly with TDA to {\em synthesize} a new result is novel.
-Related works have used the graph Laplacian to rearrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and to reorder the frames of microscope images from a developing embryo around a loop using vector diffusion maps~\cite{dsilva2015diffusionvecordering}.
+Related works have used the graph Laplacian to rearrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and to reorder the frames of microscope images from a developing embryo~\cite{dsilva2015diffusionvecordering}.
 However, our use of the graph Laplacian to instead {\em parameterize} time series is unique.
@@
 Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that pairwise distances are preserved.
-Since $N \ll (3 \cdot W \cdot H)$, the frames can be projected into a $N-1$-dimensional space such that all distances are preserved.
+Since $N \ll (3 \cdot W \cdot H)$, a distance-preserving projection into an $N-1$-dimensional space is always possible.
 Denoting this projection by $\mb{P} \in \mathbb{R}^{(N-1) \times (3 \cdot W \cdot H)}$, our method for the steps in (a) operates on $\mb{Z}(t) = \mb{P} \mb{X}(t)$.
@@
 Furthermore, the sliding window length $(d-1)$ maximizes the roundness of the embeddings when $(d-1) = k T$ for some integer $k$, where $T$ is the fundamental period.
-Since we will use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that we tune our window size to be an integer multiple of the period.
-To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on the original frames of the video to generate a 1D surrogate signal, and we perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $d$.
+Since we will use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that the window size is an integer multiple of the period.
+To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on $\mb{Z}$ to generate a 1D surrogate signal, and perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $d$.
 This estimation often returns integer multiples of the fundamental period, which is fine for our purposes.
+% MSB: "roundness" is not being very precise
 
@@
 We now examine the unweighted Laplacian of an ideal model to motivate our approach.
-Suppose we have extracted a sliding window embedding $SW_{d}$ for a video $\mb{Z}$ which repeats itself exactly every $T$ frames $k$ times total, for a total of $N = kT$ windows.
+Suppose we have extracted a sliding window embedding $SW_{d}$ for a video $\mb{Z}$ which repeats itself exactly every $T$ frames for $k$ times, for a total of $N = kT$ windows.
 Let us further suppose it is possible to choose an $\sigma$ so that the unweighted adjacency matrix contains an entry of 1 for edges corresponding to windows that are adjacent in time, as well as for the corresponding windows at, before, and after repetitions of the window at intervals of $T$; that is, the Laplacian is a symmetric, {\em circulant} matrix defined as
@@
 \end{equation}
-Therefore, the smallest two numerical nonzero eigenvalues each correspond to sinusoids with period $T$ which are mutually orthogonal.
+Therefore, the smallest two numerically nonzero eigenvalues each correspond to sinusoids with period $T$ which are mutually orthogonal.
 When plotted against each other, they form a circle with an arbitrary phase offset.
-Therefore, we compute the circular phase numerically $\phi = \tan^{-1}(\hat{v_1}[n] / \hat{v_2}[n])$, where $\hat{v_i}$ is the eigenvector corresponding to the $i^\text{th}$ smallest nonzero numerical eigenvalue.
+Therefore, we compute the circular phase numerically $\phi = \tan^{-1}(\hat{v_1}[n] / \hat{v_2}[n])$, where $\hat{v_i}$ is the eigenvector corresponding to the $i^\text{th}$ smallest numerically nonzero eigenvalue.
 
@@
 The algorithm returns a so-called persistence diagram, which is a multiset of points on a 2D birth/death grid, with each point corresponding to a loop class.
-The birth value $b_i$ indicates the scale at which the $i^{\text{th}}$ loop class forms, and the death value $d_i$ indicates the scale at which that class no longer exists (expressible as a formal sum of triangle boundaries with coefficients in some field).
+The birth value $b_i$ indicates the scale at which the $i^{\text{th}}$ loop class forms, and the death value $d_i$ indicates the scale at which that class no longer exists.
 The difference $d_i - b_i$ is known as the {\em persistence} of the $i^{\text{th}}$ class.
@@
 Let $\Phi_i$ be the unwrapped phase of $\phi_i$.
-Based on this, we esimate the number of periods $X(t)$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.
+Based on this, we esimate the number of periods $\mb{X}$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.
 Assuming $k$ is correct and that $\phi_i$ has a constant slope over $i$, there is a phase gap of $2 \pi k/N$ between adjacent stacked frames in each sliding window.
@@
 We thus add an additional user-defined parameter ``F'' which only includes linearly interpolated frames in the median if the frame to interpolate is at most $F$ frames away from an existing frame in the window.
-% MSB: I do not understand this last sentence..
+% MSB: I do not understand this last sentence, but could probably be tighter..
 
@@
 
-We now show some experimental results from our pipeline.  We use the GUDHI library\cite{maria2014gudhi} to compute persistent homology quickly with fields other than $\mathbb{Z}_2$.
+We now show some experimental results from our pipeline.
+%We use the GUDHI library\cite{maria2014gudhi} to compute persistent homology quickly with fields other than $\mathbb{Z}_2$.
 

### 2018-02-06 Paper/paper.tex
Labeling figure to match captions

@@
 We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mb{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$.
-The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}, which we split into two parts: an analysis part (a), which culminates in phase estimates $\phi$, and a synthesis part (b), in which the template is created based on information in (a).
-For the analysis part, we do not rely on the {\em extrinsic} geometry of the set of points $\mb{X}(t)$, only its set of {\em pairwise distances}.
+The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}.
+For steps (a-c), we do not rely on the {\em extrinsic} geometry of the set of points $\mb{X}(t)$, only its set of {\em pairwise distances}.
 Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that pairwise distances are preserved.

### 2018-02-10 Laplacian.py
Adding tests with drifting objects, and making Laplacian more robust by requiring zero crossings ratio between adjacent eigenvectors to be within a tolerance bound

@@ -50,14 +50,22 @@ def getSlopes(thetas, sWin = 10):
     slopes[-(sWin+1):] = slopes[-(sWin+1)]
     return slopes
 
-def getSlowestEigenvectorIdx(v):
+def getSlowestEigenvectorIdx(v, tol = 0.95):
+    """
+    Find the adjacent pair of eigenvectors with similar eigenvalues that have
+    the smallest number of zero crossings
+    :param v: NEigs x k array of eigenvectors arrange along columns
+    :param tol: Reject pairs with zero crossings ratio less than tol
+    """
     #Compute zero crossings and put the low frequencies eigenvectors first
     s = v > 0
     zcs = np.sum(s[1::, :] - s[0:-1, :], 0)
-    #Find the adjacent pair with the smallest number of zero crossings
     smallest = np.inf
     i1 = 1
     for i in range(1, len(zcs)-1):
+        ratio = min(float(zcs[i])/zcs[i+1], float(zcs[i+1])/zcs[i])
+        if ratio < tol:
+            continue
         bothSum = zcs[i] + zcs[i+1]
         if bothSum < smallest:
             smallest = bothSum

### 2018-02-10 RobustnessTests.py

@@ -100,7 +100,7 @@ def getCycles(NCycles, filename, NFinal = -1):
     theta = np.mod(theta, 2*np.pi)
     return {'I':I[idx, :], 'IDims':IDims, 'idx':idx, 'theta':theta}
 
-def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, saveVideos = False):
+def doTest(filename, NCycles, noise = 0, shake = 0, bgfac = 0, fileprefix = "", Verbose = False, saveVideos = False):
     doPlot = False
     if len(fileprefix) > 1:
         doPlot = True
@@ -110,6 +110,8 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
     I += noise*np.random.randn(I.shape[0], I.shape[1])
     if shake > 0:
         simulateCameraShake(I, IDims, shake)
+    if bgfac > 0:
+        simulateBGBlob(I, IDims, bgfac)
     if saveVideos:
         saveVideo(I, IDims, "%s_simulated.avi"%fileprefix)
     ret = {}
@@ -149,7 +151,7 @@ def doTest(filename, NCycles, noise, shake, fileprefix = "", Verbose = False, sa
                         plt.scatter(rank1, rank2)
                         plt.title("$\\tau = %.3g$"%kendTau)
                         plt.savefig("%s_CircCoordsCorr.svg"%(fileprefix+thisprefix), bbox_inches = 'tight')
-                    if saveVideos:
+                    if saveVideos and res['X']:
                         saveVideo(res['X'], IDims, (fileprefix+thisprefix)+".avi")
     return ret
 
@@ -158,24 +160,27 @@ def writeBatchHeader(fout, filename):
     fout.write("""<html>
     <body><h1>{}</h1>
     <table border = "1">
-    <tr><td>NCycles</td><td>Noise</td><td>Shake</td><td>TrialNumber</td><td>SlidingWindow</td>
-        <td>PyramidLevel</td><td>Alpha</td><td>Weighted</td><td>Percentile</td><td>CircError</td><td>KendallTau</td></tr>   
+    <tr><td>NCycles</td><td>Noise</td><td>Shake</td><td>BgFac</td><td>TrialNumber</td><td>SlidingWindow</td>
+        <td>PyramidLevel</td><td>Alpha</td><td>Weighted</td><td>CircError</td><td>KendallTau</td></tr>   
     """.format(filename))
 
 def writeBatchHeaderCSV(fout, filename):
[…]

### 2018-02-10 VideoTools.py

@@ -485,21 +485,48 @@ def simulateCameraShake(I, IDims, shakeMag):
             IBlur[:, :, k] = scipy.signal.fftconvolve(X[:, :, k], mask, 'same')
         I[i, :] = IBlur.flatten()
 
-if __name__ == '__main__2':
-    (I, IDims) = loadVideo("VocalCordsVideos/LTR_ED_MucusBiphonCrop.avi")
-    IBlur = simulateCameraShake(I, IDims, 40)
-    saveVideo(IBlur, IDims, "MucusBlur.avi")
-    IGradient = getGradientVideo(I, IDims, sigma=1)
-    IGradient = IGradient/np.max(IGradient)
-    saveVideo(IGradient, IDims, "out.avi")
+def simulateBGBlob(I, IDims, fac):
+    """
+    Simulate a blob taking a random walk in the video as a source
+    of unrelated background motion.
+    Do the blur in place to save memory
+    :param I: NFrames x (NPixelsxNChannels) dimensional video
+    :param IDims: Tuple of dimensions of each frame
+    :param fac: A fraction in [0, 1] of the area that the blob occupes
+    """
+    NFrames = I.shape[0]
+    L = int(np.sqrt(IDims[0]*IDims[1]*fac)) #Width of blob
+    H = int(min(IDims[0]-L, IDims[1]-L))
+    X = makeRandomWalkCurve(H, int(NFrames/4.0), 2)
+    X = smoothCurve(X, 20)
+    skip = int(np.floor(X.shape[0]/NFrames))
+    X = X[0::skip, :]
+    X = X[0:NFrames, :]
+    X = X - np.min(X, 0)[None, :]
+    denom = np.max(X, 0)
+    denom[denom == 0] = 1
+    X = X/denom[None, :]
+    X[:, 0] *= (IDims[0]-L)
+    X[:, 1] *= (IDims[1]-L)
+    X = np.round(X)
+    X[X < 0] = 0
+    X[X[:, 0] > IDims[0]-L-1, 0] = IDims[0]-L-1
+    X[X[:, 1] > IDims[1]-L-1, 1] = IDims[1]-L-1
+    X = np.array(X, dtype=np.int64)
+    colordrift = np.cumsum(np.random.randn(NFrames, 3), 0)
+    colordrift = colordrift - np.min(colordrift, 0)
+    denom = np.max(colordrift, 0)
[…]

### 2018-02-11 Paper/paper.tex
More paper edits

@@
 \newcommand{\mb}{\mathbf}
+\setlength{\parskip}{0pt}
 
@@
 In this paper we consider the problem of taking a video that is comprised of multiple periods of repetitive motion, and reordering the frames of the video into a single period, producing a detailed, single cycle video of motion.
-This problem is challenging to solve, as such videos often contain noise, drift due to camera motion, and irrelevant background motion, and these factors can confound the relevant periodic motion we seek in the video.
-To address these issues in a simple and efficient manner, we introduce an Eulerian approach for synthesizing a single cycle of motion.
+This problem is challenging to solve, as such videos often contain noise, drift due to camera motion and from cycle to cycle, and irrelevant background motion/occlusions, and these factors can confound the relevant periodic motion we seek in the video.
+To address these issues in a simple and efficient manner, we introduce an Eulerian approach for synthesizing a single cycle of motion, which requires no tracking.
 Our approach is geometric: we treat each video frame as a point in a high-dimensional Euclidean space, and analyze the {\em sliding window embedding} formed by this sequence of points, which yields points sampled along a topological loop regardless of the type of periodic motion.
-% MSB: would be nice to have a concise description of what this is, but that is tricky to write up.
-Alternatively, we could also state why this embedding is useful for 1-cycle estimation
 Our technique for ordering the embedding combines tools from topological data analysis to determine the appropriate spatial scale, with tools from spectral geometric analysis to estimate the phase of each window.
-% MSB: not mentioning the median voting - should probably mention that in as few words as possible
-We show quantitative results that highlight the robustness of our technique to camera shake, and show qualitative results of single-cycle motion synthesis across a wide variety of scenarios.
+We also exploit the sliding window structure by using overlapping windows to vote on a final template after phase reordering.
+We show quantitative results that highlight the robustness of our technique to camera shake, noise, and occlusions, and we show qualitative results of single-cycle motion synthesis across a wide variety of scenarios.
 
@@
 They are known to fail for large motions, and also require the user to manually specify frequencies of interest \cite{wu2012eulerian, wadhwa2013phase}.
-Furthermore, period-to-period drift that is due to a moving camera or small variation in motion can be problematic, as well as unrelated motion in the background \cite{stauffer1999adaptive}.
+Furthermore, period-to-period drift that is due to a moving camera or small variation in motion can be problematic, as well as unrelated motion in the background or occlusions \cite{stauffer1999adaptive}.
 
-\begin{figure*}[t!]
+\begin{figure*}
 \centering
@@
 However, our use of the graph Laplacian to instead {\em parameterize} time series is unique.
-One can also view the combination of TDA and Laplacian eigenmaps as a simpler alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} for the special case of periodic data.
-%Our approach is also the opposite of the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA. - MSB: this is related work, not opposite work :)
+One can also view the combination of TDA and Laplacian eigenmaps as a simpler alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} for the special case of periodic data, and it is related to the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA.
 
@@
 The same is true of videos in general \cite{tralie2017quasi}.
-Furthermore, the sliding window length $(d-1)$ maximizes the roundness of the embeddings when $(d-1) = k T$ for some integer $k$, where $T$ is the fundamental period.
-Since we will use topological data analysis (TDA) to find the scale of the loop, and since TDA measures roundness, it is important that the window size is an integer multiple of the period.
-To do this, we perform 1D ISOMAP \cite{tenenbaum2000global} on $\mb{Z}$ to generate a 1D surrogate signal, and perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter} on this signal to estimate the period and, hence, the appropriate $d$.
-This estimation often returns integer multiples of the fundamental period, which is fine for our purposes.
-% MSB: "roundness" is not being very precise
+Furthermore, the sliding window length $(d-1)$ maximizes the topological persistence (Section~\ref{sec:tda}) of the embeddings when $(d-1) = k T$ for some integer $k$, where $T$ is the fundamental period \cite{perea2015sliding, tralie2017quasi}.
+To estimate $T$, and hence $d$, we perform 1D ISOMAP \cite{tenenbaum2000global} on $\mb{Z}$ to generate a 1D surrogate signal, and perform an autocorrelation-based fundamental frequency estimation \cite{Mcleod05asmarter}.
 
@@
 Since sliding window embeddings of periodic videos lie on a topological loop, this means that, at an appropriate scale, a graph built on the sliding window point cloud will be approximately circular.
-This permits us to compute the {\em phase} $\phi \in [0, 2\pi]$ of each sliding window from this graph, where we use tools from spectral graph theory~\cite{chung1997spectral}, in particular the {\em graph Laplacian}, for phase estimation.
+Based on this, we use tools from spectral graph theory~\cite{chung1997spectral}, in particular the {\em graph Laplacian}, to estimate the {\em phase} $\phi \in [0, 2 \pi]$ of each sliding window.
 We first construct an adjacency matrix $\mb{A}$ in which the entry at $\mb{A}_{ij}$ represents the similarity between windows at times $i$ and $j$.
@@
 In this case, harmonics of the actual frequency of interest occasionally have smaller eigenvalues when the corresponding harmonics are strongly present in the video.
-To mitigate this, we use the pair of eigenvectors with the smallest number of zero crossings within the eigenvectors corresponding to the 10 smallest nonzero eigenvalues.
+To mitigate this, we search through the 10 eigenvectors corresponding to the smallest 10 eigenvalues, sorted by eigenvalue, and we use the pair of adjacent eigenvectors with the smallest number of zero crossings whose zero crossing counts are within a factor of 5$\%$ of each other.
 
 \subsection{Persistent Homology}
+\label{sec:tda}
 Our discussion so far has assumed we can find the appropriate $\sigma$ for the (un)weighted graph Laplacian, but this is data dependent.
@@
 
-Finally, homology computation requires the specification of coefficients that belong to a user-given field.
+Finally, homology computation requires the specification of coefficients that belong to a user-given field \cite{Hatcher,maria2014gudhi}.
 Coefficients in $\mathbb{Z}_2$ are commonly chosen, however in our scenario this is problematic.
-For instance, the motion of someone performing a jumping jack contains a second harmonic, since an individual jumps twice per cycle, and using coefficients in $\mathbb{Z}_2$ would lead to so-called M{\"o}bius splitting~\cite{traliemoebius}.
+For instance, the motion of a jumping jack contains a second harmonic, since an individual jumps twice per cycle, and using coefficients in $\mathbb{Z}_2$ would lead to so-called M{\"o}bius splitting~\cite{traliemoebius}.
 Thus, we use coefficients in the field $\mathbb{Z}_{49}$ in order to capture these types of complex motions.
@@
 The frame at angle $\phi_j$ is taken as the median of all interpolated frames.
-In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ghosting artifacts in linear interpolation \cite{meyer2015phase}.
-We thus add an additional user-defined parameter ``F'' which only includes linearly interpolated frames in the median if the frame to interpolate is at most $F$ frames away from an existing frame in the window.
-% MSB: I do not understand this last sentence, but could probably be tighter..
+In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.
+We thus add an optional user-defined parameter ``F,'' and we only include interpolated frames in the median which are at most $F$ frames away from an actual frame.
 
@@
 
-We now show some experimental results from our pipeline.
 %We use the GUDHI library\cite{maria2014gudhi} to compute persistent homology quickly with fields other than $\mathbb{Z}_2$.
@@
 \centering
-\includegraphics[width=\columnwidth]{RobustnessTestsShake.pdf}
+\includegraphics[width=\columnwidth]{RobustnessTests.pdf}
 \caption{Robustness tests.}
-\label{fig:RobustnessTestsShake}
+\label{fig:RobustnessTests}
 \end{figure}
 
-We first experimentally quantify the accuracy of our circular coordinate inference, since we cannot hope to get a good slow motion template unless our circular coordinates are accurate.
+We first experimentally quantify the accuracy of our circular coordinate inference, since we cannot hope to get a good slow motion template without accurate circular coordinates.
 We generate 3 different 600 frame synthetic periodic videos for which we know the ground truth circular coordinates, using software from \cite{jacobson2012fast}.
-We vary the number of cycles that the videos undergo between 3, 5, 10, 15, 20, 25, 30, 40, and 50, and we also vary the ``shake'' of the video (width of a motion blur kernel) from $0 \times0 $ to $50 \times 50$ pixels, in increments of 10, to assess the effect of drift.
-We also compare different fractions $\kappa$ of mutual nearest neighbors to tune the threshold at which the unweighted Laplacian is built to TDA for aututuning the scale.
-Figure~\ref{fig:RobustnessTestsShake} shows the average angular error in degrees for our entire pipeline under different amounts of shake.
-The errors are overall quite low for moderate shake with a sliding window, though they increase as more shake is introduced.
-Without a sliding window, the only video that performs reasonably well is the ``crowd'' videom, though the errors increase with shake much more rapidly than with the sliding window, supporting the ``time regularization'' properties of the sliding window.
+Each video is roughly $300 \times 300$ pixels.
+We vary the number of cycles that the videos undergo between 3, 5, 10, 15, 20, 25, 30, 40, and 50.
+We then vary the ``shake'' of the video (width of a motion blur kernel) from $10 \times 10 $ to $50 \times 50$ pixels, in increments of 10, to assess the effect of drift.
+We also add Gaussian noise width standard deviations of $0.5, 1, 2$ (where original RGB ranges are in $[0, 1]$), and we add a color drifting square of length between 10 and 50 pixels taking a random walk to assess the effect of occlusions / background motion.
+We also compare the $\alpha$ which weights the birth time and death time from TDA.
+Figure~\ref{fig:RobustnessTests} shows the average angular error in degrees for our entire pipeline under these variations.
+Overall, performance is stable to the choice of $\alpha$, and the errors are quite low for severe noise and for moderate shake and occlusions with a sliding window, though they increase as more shake or larger occlusions are introduced.
+Without a sliding window, the only video that performs reasonably well is the ``crowd'' video, since this is the only video which is loop-like without a sliding window embedding, though the errors increase much more rapidly than with the sliding window, validating the ``time regularization'' aspect of sliding windows.
 
@@
 Figure~\ref{fig:XTSliceFan} shows an extreme example in which an original spinning fan video has only 6 frames per period at framerate.
-In addition to these examples, in our supplementary material, we show results from jumping jacks 2 men, two exercise videos from \cite{levy2015live}, and beating heart videos from \cite{traliehigh}, \cite{wu2012eulerian}, and \cite{wadhwa2013phase}.
+In addition to these examples, in our supplementary material, we show results from jumping jacks 2 men, an exercise video \cite{levy2015live}, and beating heart videos \cite{traliehigh, wadhwa2013phase}.
 

### 2018-02-11 ImageAnalogies.py

@@ -200,13 +200,19 @@ def flattenPatchArray(X):
     X = np.reshape(X, [X.shape[0]*X.shape[1]*X.shape[2], X.shape[3]])
     return X
 
-def doImageAnalogiesAcausal(As, Aps, B, KSpatial = 5, \
+def doImageAnalogiesAcausal(As, Aps, Bs, KSpatial = 5, \
         patchfn = getColorPatchesImageSet, outputIters = False):
-    BPatches = patchfn([B], KSpatial, getPatches)
-    ShapeBefore = BPatches.shape[1::]
-    BPatches = flattenPatchArray(BPatches)
-    BpPatches = np.array([])
-    minDists = np.array([])
+    BPatches = []
+    minDists = []
+    BpPatches = []
+    ShapesBefore = []
+    for B in Bs:
+        BPatches.append(patchfn([B], KSpatial, getPatches))
+        ShapesBefore.append(BPatches[-1].shape[1::])
+        BPatches[-1] = flattenPatchArray(BPatches[-1])
+        minDists.append(np.array([]))
+        BpPatches.append(np.array([]))
+    
     for i in range(len(As)):
         #Loop through for memory reasons
         APatches = patchfn([As[i]], KSpatial, getPatches)
@@ -215,29 +221,32 @@ def doImageAnalogiesAcausal(As, Aps, B, KSpatial = 5, \
         ApPatches = flattenPatchArray(ApPatches)
         #Build ANN function off of A patches
         annList = pyflann.FLANN()
-        print("Building ANN list...")
-        tic = time.time()
         annList.build_index(APatches)
-        print("Elapsed Time: %g"%(time.time() - tic))
-        print("Finding nearest neighbors...")
+        
         tic = time.time()
-        (idx, dists) = annList.nn_index(BPatches)
-        print("Elapsed Time: %g"%(time.time() - tic))
-        if i == 0:
-            BpPatches = ApPatches[idx, :]
-            minDists = dists
-        else:
-            bidx = np.arange(BpPatches.shape[0])
-            bidx = bidx[dists < minDists]
-            BpPatches[bidx] = ApPatches[idx[bidx], :]
-            minDists[bidx] = dists[bidx]
-            print("%g%s Better Patches"%(100*float(len(bidx))/BpPatches.shape[0], '%'))
-        if outputIters:
-            Bp = recombineColorPatches(np.reshape(BpPatches, ShapeBefore),
[…]

### 2018-02-11 RobustnessTests.py

@@ -100,7 +100,7 @@ def getCycles(NCycles, filename, NFinal = -1):
     theta = np.mod(theta, 2*np.pi)
     return {'I':I[idx, :], 'IDims':IDims, 'idx':idx, 'theta':theta}
 
-def doTest(filename, NCycles, noise = 0, shake = 0, bgfac = 0, fileprefix = "", Verbose = False, saveVideos = False):
+def doTest(filename, NCycles, noise = 0, shake = 0, bgwidth = 0, fileprefix = "", Verbose = False, saveVideos = False):
     doPlot = False
     if len(fileprefix) > 1:
         doPlot = True
@@ -110,8 +110,8 @@ def doTest(filename, NCycles, noise = 0, shake = 0, bgfac = 0, fileprefix = "", 
     I += noise*np.random.randn(I.shape[0], I.shape[1])
     if shake > 0:
         simulateCameraShake(I, IDims, shake)
-    if bgfac > 0:
-        simulateBGBlob(I, IDims, bgfac)
+    if bgwidth > 0:
+        simulateBGBlob(I, IDims, bgwidth)
     if saveVideos:
         saveVideo(I, IDims, "%s_simulated.avi"%fileprefix)
     ret = {}
@@ -160,27 +160,29 @@ def writeBatchHeader(fout, filename):
     fout.write("""<html>
     <body><h1>{}</h1>
     <table border = "1">
-    <tr><td>NCycles</td><td>Noise</td><td>Shake</td><td>BgFac</td><td>TrialNumber</td><td>SlidingWindow</td>
+    <tr><td>NCycles</td><td>Noise</td><td>Shake</td><td>BgWidth</td><td>TrialNumber</td><td>SlidingWindow</td>
         <td>PyramidLevel</td><td>Alpha</td><td>Weighted</td><td>CircError</td><td>KendallTau</td></tr>   
     """.format(filename))
 
 def writeBatchHeaderCSV(fout, filename):
-    fout.write("NCycles,Noise,Shake,BgFac,TrialNumber,SlidingWindow,PyramidLevel,Alpha,Weighted,CircError,KendallTau")
+    fout.write("NCycles,Noise,Shake,BgWidth,TrialNumber,SlidingWindow,PyramidLevel,Alpha,Weighted,CircError,KendallTau")
 
 def doBatchTests(filename, fout, batchidx = -1):
     idx = 0
     noise = 0
[…]

### 2018-02-11 VideoReordering.py

@@ -171,28 +171,40 @@ def upsampleVideo(I, IDims, IDimsNew):
         INew.append(FNew.flatten())
     return np.array(INew)
 
-def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = 20):
+def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = -1, NPerBatch = 40):
     """
     Use image analogies to sharpen the consensus video
     """
-    #Randomly sample 10 analogy image pairs from original video
     As = []
     Aps = []
-    np.random.seed(NExamples)
-    for idx in np.random.permutation(XOrig.shape[0])[0:NExamples]:
+    idxs = np.arange(XOrig.shape[0])
+    if NExamples > 0:
+        #Randomly sample 10 analogy image pairs from original video
+        np.random.seed(NExamples)
+        idxs = np.random.permutation(XOrig.shape[0])[0:NExamples]
+    for idx in idxs:
         A = np.reshape(XDown[idx, :], IDimsDown)
         A = resizeImage(A, IDims)
         Ap = np.reshape(XOrig[idx, :], IDims)
         As.append(A)
         Aps.append(Ap)
     XFinal = []
-    for i in range(XDownNew.shape[0]):
-        print("Doing image analogies sharpening frame %i of %i"%(i, XDownNew.shape[0]))
-        B = np.reshape(XDownNew[i, :], IDimsDown)
-        B = resizeImage(B, IDims)
-        Bp = doImageAnalogiesAcausal(As, Aps, B, KSpatial = 5, outputIters = True)
-        writeImage(Bp, "%s%i.png"%(TEMP_STR, i+1))
-        XFinal.append(Bp.flatten())
+    NIters = int(np.ceil(XDownNew.shape[0]/float(NPerBatch)))
+    for it in range(NIters):
+        print("Doing image analogies sharpening batch %i of %i"%(it+1, NIters))
+        Bs = []
+        ivals = []
+        for i in range(it*NPerBatch, (it+1)*NPerBatch):
+            if i > XDownNew.shape[0]-1:
+                break
+            B = np.reshape(XDownNew[i, :], IDimsDown)
+            B = resizeImage(B, IDims)
+            Bs.append(B)
+            ivals.append(i)
+        Bps = doImageAnalogiesAcausal(As, Aps, Bs, KSpatial = 5, outputIters = False)
[…]

### 2018-02-11 VideoTools.py

@@ -485,17 +485,16 @@ def simulateCameraShake(I, IDims, shakeMag):
             IBlur[:, :, k] = scipy.signal.fftconvolve(X[:, :, k], mask, 'same')
         I[i, :] = IBlur.flatten()
 
-def simulateBGBlob(I, IDims, fac):
+def simulateBGBlob(I, IDims, L):
     """
     Simulate a blob taking a random walk in the video as a source
     of unrelated background motion.
     Do the blur in place to save memory
     :param I: NFrames x (NPixelsxNChannels) dimensional video
     :param IDims: Tuple of dimensions of each frame
-    :param fac: A fraction in [0, 1] of the area that the blob occupes
+    :param L: Blob width in pixels
     """
     NFrames = I.shape[0]
-    L = int(np.sqrt(IDims[0]*IDims[1]*fac)) #Width of blob
     H = int(min(IDims[0]-L, IDims[1]-L))
     X = makeRandomWalkCurve(H, int(NFrames/4.0), 2)
     X = smoothCurve(X, 20)
@@ -528,5 +527,5 @@ def simulateBGBlob(I, IDims, fac):
 if __name__ == '__main__':
     #Test adding background blob
     (I, I_Feat, IDims) = loadImageIOVideo("jumpingjacks2menlowres.ogg")
-    simulateBGBlob(I, IDims, 0.05)
+    simulateBGBlob(I, IDims, 40)
     saveVideo(I, IDims, "bg.avi")

### 2018-02-11 Paper/paper.tex
conclusions, slimming text

@@
 \setlength{\parskip}{0pt}
+
+%\usepackage{titlesec}
+%\titlespacing\section{0pt}{4pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
 
@@
 Our approach is geometric: we treat each video frame as a point in a high-dimensional Euclidean space, and analyze the {\em sliding window embedding} formed by this sequence of points, which yields points sampled along a topological loop regardless of the type of periodic motion.
-Our technique for ordering the embedding combines tools from topological data analysis to determine the appropriate spatial scale, with tools from spectral geometric analysis to estimate the phase of each window.
-We also exploit the sliding window structure by using overlapping windows to vote on a final template after phase reordering.
-We show quantitative results that highlight the robustness of our technique to camera shake, noise, and occlusions, and we show qualitative results of single-cycle motion synthesis across a wide variety of scenarios.
+We combine tools from topological data analysis to determine the appropriate spatial scale, with tools from spectral geometric analysis to estimate the phase of each window.
+We also exploit the sliding window structure to robustly reorder frames.
+We show quantitative results that highlight the robustness of our technique to camera shake, noise, and occlusions, and qualitative results of single-cycle motion synthesis across a wide variety of scenarios.
 
@@
 However, our use of the graph Laplacian to instead {\em parameterize} time series is unique.
+%However, our use of the graph Laplacian to instead {\em parameterize} time series is unique.
 One can also view the combination of TDA and Laplacian eigenmaps as a simpler alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} for the special case of periodic data, and it is related to the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA.
@@
 
-\section{Discussion}
+\section{Conclusions}
 
-Since we rely on the theory and constructions in \cite{tralie2017quasi}, we are subject to similar constraints in the allowable motion and drift for our method to work well.
+We have presented an approach that combines topological data analysis with spectral geometric analysis to reorder a video consisting of repetitive periodic motion into a single, slow motion template cycle.
+Our quantitative results demonstrate robustness to noise, drift, and background outliers, and our qualitative results reveal motion that is challenging to visually perceive from the raw input video.
+For future work, we plan on exploring applications of our technique to detecting motion irregularities, as well as visualizing subtle motions from repetitive motion that is temporally aliased.
+We will also investigate robust TDA and spectral methods, and sliding window reordering techniques, for dealing with large amounts of drift.
+%Since we rely on the theory and constructions in \cite{tralie2017quasi}, we are subject to similar constraints in the allowable motion and drift for our method to work well.
 We note that Eulerian video magnification also degrades in the presence of too much drift \cite{wu2012eulerian, wadhwa2013phase}.

### 2018-02-11 Paper/paper.tex
at 4 pages

@@
 % MSB: opportunity to slim paper by cutting examples 
-Many prior works use a combination of sliding window embeddings and topological data analysis, for instance detecting chatter in mechanical systems \cite{khasawneh2016chatter} and quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}.
+Many prior works use a combination of sliding window embeddings and TDA, for instance detecting chatter in mechanical systems \cite{khasawneh2016chatter} and quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}.
 However, our approach in using a sliding window jointly with TDA to {\em synthesize} a new result is novel.
@@
 Figure~\ref{fig:ConceptFigure} shows the different parts of our method for a 1D periodic signal for illustration purposes.
-In general, the actual input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$.
+The actual input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$.
 We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mb{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$.
-The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}.
 For steps (a-c), we do not rely on the {\em extrinsic} geometry of the set of points $\mb{X}(t)$, only its set of {\em pairwise distances}.
@@
 In practice, graphs of the sliding window embedding may deviate from the ideal Laplacian model in Equation~\ref{eq:modellaplacian}, though they do so gracefully.
-Figure~\ref{fig:CirculantExample} shows an example of $\hat{v_1}[n]$ and $\hat{v_2}[n]$ for the unweighted case for an imperfect graph corresponding to the sliding window embedding of a video of two men doing jumping jacks.
-To further improve robustness, we default to the weighted Laplacian so that small changes in the threshold lead to small changes in $\mb{A}$.
+Figure~\ref{fig:CirculantExample} shows an example of $\hat{v_1}[n]$ and $\hat{v_2}[n]$ for the jumping jacks video.
+To improve robustness, we default to the weighted Laplacian so that small changes in the threshold lead to small changes in $\mb{A}$.
 In this case, harmonics of the actual frequency of interest occasionally have smaller eigenvalues when the corresponding harmonics are strongly present in the video.
@@
 \label{sec:tda}
-Our discussion so far has assumed we can find the appropriate $\sigma$ for the (un)weighted graph Laplacian, but this is data dependent.
-%The authors of \cite{averbuch2015ringit} use $k$-nearest neighbors, which helps with scale, but which still requires an arbitrary parameter $k$.
-To adapt to the data, we leverage 1D persistent homology from topological data analysis \cite{edelsbrunner2010computational}.
-This framework allows one to find the scale at which topological features exist in point cloud data.
-Specifically, we compute the 1D Vietoris Rips Filtration on our sliding window data $X$, which tracks equivalence classes of loops, known as {\em homology classes} \cite{Hatcher}, as edges and triangles are gradually added between sliding window points.
-The algorithm returns a so-called persistence diagram, which is a multiset of points on a 2D birth/death grid, with each point corresponding to a loop class.
+It remains to find the spatial scale $\sigma$ for the Laplacian.
+To adapt to the data, we leverage 1D persistent homology from TDA \cite{edelsbrunner2010computational} to find the scale at which the primary topological feature -- the single cycle -- exists.
+Specifically, we compute the 1D Vietoris Rips Filtration on our sliding window data $\mb{Z}$, which tracks equivalence classes of loops, known as {\em homology classes} \cite{Hatcher}.
+The algorithm returns a so-called persistence diagram, a multiset of points on a 2D birth/death grid, with each point corresponding to a loop class.
 The birth value $b_i$ indicates the scale at which the $i^{\text{th}}$ loop class forms, and the death value $d_i$ indicates the scale at which that class no longer exists.
 The difference $d_i - b_i$ is known as the {\em persistence} of the $i^{\text{th}}$ class.
-For sliding window periodic time series, one point in the diagram should have a much larger persistence than the others (e.g.
+For our scenario, one point in the diagram should have a much larger persistence than the others (e.g.
 Figure~\ref{fig:ConceptFigure})~\cite{perea2015sliding,tralie2017quasi}, and this ideally reflects the single cycle of motion that we seek.
@@
 The frame at angle $\phi_j$ is taken as the median of all interpolated frames.
-In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.
+Furthermore, we only use interpolated frames that are a user-prescribed amount away in time for each given reordered frame, to avoid ghosting artifacts~\cite{meyer2015phase}.
+%In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.
 We thus add an optional user-defined parameter ``F,'' and we only include interpolated frames in the median which are at most $F$ frames away from an actual frame.

### 2018-02-12 Paper/paper.tex
Submitted version of paper

@@
 
-In this paper we consider the problem of taking a video that is comprised of multiple periods of repetitive motion, and reordering the frames of the video into a single period, producing a detailed, single cycle video of motion.
-This problem is challenging to solve, as such videos often contain noise, drift due to camera motion and from cycle to cycle, and irrelevant background motion/occlusions, and these factors can confound the relevant periodic motion we seek in the video.
-To address these issues in a simple and efficient manner, we introduce an Eulerian approach for synthesizing a single cycle of motion, which requires no tracking.
-Our approach is geometric: we treat each video frame as a point in a high-dimensional Euclidean space, and analyze the {\em sliding window embedding} formed by this sequence of points, which yields points sampled along a topological loop regardless of the type of periodic motion.
-We combine tools from topological data analysis to determine the appropriate spatial scale, with tools from spectral geometric analysis to estimate the phase of each window.
-We also exploit the sliding window structure to robustly reorder frames.
-We show quantitative results that highlight the robustness of our technique to camera shake, noise, and occlusions, and qualitative results of single-cycle motion synthesis across a wide variety of scenarios.
+We consider the problem of taking a video that is comprised of multiple periods of repetitive motion, and reordering the frames of the video into a single period, producing a detailed, single cycle video of motion.
+This problem is challenging, as such videos often contain noise, drift due to camera motion and from cycle to cycle, and irrelevant background motion/occlusions, and these factors can confound the relevant periodic motion we seek in the video.
+To address these issues in a simple and efficient manner, we introduce a tracking free Eulerian approach for synthesizing a single cycle of motion.
+Our approach is geometric: we treat each frame as a point in high-dimensional Euclidean space, and analyze the sliding window embedding formed by this sequence of points, which yields samples along a topological loop regardless of the type of periodic motion.
+We combine tools from topological data analysis and spectral geometric analysis to estimate the phase of each window, and we exploit the sliding window structure to robustly reorder frames.
+We show quantitative results that highlight the robustness of our technique to camera shake, noise, and occlusions, and qualitative results of single-cycle motion synthesis across a variety of scenarios.
 
@@
 \begin{keywords}
-One, two, three, four, five
+Periodicity, slow motion, sliding window embeddings, graph Laplacian, persistent homology
 \end{keywords}
@@
 We use Laplacian Eigenmaps~\cite{belkin2003laplacian} computed on the sliding window embedding to obtain a circular phase $\phi \in [0, 2\pi]$ for each window.
-We then reorder the embedding using $\phi$, and reorder the video by having windows that overlap in time vote on final pixels in each frame of the template, further mitigating drift.
+We then reorder the windows by $\phi$, and we use windows that overlap in time vote on final pixels in each frame of the template, further mitigating drift.
 Figure~\ref{fig:ConceptFigure} highlights the steps of our technique for a sampled 1D periodic time series.
@@
 % MSB: opportunity to slim paper by cutting examples 
-Many prior works use a combination of sliding window embeddings and TDA, for instance detecting chatter in mechanical systems \cite{khasawneh2016chatter} and quantifying periodic activites in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}.
+Many prior works use a combination of sliding window embeddings and TDA, for instance detecting chatter in mechanical systems \cite{khasawneh2016chatter} and quantifying periodic activities in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}.
 However, our approach in using a sliding window jointly with TDA to {\em synthesize} a new result is novel.
 Related works have used the graph Laplacian to rearrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and to reorder the frames of microscope images from a developing embryo~\cite{dsilva2015diffusionvecordering}.
-However, our use of the graph Laplacian to instead {\em parameterize} time series is unique.
-%However, our use of the graph Laplacian to instead {\em parameterize} time series is unique.
+However, our use of the graph Laplacian to instead parameterize time series is unique.
+
+%However, our use of the graph Laplacian to instead parameterize time series is unique.
 One can also view the combination of TDA and Laplacian eigenmaps as a simpler alternative to cohomology circular coordinates \cite{de2011persistent,vejdemo2015cohomological} for the special case of periodic data, and it is related to the approach in \cite{bendich2011improving}, which performs diffusion maps before TDA.
@@
 In this case, harmonics of the actual frequency of interest occasionally have smaller eigenvalues when the corresponding harmonics are strongly present in the video.
-To mitigate this, we search through the 10 eigenvectors corresponding to the smallest 10 eigenvalues, sorted by eigenvalue, and we use the pair of adjacent eigenvectors with the smallest number of zero crossings whose zero crossing counts are within a factor of 5$\%$ of each other.
+To mitigate this, we search through the 10 eigenvectors corresponding to the smallest 10 eigenvalues, sorted by eigenvalue, and we use the pair of adjacent eigenvectors with the smallest number of zero crossings whose zero crossing counts are within a factor of 20$\%$ of each other.
 
@@
 Coefficients in $\mathbb{Z}_2$ are commonly chosen, however in our scenario this is problematic.
-For instance, the motion of a jumping jack contains a second harmonic, since an individual jumps twice per cycle, and using coefficients in $\mathbb{Z}_2$ would lead to so-called M{\"o}bius splitting~\cite{traliemoebius}.
+For instance, the motion of a jumping jack contains a second harmonic, since an individual jumps twice per cycle, and using coefficients in $\mathbb{Z}_2$ would lead to so-called M{\"o}bius splitting~\cite{traliemoebius, perea2015sliding}.
 Thus, we use coefficients in the field $\mathbb{Z}_{49}$ in order to capture these types of complex motions.
@@
 Let $\Phi_i$ be the unwrapped phase of $\phi_i$.
-Based on this, we esimate the number of periods $\mb{X}$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.
+Based on this, we estimate the number of periods $\mb{X}$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.
 Assuming $k$ is correct and that $\phi_i$ has a constant slope over $i$, there is a phase gap of $2 \pi k/N$ between adjacent stacked frames in each sliding window.
@@
 The frame at angle $\phi_j$ is taken as the median of all interpolated frames.
-Furthermore, we only use interpolated frames that are a user-prescribed amount away in time for each given reordered frame, to avoid ghosting artifacts~\cite{meyer2015phase}.
+Furthermore, we only use interpolated frames that are a user-prescribed amount $F$ away in time for each given reordered frame, to avoid ghosting artifacts~\cite{meyer2015phase}.
 %In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.
@@
 
-\subsection{Robustness Tests}
+\subsection{Quantitative Tests of Circular Coordinates}
 
@@
 \includegraphics[width=\columnwidth]{RobustnessTests.pdf}
-\caption{Robustness tests.}
+\caption{Average angular errors of circular coordinates under different sources of corruption on 3 different ground truth videos, with and without a sliding window.}
 \label{fig:RobustnessTests}
@@
 We first experimentally quantify the accuracy of our circular coordinate inference, since we cannot hope to get a good slow motion template without accurate circular coordinates.
-We generate 3 different 600 frame synthetic periodic videos for which we know the ground truth circular coordinates, using software from \cite{jacobson2012fast}.
+We generate 3 different 600 frame synthetic periodic videos for which we know the ground truth circular coordinates, using software from \cite{jacobson2012fast}\footnote{Please see supplementary material for these videos and simulated errors.}.
 Each video is roughly $300 \times 300$ pixels.
-We vary the number of cycles that the videos undergo between 3, 5, 10, 15, 20, 25, 30, 40, and 50.
-We then vary the ``shake'' of the video (width of a motion blur kernel) from $10 \times 10 $ to $50 \times 50$ pixels, in increments of 10, to assess the effect of drift.
-We also add Gaussian noise width standard deviations of $0.5, 1, 2$ (where original RGB ranges are in $[0, 1]$), and we add a color drifting square of length between 10 and 50 pixels taking a random walk to assess the effect of occlusions / background motion.
+We vary the number of cycles that the videos undergo between $3, 5, 10, 15, 20, 25, 30, 40, 50$.
+We then vary the ``shake'' of the video (width of a motion blur kernel) from $10 \times 10 $ to $50 \times 50$ pixels to assess the effect of drift.
+We then add Gaussian noise width standard deviations of $0.5, 1, 2$ (original RGB ranges are in $[0, 1]$.
+Finally, we add color drifting, occluding squares of varying lengths taking a random walk to assess the effect of occlusions / background motion.
 We also compare the $\alpha$ which weights the birth time and death time from TDA.
-Figure~\ref{fig:RobustnessTests} shows the average angular error in degrees for our entire pipeline under these variations.
-Overall, performance is stable to the choice of $\alpha$, and the errors are quite low for severe noise and for moderate shake and occlusions with a sliding window, though they increase as more shake or larger occlusions are introduced.
-Without a sliding window, the only video that performs reasonably well is the ``crowd'' video, since this is the only video which is loop-like without a sliding window embedding, though the errors increase much more rapidly than with the sliding window, validating the ``time regularization'' aspect of sliding windows.
+Figure~\ref{fig:RobustnessTests} shows the average angular error in degrees for our pipeline under these variations, over 50 trials per condition.
+Overall, performance is stable to the choice of $\alpha$, and the errors are low for severe noise and for moderate shake and occlusions with a sliding window.
+Without a sliding window, the only video that performs reasonably is the ``crowd'' video, though the errors increase more rapidly with shake/noise/occlusion than with the sliding window, validating the ``time regularization'' aspect of sliding windows.
 
-\subsection{Qualitative Results}
+\subsection{Qualitative Video Template Results}
 \begin{figure}
@@
 \includegraphics[width=\columnwidth]{XTSliceFan.pdf}
-\caption{An XT slice of a line of pixels (magenta line, upper left) over time for an input video of a fan with only 6 frames per period and the corresponding reorderd template.}
+\caption{An XT slice of a line of pixels (magenta line, upper left) over time for an input video of a fan with only 6 frames per period and the corresponding reordered template.}
 \label{fig:XTSliceFan}
@@
 Figure~\ref{fig:XTSliceFan} shows an extreme example in which an original spinning fan video has only 6 frames per period at framerate.
-In addition to these examples, in our supplementary material, we show results from jumping jacks 2 men, an exercise video \cite{levy2015live}, and beating heart videos \cite{traliehigh, wadhwa2013phase}.
+Please refer to our supplementary materials for these videos, as well as an exercise video \cite{levy2015live} and videos of amplified blood flow in the neck \cite{wadhwa2013phase} and face \cite{wu2012eulerian}.
 
@@
 Our quantitative results demonstrate robustness to noise, drift, and background outliers, and our qualitative results reveal motion that is challenging to visually perceive from the raw input video.
-For future work, we plan on exploring applications of our technique to detecting motion irregularities, as well as visualizing subtle motions from repetitive motion that is temporally aliased.
-We will also investigate robust TDA and spectral methods, and sliding window reordering techniques, for dealing with large amounts of drift.
-%Since we rely on the theory and constructions in \cite{tralie2017quasi}, we are subject to similar constraints in the allowable motion and drift for our method to work well.
-We note that Eulerian video magnification also degrades in the presence of too much drift \cite{wu2012eulerian, wadhwa2013phase}.
+For future work, we plan on exploring applications of our technique to detecting motion irregularities, visualizing subtle motions from repetitive motion that is temporally aliased, and reconstructing templates for videos with large amounts of missing data.
 

### 2018-02-12 Laplacian.py

@@ -50,22 +50,24 @@ def getSlopes(thetas, sWin = 10):
     slopes[-(sWin+1):] = slopes[-(sWin+1)]
     return slopes
 
-def getSlowestEigenvectorIdx(v, tol = 0.95):
+def getSlowestEigenvectorIdx(v, tol = 0.8):
     """
     Find the adjacent pair of eigenvectors with similar eigenvalues that have
     the smallest number of zero crossings
     :param v: NEigs x k array of eigenvectors arrange along columns
     :param tol: Reject pairs with zero crossings ratio less than tol
     """
-    #Compute zero crossings and put the low frequencies eigenvectors first
-    s = v > 0
-    zcs = np.sum(s[1::, :] - s[0:-1, :], 0)
+    #Compute circular zero crossings and put the low frequencies eigenvectors first
+    s = 1.0*(v > 0)
+    zcs = np.sum(np.abs(np.sign(s[1::, :]-s[0:-1, :])), 0)
     smallest = np.inf
     i1 = 1
     for i in range(1, len(zcs)-1):
-        ratio = min(float(zcs[i])/zcs[i+1], float(zcs[i+1])/zcs[i])
-        if ratio < tol:
-            continue
+        if tol > -1:
+            ratio = min(float(zcs[i])/zcs[i+1], float(zcs[i+1])/zcs[i])
+            print("%i and %i, %g"%(i, i+1, ratio))
+            if ratio < tol:
+                continue
         bothSum = zcs[i] + zcs[i+1]
         if bothSum < smallest:
             smallest = bothSum

### 2018-05-15 ImageAnalogies.py
Getting rid of image analogies, switching back to ripser, and cleaning up VideoReordering.py a bit

@@ -1,278 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import scipy.io as sio
-import scipy.misc
-from skimage.transform import pyramid_gaussian
-import pyflann
-from PatchTools import *
-from sklearn.decomposition import PCA
-import time
-
-def getCoherenceMatch(X, x0, BpLidx, dim, i, j):
-    """
-    :param X: An NImagesxMxNxDimFeatures array of feature vectors at each pixel\
-                in each image
-    :param x0: The feature vector of the pixel that's being filled in
-    :param BpLidx: An MxN array of raveled indices from which pixels have
-        been drawn so far
-    :param dim: Dimension of patch
-    :param i: Row of pixel
-    :param j: Column of pixel
-    """
-    k = int((dim*dim-1)/2)
-    M = X.shape[0]
-    N = X.shape[1]
-    minDistSqr = np.inf
-    idxmin = [-1, -1]
-    [dJ, dI] = np.meshgrid(np.arange(dim), np.arange(dim))
-    dI = np.array(dI.flatten()[0:k], dtype = np.int64) - (dim-1)/2
-    dJ = np.array(dJ.flatten()[0:k], dtype = np.int64) - (dim-1)/2
-    #TODO: Vectorize code below
-    for n in range(dI.size):
-        #Indices of pixel picked for neighbor
-        offi = int(dI[n]+i)
-        offj = int(dJ[n]+j)
-        imidx = int(BpLidx[offi, offj][0])
-        ni = BpLidx[offi, offj][1]
-        nj = BpLidx[offi, offj][1]
-        if ni == -1 or nj == -1:
-            continue
-        ni = int(ni - dI[n])
-        nj = int(nj - dJ[n])
-        if ni < 0 or nj < 0 or ni >= M or nj >= N:
-            continue
-        x = X[imidx, ni, nj, :]
-        distSqr = np.sum((x - x0)**2)
-        if distSqr < minDistSqr:
-            minDistSqr = distSqr
-            idxmin = [imidx, ni, nj]
-    return (idxmin, minDistSqr)
-
-def getPatchDictionaries(As, Aps, NLevels = 3, KSpatials = [5, 5], patchfn = getColorPatchesImageSet, kPCA = 5):
-    """
-    :param As: An array of images of the same dimension
-    :param Aps: An array of images of the same dimension as As, parallel to As
-    """
-    #Make image pyramids
-    ALs = []
-    ApLs = []
[…]

### 2018-05-15 VideoReordering.py

@@ -1,10 +1,14 @@
+"""
+Purpose: The main algorithm implementation of slow motion loops by sliding window
+video reordering
+"""
 from VideoTools import *
 from CSMSSMTools import *
 from Laplacian import *
 from FundamentalFreq import *
 from PatchTools import *
-from ImageAnalogies import *
 from TDA import *
+from ripser import Rips
 import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib.image as mpimage
@@ -13,6 +17,7 @@ import scipy.interpolate as interp
 from sklearn import manifold
 import time
 import argparse
+import os
 
 def getReorderedConsensus1D(X, N, thetau, doPlot = False):
     """
@@ -153,7 +158,7 @@ def getReorderedConsensusVideo(X, IDims, Mu, VT, dim, thetau, tdifflim = -1, \
         XRet[i, :] = F.flatten()
         XRet[i,:] = np.minimum(XRet[i,:],1.0)
         XRet[i,:] = np.maximum(XRet[i,:],0.0)
-        mpimage.imsave("%s%i.png"%(TEMP_STR, i+1), np.reshape(XRet[i, :], IDims))
+        #mpimage.imsave("%s%i.png"%(TEMP_STR, i+1), np.reshape(XRet[i, :], IDims))
     return XRet
     
 def downsampleVideo(I, IDims, fac):
@@ -171,46 +176,10 @@ def upsampleVideo(I, IDims, IDimsNew):
         INew.append(FNew.flatten())
     return np.array(INew)
 
-def sharpenVideo(XOrig, IDims, XDown, IDimsDown, XDownNew, NExamples = -1, NPerBatch = 40):
-    """
-    Use image analogies to sharpen the consensus video
-    """
-    As = []
-    Aps = []
-    idxs = np.arange(XOrig.shape[0])
-    if NExamples > 0:
-        #Randomly sample 10 analogy image pairs from original video
-        np.random.seed(NExamples)
-        idxs = np.random.permutation(XOrig.shape[0])[0:NExamples]
-    for idx in idxs:
-        A = np.reshape(XDown[idx, :], IDimsDown)
-        A = resizeImage(A, IDims)
-        Ap = np.reshape(XOrig[idx, :], IDims)
-        As.append(A)
-        Aps.append(Ap)
-    XFinal = []
-    NIters = int(np.ceil(XDownNew.shape[0]/float(NPerBatch)))
-    for it in range(NIters):
[…]

### 2018-05-15 Paper/paper.tex
Addressing reviewer confusion about prior art

@@
 % ---------------
-\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
-\address{Author Affiliation(s)}
+%\name{Author(s) Name(s)\thanks{Thanks to XYZ agency for funding.}}
+%\address{Author Affiliation(s)}
 %
@@
 % ----------------------------------------------------------
-%\twoauthors
-%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
-%	{School A-B\\
-%	Department A-B\\
-%	Address A-B}
-%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
-%	while at ...}}
-%	{School C-D\\
-%	Department C-D\\
-%	Address C-D}
+\twoauthors
+  {Christopher J. Tralie}
+	{Duke University,  Mathematics\\
+	ctralie@alumni.princeton.edu}
+  {Matthew Berger}
+	{University of Arizona, Computer Science\\
+	matthew.sh.berger@gmail.com}
 %
@@
 Eulerian approaches for video synthesis are attractive due to their simplicity and ease of implementation.
-For instance, a Fourier bandpass filtering can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.
-Additionally, time-domain Eulerian approaches have been used to synthesize infinitely playing ``video textures''~\cite{schodl2000video}, as well as looping video templates for more general scenarios~\cite{Liao2013VideoLoops,Liao2015VideoLoops}.
+For instance, a Fourier bandpass filter can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.
+Additionally, time-domain Eulerian approaches have been used to synthesize infinitely playing stochastic ``video textures''~\cite{schodl2000video}, as well as seamlessly looping video templates from a single cycle of periodic motion ~\cite{Liao2013VideoLoops,Liao2015VideoLoops} (this is not applicable to our problem since we fuse multiple cycles).
 There are some pitfalls with Eulerian techniques, however.
 They are known to fail for large motions, and also require the user to manually specify frequencies of interest \cite{wu2012eulerian, wadhwa2013phase}.
-Furthermore, period-to-period drift that is due to a moving camera or small variation in motion can be problematic, as well as unrelated motion in the background or occlusions \cite{stauffer1999adaptive}.
+Furthermore, period-to-period drift due to a moving camera or small motion variations can be problematic, as can unrelated motion in the background or occlusions \cite{stauffer1999adaptive}.
 
@@
 % MSB: opportunity to slim paper by cutting examples 
-Many prior works use a combination of sliding window embeddings and TDA, for instance detecting chatter in mechanical systems \cite{khasawneh2016chatter} and quantifying periodic activities in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}.
+Many prior works use a combination of sliding window embeddings and TDA, for instance to detect chatter in mechanical systems \cite{khasawneh2016chatter} and quantify periodic activities in motion capture data \cite{vejdemo2015cohomological, venkataraman2016persistent}.
 However, our approach in using a sliding window jointly with TDA to {\em synthesize} a new result is novel.
-Related works have used the graph Laplacian to rearrange images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit}, and to reorder the frames of microscope images from a developing embryo~\cite{dsilva2015diffusionvecordering}.
-However, our use of the graph Laplacian to instead parameterize time series is unique.
+Related works use spectral geometry to rearrange unstructured collections of images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit} or along a line to order the microscopic images of a developing embryo \cite{dsilva2015diffusionvecordering}.
+By constrast, we seek a cyclic order, and our input frames are ordered in time, enabling us to construct a sliding window.
 
@@
 Suppose we have extracted a sliding window embedding $SW_{d}$ for a video $\mb{Z}$ which repeats itself exactly every $T$ frames for $k$ times, for a total of $N = kT$ windows.
-Let us further suppose it is possible to choose an $\sigma$ so that the unweighted adjacency matrix contains an entry of 1 for edges corresponding to windows that are adjacent in time, as well as for the corresponding windows at, before, and after repetitions of the window at intervals of $T$; that is, the Laplacian is a symmetric, {\em circulant} matrix defined as
+Let us further suppose it is possible to choose a $\sigma$ so that the unweighted adjacency matrix contains an entry of 1 for edges corresponding to windows that are adjacent in time, as well as for the corresponding windows at, before, and after repetitions of the window at intervals of $T$; that is, the Laplacian is a symmetric, {\em circulant} matrix defined as
 
@@
 \bibliographystyle{IEEEbib}
+\footnotesize
 \bibliography{refs}

### 2018-05-15 Paper/paper.tex
Adding reference to my thesis

@@
 Coefficients in $\mathbb{Z}_2$ are commonly chosen, however in our scenario this is problematic.
-For instance, the motion of a jumping jack contains a second harmonic, since an individual jumps twice per cycle, and using coefficients in $\mathbb{Z}_2$ would lead to so-called M{\"o}bius splitting~\cite{traliemoebius, perea2015sliding}.
+For instance, the motion of a jumping jack contains a second harmonic, since an individual jumps twice per cycle, and using coefficients in $\mathbb{Z}_2$ would lead to so-called M{\"o}bius splitting~\cite{perea2015sliding, tralie2017geometric, traliemoebius}.
 Thus, we use coefficients in the field $\mathbb{Z}_{49}$ in order to capture these types of complex motions.

### 2018-05-15 Paper/paper.tex
minor edits

--- 2018-05-15 Paper/paper.tex
@@
   {Christopher J. Tralie}
-	{Duke University,  Mathematics\\
+	{Duke University,  Dept. of Mathematics\\
 	ctralie@alumni.princeton.edu}
   {Matthew Berger}
-	{University of Arizona, Computer Science\\
+	{University of Arizona, Dept. of Computer Science\\
 	matthew.sh.berger@gmail.com}
@@
 For instance, a Fourier bandpass filter can successfully elucidate subtle periodic motions in videos \cite{wu2012eulerian, wadhwa2013phase}.
-Additionally, time-domain Eulerian approaches have been used to synthesize infinitely playing stochastic ``video textures''~\cite{schodl2000video}, as well as seamlessly looping video templates from a single cycle of periodic motion ~\cite{Liao2013VideoLoops,Liao2015VideoLoops} (this is not applicable to our problem since we fuse multiple cycles).
+Time-domain Eulerian approaches can synthesize infinitely playing stochastic ``video textures''~\cite{schodl2000video}, as well as seamlessly loop video templates from a single cycle of periodic motion ~\cite{Liao2013VideoLoops,Liao2015VideoLoops}, though such approaches are not applicable to our problem since we fuse multiple cycles.
 There are some pitfalls with Eulerian techniques, however.
@@
 Related works use spectral geometry to rearrange unstructured collections of images around a loop as a pre-processing step for structure from motion \cite{averbuch2015ringit} or along a line to order the microscopic images of a developing embryo \cite{dsilva2015diffusionvecordering}.
-By constrast, we seek a cyclic order, and our input frames are ordered in time, enabling us to construct a sliding window.
+By constrast, we seek a cyclic reordering given input frames ordered in time, enabling us to construct a sliding window.
 
